### 2018-01-23 docs/paper.tex
rayleigh expansion and some POTCAR info in the paper

\documentclass[12pt]{article}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{gensymb}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{float}
\usepackage{braket}
\usepackage[margin=1.0in]{geometry}
\usepackage[style=chem-acs,backend=bibtex,articletitle=false]{biblatex}
\graphicspath{ {images/} }
\bibliography{mybib}

\begin{document}

\newcommand{\ind}{lm\epsilon}

\section{Theory}

\subsection{Projector Augmented Wave (PAW) Method}

\subsection{Projections}
\begin{equation}
\ket{\psi_{n\mathbf{k}}}=\ket{\widetilde{\psi}_{n\mathbf{k}}}+
\sum_{a,n,l,m}(\ket{\phi_{a\ind}}-\ket{\widetilde{\phi}_{a\ind}})
\braket{\widetilde{p}_{a\ind}|\widetilde{\psi}_{n\mathbf{k}}}
\label{eq:1}
\end{equation}

\subsubsection{Projection onto Basis from Different Structure}
In the pure physical picture of a quantum mechanical system, the eigenfunctions of the time
independent Hamiltonian form a complete basis for any function in real space. By expressing
a wavefunction from a system in the basis of the eigenstates of another system, one might
be able to learn about the nature of the wavefunction in question. For example, projecting
the wavefunction of a defect level in a periodic crystal onto the eigenfunctions of the
bulk crystal might yield information about how the defect level is constructed. For example,
the defect state might project primarily onto the conduction band, characterizing it
as a weakly perturbed host state. Such an understanding of defect levels could help select
corrections to perform on the defect system.\ref{eq:1}
\begin{equation}
\centering
\begin{split}
\braket{\psi_{Rn_1\mathbf{k}}|\psi_{Sn_2\mathbf{k}}}=\widetilde{O}+O_M+O_R+O_S+O_N\\
O_M=\sum_{a\in M_{RS}}\sum_{l,m}\sum_{\epsilon_1}\sum_{\epsilon_2}
\braket{\widetilde{\psi}_{Rn_1\mathbf{k}}|\widetilde{p}_{a\ind _1}}
(\braket{\phi_{a\ind _1}|{\phi_{a\ind _2}}}
-\bra{\widetilde{\phi}_{a\ind _1}}\ket{\widetilde{\phi}_{a\ind _2}})
\braket{\widetilde{p}_{a\ind _2}|\widetilde{\psi}_{Sn_2\mathbf{k}}}\\
O_R=\sum_{i\in N_R}\braket{\widetilde{\psi}_{Rn_1\mathbf{k}}|\widetilde{p}_i}
(\bra{\phi_i}-\bra{\widetilde{\phi}_i})
\ket{\widetilde{\psi}_{Sn_2\mathbf{k}}}\\
O_S=\sum_{j\in N_S}\bra{\widetilde{\psi}_{Rn_1\mathbf{k}}}(\ket{\phi_j}-\ket{\widetilde{\phi}_j})
\braket{\widetilde{p}_j|\widetilde{\psi}_{Sn_2\mathbf{k}}}\\
O_N=\sum_{i,j\in N_{RS}}\braket{\widetilde{\psi}_{Rn_1\mathbf{k}}|
\widetilde{p}_i}(\bra{\phi_i}-\bra{\widetilde{\phi}_i})
(\ket{\phi_j}-\ket{\widetilde{\phi}_j})\braket{\widetilde{p}_j|\widetilde{\psi}_{Sn_2\mathbf{k}}}
\end{split}
\label{eq:finp}
\end{equation}
Equation \ref{eq:finp} is derived in Appendix A.

\section{Implementation}

\section*{Appendix A: Derivation of Overlap Operators from PAW Formalism}
The starting point for this derivation is the transformation operator that
is performed on the pseudowavefunction to obtain the all electron wavefunction
\begin{equation}
T=1+\sum_a\sum_l\sum_m\sum_{\epsilon}(\ket{\phi_{a\ind}}-\ket{\widetilde{\phi}_{a\ind}})
\bra{\widetilde{p}_{a\ind}}=1+\sum_i(\ket{\phi_i}-\ket{\widetilde{\phi}_i})
\bra{\widetilde{p}_i}
\label{eq:T}
\end{equation}
where $\phi_{a\ind}$ are all electron (AE) partial waves, $\widetilde{\phi}_{a\ind}$
are pseudo (PS) partial waves, $\widetilde{p}_{a\ind}$ are projector functions,
$a$ are the site indices of each atom in the structure, and $l$, $m$, and $\epsilon$
specify a spherical harmonic and index which uniquely specify partial wave at a given
index. A summation over $i$ (or $j$, as below) represents a summation over $a$, $l$, $m$,
and $\epsilon$. For further details on the PAW method, including the physical significance
and construction of the partial waves and projector functions, see Blochl's original paper
and Kresse and Joubert's paper relating ultrasoft pseudopotentials and PAW.\cite{blochl}
The next step is to define and pseudo operator $\widetilde{A}$ for each operator $A$
such that $\bra{\psi}A\ket{\psi}=\bra{\widetilde{\psi}}\widetilde{A}\ket{\widetilde{\psi}}$.
Because $\ket{\psi}=T\ket{\widetilde{\psi}}$, one can write
\begin{equation}
\widetilde{A}=T^{\dagger}AT
\label{eq:op}
\end{equation}
One can then plug Equation \ref{eq:T} into Equation \ref{eq:op} to find
$$\widetilde{A}=[1+\sum_i\ket{\widetilde{p}_i}(\bra{\phi_i}-\bra{\widetilde{\phi}_i})]
A[1+\sum_j(\ket{\phi_j}-\ket{\widetilde{\phi}_j})
\bra{\widetilde{p}_j}]$$
\begin{equation}
\widetilde{A}=A+\sum_i\ket{\widetilde{p}_i}(\bra{\phi_i}-\bra{\widetilde{\phi}_i})A
+\sum_j A(\ket{\phi_j}-\ket{\widetilde{\phi}_j})\bra{\widetilde{p}_j}
+\sum_i\sum_j\ket{\widetilde{p}_i}(\bra{\phi_i}-\bra{\widetilde{\phi}_i})A
(\ket{\phi_j}-\ket{\widetilde{\phi}_j})\bra{\widetilde{p}_j}
\label{eq:res}
\end{equation}
Using the following relation,
$$(\bra{\phi_i}-\bra{\widetilde{\phi}_i})A(\ket{\phi_j}-\ket{\widetilde{\phi}_j})
=\bra{\phi_i}A\ket{\phi_j}-\bra{\widetilde{\phi}_i}A\ket{\phi_j}
-(\bra{\phi_i}-\bra{\widetilde{\phi}_i})A\ket{\widetilde{\phi}_j}$$
$$=\bra{\phi_i}A\ket{\phi_j}-\bra{\widetilde{\phi}_i}A(\ket{\phi_j}-\ket{\widetilde{\phi_j}})
-(\bra{\phi_i}-\bra{\widetilde{\phi}_i})A\ket{\widetilde{\phi}_j}
-\bra{\widetilde{\phi_i}}A\ket{\widetilde{\phi_j}}$$
one can rearrange Equation \ref{eq:res} in the manner of Blochl\cite{blochl}:
\begin{equation}
\begin{split}
\widetilde{A}=A+\sum_i\sum_j[\ket{\widetilde{p}_i}(\bra{\phi_i}A\ket{\phi_j}
-\bra{\widetilde{\phi_i}}A\ket{\widetilde{\phi_j}})\bra{\widetilde{p}_j}] \\
+\sum_i[(1-\sum_j\ket{\widetilde{p}_j}\bra{\widetilde{\phi}_j})A(\ket{\phi_i}-\ket{\widetilde{\phi_i}})
\bra{\widetilde{p}_i}+\ket{\widetilde{p}_i}
(\bra{\phi_i}-\bra{\widetilde{\phi}_i})A(1-\sum_j\ket{\widetilde{\phi}_j}\bra{\widetilde{p}_j})]
\end{split}
\label{eq:nonloc}
\end{equation}
When the operator $A$ is local, then $\sum_j\ket{\widetilde{\phi}_j}\bra{\widetilde{p}_j}=1$,
so the entire second line of Equation \ref{eq:nonloc} vanishes, giving Blochl's formulation:\cite{blochl}
\begin{equation}
\widetilde{A}=A+\sum_i\sum_j\ket{\widetilde{p}_i}(\bra{\phi_i}A\ket{\phi_j}
-\bra{\widetilde{\phi_i}}A\ket{\widetilde{\phi_j}})\bra{\widetilde{p}_j}
\label{eq:loc}
\end{equation}

However, while the overlap operator is local, the simplification in Equation \ref{eq:loc} assumes that
the summations over $i$ and $j$ go over the same species at the same locations in the same lattice;
only the third condition is always satisfied for systems of interest for projections between different
bases. Equation \ref{eq:res} is a more convenient representation than Equation \ref{eq:nonloc} for this
purpose because it is easily seen that all terms between projectors whose augmentation regions do not
overlap vanish. In addition, the POTCAR file in VASP only stores the PS and AE partial waves out to the
edge of the augmentation region, where they are equal but not nonzero, so it is useful to organize the terms
so that they are guaranteed to vanish outside the augmentation regions. Replacing $A$ with unity
allows the overlap between two bands
in different structures $R$ and $S$ with the same lattice to be specified (note that the
summation over $i$ is for structure $R$ and the summation over $j$ is for structure $S$):
\begin{equation}
\braket{\psi_{Rn_1\mathbf{k}}|\psi_{Sn_2\mathbf{k}}}=\widetilde{O}+O_1+O_2+O_3
\label{eq:ov1}
\end{equation}
$$\widetilde{O}=\braket{\widetilde{\psi}_{Rn_1\mathbf{k}}|\widetilde{\psi}_{Sn_2\mathbf{k}}}$$
$$O_1=\sum_i\braket{\widetilde{\psi}_{Rn_1\mathbf{k}}|\widetilde{p}_i}(\bra{\phi_i}-\bra{\widetilde{\phi}_i})
\ket{\widetilde{\psi}_{Sn_2\mathbf{k}}}$$
$$O_2=\sum_j\bra{\widetilde{\psi}_{Rn_1\mathbf{k}}}(\ket{\phi_j}-\ket{\widetilde{\phi}_j})
\braket{\widetilde{p}_j|\widetilde{\psi}_{Sn_2\mathbf{k}}}$$
$$O_3=\sum_i\sum_j\braket{\widetilde{\psi}_{Rn_1\mathbf{k}}|
\widetilde{p}_i}(\bra{\phi_i}-\bra{\widetilde{\phi}_i})
(\ket{\phi_j}-\ket{\widetilde{\phi}_j})\braket{\widetilde{p}_j|\widetilde{\psi}_{Sn_2\mathbf{k}}}$$
The pseudowavefunctions can be expanded as a summation of plane waves,
$$\widetilde{\psi}_{n\mathbf{k}}(\mathbf{r})=\sqrt{\frac{\omega_{\mathbf{k}}}{V}}
e^{i\mathbf{k}\cdot \mathbf{r}}\sum_{\mathbf{G}} C_{n\mathbf{k}\mathbf{G}}
e^{i\mathbf{G}\cdot \mathbf{r}}$$
so the overlap between two pseudowavefunctions per unit cell can be written as
$$\widetilde{O}=\braket{\widetilde{\psi}_{n_1\mathbf{k}_1}|\widetilde{\psi}_{n_2\mathbf{k}_2}}
=\delta_{\mathbf{k}_1,\mathbf{k}_2}
\omega_{\mathbf{k}} \sum_{\mathbf{G}} C^*_{n_1\mathbf{k}_1\mathbf{G}}C_{n_2\mathbf{k}_2\mathbf{G}}$$
In VASP, structures with the same energy, k-points, and lattice will have the same basis set,
so this projection is performed simply by reading plane wave coefficients from the VASP WAVECAR file.

It is important to simplify the calculation of the other terms in equation \ref{eq:ov1} as much
as possible because their calculation can be quite computationally intensive, and the number of
necessary calculations for projecting onto an entire basis set can scale with the number
of sites times the size of the basis set. One major simplification is that if a site $a$ in structure
$R$ and site $b$ in structure $S$ have the same species and position, $a$ and $b$ will only have
overlapping augmentation regions with each other and no other sites. Then, defining $O_{1a}$
as the summation over on-site terms for the identical sites $a$ and $b$ in $O_1$:
$$O_{1a}+O_{2a}+O_{3a}=\sum_{l,m}\sum_{\epsilon_1}\sum_{\epsilon_2}
\braket{\widetilde{\psi}_{Rn_1\mathbf{k}}|\widetilde{p}_{a\ind _1}}
(\braket{\phi_{a\ind _1}|{\phi_{a\ind _2}}}
-\bra{\widetilde{\phi}_{a\ind _1}}\ket{\widetilde{\phi}_{a\ind _2}})
\braket{\widetilde{p}_{a\ind _2}|\widetilde{\psi}_{Sn_2\mathbf{k}}}$$
which is the local operator solution derived by Blochl. All three terms must
be evaluated in full for the other sites, but terms in $O_3$ where $i$ and $j$ correspond
to sites with nonoverlapping augmentation spheres vanish. Therefore, if $M_{RS}$ is the set
of identical sites in the structures $R$ and $S$, $N_R$ and $N_S$ are the sets of sites
in $R$ and $S$ not in $M_{RS}$, and $N_{RS}$ is the set of \emph{pairs} of sites not in
$M$ with overlapping augmentation regions, then
$$
\braket{\psi_{Rn_1\mathbf{k}}|\psi_{Sn_2\mathbf{k}}}=\widetilde{O}+O_M+O_R+O_S+O_N
$$
$$
O_M=\sum_{a\in M_{RS}}\sum_{l,m}\sum_{\epsilon_1}\sum_{\epsilon_2}
\braket{\widetilde{\psi}_{Rn_1\mathbf{k}}|\widetilde{p}_{a\ind _1}}
(\braket{\phi_{a\ind _1}|{\phi_{a\ind _2}}}
-\bra{\widetilde{\phi}_{a\ind _1}}\ket{\widetilde{\phi}_{a\ind _2}})
\braket{\widetilde{p}_{a\ind _2}|\widetilde{\psi}_{Sn_2\mathbf{k}}}
$$
$$
O_R=\sum_{i\in N_R}\braket{\widetilde{\psi}_{Rn_1\mathbf{k}}|\widetilde{p}_i}
(\bra{\phi_i}-\bra{\widetilde{\phi}_i})
\ket{\widetilde{\psi}_{Sn_2\mathbf{k}}}
$$
$$
O_S=\sum_{j\in N_S}\bra{\widetilde{\psi}_{Rn_1\mathbf{k}}}(\ket{\phi_j}-\ket{\widetilde{\phi}_j})
\braket{\widetilde{p}_j|\widetilde{\psi}_{Sn_2\mathbf{k}}}
$$
$$
O_N=\sum_{i,j\in N_{RS}}\braket{\widetilde{\psi}_{Rn_1\mathbf{k}}|
\widetilde{p}_i}(\bra{\phi_i}-\bra{\widetilde{\phi}_i})
(\ket{\phi_j}-\ket{\widetilde{\phi}_j})\braket{\widetilde{p}_j|\widetilde{\psi}_{Sn_2\mathbf{k}}}
$$
which is Equation \ref{eq:finp}.

\section*{Appendix B: Comprehensive POTCAR Guide}
The PAWpySeed module makes use of the POTCAR files provided with the VASP source code, which
contain the projector functions, partial waves, pseudopotentials, and core charge densities
for each element. The format of the POTCAR file is not intuitive to non-developers, so this
appendix seeks to comprehensively document the format of the VASP POTCAR files.

\subsection*{Overview}
A single POTCAR contains the data for one element; a POTCAR file to a multi-element system
is made by simply concatenating elemental POTCAR files. Each PAW POTCAR file follows
the following format.

\begin{enumerate}
	\item
	Settings
	\item
	adsf
	\item
	\textbf{Non local Part}: This section contains the \emph{non local projector functions}.
	The first line after "Non local Part" gives the $l$ quantum number of the projector,
	the number of projectors for that $l$ quantum number, and the radius of the real
	space projector region.
	\begin{enumerate}
		\item
		\textbf{Reciprocal Space Part}: The reciprocal space projection operator.
		\item
		\textbf{Real Space Part}: The real space projection operator values on a radial
		grid. The radius at a given index $I$ is $RMAX*I/NDATA$, where RMAX and NDATA
		are given in the settings section. Since $I$ is 0-indexed, the true maximal
		radius of the projector is actually $RMAX*(NDATA-1)/NDATA$. Unlike the
		\emph{partial wave} values (see \textbf{pseudo wavefunction},
		the projector values are not mulitplied by $r$.
		$$p(\mathbf{r})=realspacepart(index)Y_l^m(\hat{\mathbf{r}})$$
	\end{enumerate}
	\item
	PAW Radial Sets
	\begin{enumerate}
		\item
		Augmentation charges
		\item
		Occupancies
		\item
		\textbf{grid}: The exponential grid on which calculations related
		to the \emph{partial waves} are performed.
		\item
		\textbf{pseudo wavefunction}: A pseudo \emph{partial wave} on the provided
		radial grid, multiplied by $r$ for easy radial integration. I.e.
		$$\phi(\mathbf{r}(index))=\frac{pseudowavefunction(index)}{r(index)}Y_l^m(\hat{\mathbf{r}})$$
		Listed in the same order as the projector functions.
		\item
		\textbf{ae wavefunction}: Same pseudo wavefunction, but for the all electron \emph{partial wave}.
	\end{enumerate}
\end{enumerate}

\subsection*{}

\printbibliography

\end{document}

### 2018-01-23 pawpyseed/projector.c

@@ -490,3 +490,11 @@ double* compensation_terms(int BAND_NUM, pswf_t* wf_proj, pswf_t* wf_ref, ppot_t
 	mkl_free_buffers();
 	return overlap;
 }
+
+double* nonlocal_compensation_terms(int BAND_NUM, pswf_t* wf_proj, pswf_t* wf_ref, ppot_t* pps,
+	int num_elems, int num_M, int num_N_R, int num_N_S, int num_N_RS,
+	int* M, int* N_R, int* N_S, int* N_RS,
+	int* proj_labels, double* proj_coords, int* ref_labels, double* ref_coords,
+	int* fft_grid) {
+	
+}

### 2018-01-23 pawpyseed/utils.c

@@ -328,6 +328,84 @@ void frac_from_index(int index, double* coord, int* fftg) {
 	coord[2] = ((double) (index % fftg[2])) / fftg[2];
 }
 
+void direction(double* cart, double* dir) {
+	double theta = 0, phi = 0;
+	theta = acos(cart[2]/r);
+	if (r - fabs(cart[2]) == 0) phi = 0;
+	else phi = acos(cart[0] / pow(cart[0]*cart[0] + cart[1]*cart[1], 0.5));
+	if (cart[1] < 0) phi = 2*PI - phi;
+	dir[0] = theta;
+	dir[1] = phi;
+}
+
+double sph_bessel(double k, double r, int l) {
+	double x = k * r;
+	if (l == 0)
+		return sin(x) / x;
+	else if (l == 1)
+		return sin(x) / (x*x) - cos(x) / x;
+	else if (l == 2)
+		return (3 / (x*x) -1) * sin(x) / x - 3 * cos(x) / (x*x);
+	else if (l == 3)
+		return (15 / (x*x*x) - 6 / x) * sin(x) / x - (15 / (x*x) -1) * cos(x) / x;
+	else
+		printf("ERROR: sph_bessel l too high");
+		return 0;
+}
+
+double complex rayexp(double* kpt, int* Gs, float complex* Cs, int l, int m,
+	int num_waves, double* sum_terms, double* ionp) {
+
+	double complex result = 0;
+	double pvec[3] = {0,0,0};
+	for (int w = 0; w < num_waves; w++) {
+		pvec[0] = kpt[0] + Gs[3*w+0];
+		pvec[1] = kpt[1] + Gs[3*w+1];
+		pvec[2] = kpt[2] + Gs[3*w+2];
+		phase = cexp(2*PI*I*dot(ionp, pvec));
+		result += phase * Cs[w] * ssum_terms[(2*l+1)*w+l+m]
+	}
+}
+
+double complex* rayexp_terms(double* kpt, int* Gs, int num_waves,
+	int l, int wavegridsize, double* wave_grid,
+	double* aewave, double* pswave, double* reclattice) {
+
+	double complex phase = 4 * PI * cpow(I, l);
+	double complex ylmdir = 0;
+	double k = 0;
+	double complex* terms = malloc((2*l+1) * num_waves * sizeof(double complex));
+
[…]

### 2018-01-24 pawpyseed/projector.c
added rayleigh terms to header files and calculate in compensation terms

@@ -371,7 +371,7 @@ void make_pwave_overlap_matrices(ppot_t* pp_ptr) {
 
 double* compensation_terms(int BAND_NUM, pswf_t* wf_proj, pswf_t* wf_ref, ppot_t* pps,
 	int num_elems, int num_M, int num_N_R, int num_N_S, int num_N_RS,
-	int* M, int* N_R, int* N_S, int* N_RS,
+	int* M_R, int* M_S, int* N_R, int* N_S, int* N_RS,
 	int* proj_labels, double* proj_coords, int* ref_labels, double* ref_coords,
 	int* fft_grid) {
 
@@ -411,7 +411,7 @@ double* compensation_terms(int BAND_NUM, pswf_t* wf_proj, pswf_t* wf_ref, ppot_t
 		lst_proj_projs[kpt_num] = onto_projector(proj_sites, proj_labels,
 			wf_proj->G_bounds, wf_proj->lattice, wf_proj->kpts[kpt_num]->k,
 			wf_proj->kpts[kpt_num]->Gs, wf_proj->kpts[kpt_num]->bands[BAND_NUM]->Cs,
-			wf_proj->kpts[kpt_num]->bands[BAND_NUM]->num_waves, num_M, N_RS, pps, fft_grid);
+			wf_proj->kpts[kpt_num]->bands[BAND_NUM]->num_waves, num_M, M_S, pps, fft_grid);
 	}
 	for (int i = 0; i < 4; i++) {
 		printf("quick check %d %d\n", M[i], N_RS[i]);
@@ -438,6 +438,10 @@ double* compensation_terms(int BAND_NUM, pswf_t* wf_proj, pswf_t* wf_ref, ppot_t
 //  -.168378085579E-01,  -.248833474970E-02,  -.490280055892E-02,  -.955532870297E-03,  -.348693200378E-02,
 //  -.749841796375E-01,  -.716350860052E-02,  -.251609311975E-01,  -.348693200378E-02,   .697731914902E-01,
 //};
+
+  	generate_rayleigh_expansion_terms(wf_ref, pps, num_elems);
+  	generate_rayleigh_expansion_terms(wf_proj, pps, num_elems);
+
 	int l1 = 0, l2 = 0;
 	#pragma omp parallel for
 	for (int w = 0; w < NUM_BANDS * NUM_KPTS; w++) {
[…]

### 2018-01-24 pawpyseed/projector.h

@@ -20,7 +20,7 @@ void make_pwave_overlap_matrices(ppot_t* pp_ptr);
 
 double* compensation_terms(int BAND_NUM, pswf_t* wf_proj, pswf_t* wf_ref, ppot_t* pps,
 	int num_elems, int num_M, int num_N_R, int num_N_S, int num_N_RS,
-	int* M, int* N_R, int* N_S, int* N_RS,
+	int* M_R, int* M_S, int* N_R, int* N_S, int* N_RS,
 	int* proj_labels, double* proj_coords, int* ref_labels, double* ref_coords, int* fft_grid);
 
 #endif

### 2018-01-24 pawpyseed/utils.c

@@ -329,9 +329,13 @@ double** spline_coeff(double* x, double* y, int N) {
 }
 
 void frac_from_index(int index, double* coord, int* fftg) {
-	coord[0] = ((double) (index / fftg[1] / fftg[2])) / fftg[0];
-	coord[1] = ((double) ((index % (fftg[1] * fftg[2])) / fftg[2])) / fftg[1];
-	coord[2] = ((double) (index % fftg[2])) / fftg[2];
+	int t1 = index / (fftg[1] * fftg[2]);
+	int t2 = index % (fftg[1] * fftg[2]);
+	int t3 = t2 % fftg[2];
+	t2 /= fftg[2];
+	coord[0] = ((double) t1) / fftg[0];
+	coord[1] = ((double) t2) / fftg[1];
+	coord[2] = ((double) t3) / fftg[2];
 }
 
 void direction(double* cart, double* dir) {
@@ -360,7 +364,7 @@ double sph_bessel(double k, double r, int l) {
 }
 
 double complex rayexp(double* kpt, int* Gs, float complex* Cs, int l, int m,
-	int num_waves, double* sum_terms, double* ionp) {
+	int num_waves, double complex* sum_terms, double* ionp) {
 
 	double complex result = 0;
 	double pvec[3] = {0,0,0};
@@ -371,6 +375,8 @@ double complex rayexp(double* kpt, int* Gs, float complex* Cs, int l, int m,
 		phase = cexp(2*PI*I*dot(ionp, pvec));
 		result += phase * Cs[w] * ssum_terms[(2*l+1)*w+l+m]
 	}
+
+	return result;
 }
 
 double complex* rayexp_terms(double* kpt, int* Gs, int num_waves,
@@ -380,7 +386,7 @@ double complex* rayexp_terms(double* kpt, int* Gs, int num_waves,
 	double complex phase = 4 * PI * cpow(I, l);
 	double complex ylmdir = 0;
 	double k = 0;
-	double complex* terms = malloc((2*l+1) * num_waves * sizeof(double complex));
+	double complex* terms = (double complex*) malloc((2*l+1) * num_waves * sizeof(double complex));
 
 	double pvec[3] = {0,0,0}
 	double phat[2] = {0,0};
@@ -409,6 +415,24 @@ double complex* rayexp_terms(double* kpt, int* Gs, int num_waves,
[…]

### 2018-01-24 pawpyseed/utils.h

@@ -12,6 +12,11 @@ typedef struct band {
 	float complex* Cs;
 } band_t;
 
+typedef struct rayleigh_terms {
+	int l;
+	double complex* terms;
+} rayleigh_set_t;
+
 typedef struct kpoint {
 	short int up;
 	int* Gs;
@@ -19,6 +24,7 @@ typedef struct kpoint {
 	double weight;
 	int num_bands;
 	band_t** bands;
+	rayleigh_set_t** expansion;
 } kpoint_t;
 
 typedef struct pswf {
@@ -139,6 +145,17 @@ double complex proj_value(funcset_t funcs, double* x, int m, double rmax,
 double** spline_coeff(double* x, double* y, int N);
 
 void frac_from_index(int index, double* coord, int* fftg);
+
+double sph_bessel(double k, double r, int l);
+
+double complex rayexp(double* kpt, int* Gs, float complex* Cs, int l, int m,
+	int num_waves, double complex* sum_terms, double* ionp);
+
+double complex* rayexp_terms(double* kpt, int* Gs, int num_waves,
+	int l, int wavegridsize, double* wave_grid,
+	double* aewave, double* pswave, double* reclattice);
+
+void generate_rayleigh_expansion_terms(pswf_t* wf, ppot_t* pps, int num_elems);
 
 void ALLOCATION_FAILED();
 

### 2018-01-24 pawpyseed/wavefunction.py
update compensation terms call

@@ -276,10 +276,11 @@ class Wavefunction:
 		print("datsa", nband, nwk, nspin)
 		res = cdouble_to_numpy(res, 2*nband*nwk*nspin)
 		M_R, M_S, N_R, N_S, N_RS = self.make_site_lists(basis)
+		num_N_RS, N_RS = len(N_RS), np.array(N_RS).flatten()
 		projector_list, selfnums, selfcoords, basisnums, basiscoords = self.make_c_projectors(basis)
 		ct = self.projector.compensation_terms(band_num, self.pwf.wf_ptr, basis.pwf.wf_ptr, projector_list, 
-			len(self.cr.pps), len(M_R), len(N_R), len(N_S), len(M_S), numpy_to_cint(M_R),
-			numpy_to_cint(N_R), numpy_to_cint(N_S), numpy_to_cint(M_S), numpy_to_cint(selfnums),
+			len(self.cr.pps), len(M_R), len(N_R), len(N_S), len(M_S), numpy_to_cint(M_R), numpy_to_cint(M_S),
+			numpy_to_cint(N_R), numpy_to_cint(N_S), numpy_to_cint(N_RS), numpy_to_cint(selfnums),
 			numpy_to_cdouble(selfcoords), numpy_to_cint(basisnums), numpy_to_cdouble(basiscoords),
 			numpy_to_cint(self.dim))
 		ct = cdouble_to_numpy(ct, 2*nband*nwk*nspin)

### 2018-01-24 pawpyseed/projector.c
syntax fixes

@@ -383,7 +383,7 @@ double* compensation_terms(int BAND_NUM, pswf_t* wf_proj, pswf_t* wf_ref, ppot_t
 
 	printf("%d %d %d %d %d %d\n", BAND_NUM, num_elems, num_M, num_N_R, num_N_S, num_N_RS);
 	printf("%d %lf %d %lf %d\n", proj_labels[0], proj_coords[0], ref_labels[0], ref_coords[0], fft_grid[1]);
-	printf("%d %d %d %d %d %d %d\n", wf_proj->nband, wf_ref->nband, pps[0].funcs[0].l, M[0], N_R[0], N_S[0], N_RS[0]);
+	printf("%d %d %d %d %d %d %d\n", wf_proj->nband, wf_ref->nband, pps[0].funcs[0].l, M_R[0], N_R[0], N_S[0], N_RS[0]);
 	
 	int NUM_KPTS = wf_proj->nwk * wf_proj->nspin;
 	int NUM_BANDS = wf_proj->nband;
@@ -414,7 +414,7 @@ double* compensation_terms(int BAND_NUM, pswf_t* wf_proj, pswf_t* wf_ref, ppot_t
 			wf_proj->kpts[kpt_num]->bands[BAND_NUM]->num_waves, num_M, M_S, pps, fft_grid);
 	}
 	for (int i = 0; i < 4; i++) {
-		printf("quick check %d %d\n", M[i], N_RS[i]);
+		printf("quick check %d %d\n", M_R[i], N_RS[i]);
 	}
 	stop = clock();
 	printf("time %ld\n", (stop - start)/CLOCKS_PER_SEC);
@@ -454,7 +454,7 @@ double* compensation_terms(int BAND_NUM, pswf_t* wf_proj, pswf_t* wf_ref, ppot_t
 		//printf("stat check %e %e\n", creal(proj_projs[50]), creal(ref_projs[50]));
 		int t = 0;
 		for (int s = 0; s < num_M; s++) {
-			ppot_t pp = pps[ref_labels[M[s]]];
+			ppot_t pp = pps[ref_labels[M_R[s]]];
 			int ti = 0;
 			for (int i = 0; i < pp.num_projs; i++) {
 				l1 = pp.funcs[i].l;
[…]

### 2018-01-24 pawpyseed/reader.c

@@ -157,6 +157,7 @@ pswf_t* read_wavefunctions(char* filename, double* kpt_weights) {
 		fread(kptr, 8, nrecl/8, pfp);
 		
 		int nplane = (int) round(kptr[0]);
+		kpt->num_waves = nplane;
 		int* igall = malloc(3*nplane*sizeof(int));
 		if (igall == NULL) {
 		    	ALLOCATION_FAILED();

### 2018-01-24 pawpyseed/utils.h

@@ -19,6 +19,7 @@ typedef struct rayleigh_terms {
 
 typedef struct kpoint {
 	short int up;
+	int num_waves;
 	int* Gs;
 	double* k;
 	double weight;
@@ -152,7 +153,7 @@ double complex rayexp(double* kpt, int* Gs, float complex* Cs, int l, int m,
 	int num_waves, double complex* sum_terms, double* ionp);
 
 double complex* rayexp_terms(double* kpt, int* Gs, int num_waves,
-	int l, int wavegridsize, double* wave_grid,
+	int l, int wave_gridsize, double* wave_grid,
 	double* aewave, double* pswave, double* reclattice);
 
 void generate_rayleigh_expansion_terms(pswf_t* wf, ppot_t* pps, int num_elems);

### 2018-02-06 pawpyseed/memtest.c
WORKING SBT

@@ -4,6 +4,7 @@
 #include <math.h>
 #include <string.h>
 #include "utils.h"
+#include "pseudoprojector.h"
 #include "projector.h"
 #include "reader.h"
 #include "tests.h"
@@ -120,9 +121,10 @@ void test_compensation_terms() {
 
 	fclose(fp);
 
+	char* rm[1] = {"2.1042"};
 	printf("pps\n");
 	ppot_t* pps = get_projector_list(num_els, labels, ls, pgrids, wgrids,
-		projectors, aewaves, pswaves, rmaxs);
+		projectors, aewaves, pswaves, rm);
 
 	free(labels);
 	free(pgrids);

### 2018-02-06 pawpyseed/projector.c

@@ -11,6 +11,7 @@
 #include "fft.h"
 #include "quadrature.h"
 #include "radial.h"
+#include "sbt.h"
 
 #define c 0.262465831
 #define PI 3.14159265358979323846
@@ -309,6 +310,11 @@ void setup_projections(pswf_t* wf, ppot_t* pps, int num_elems,
 	for (int p = 0; p < num_elems; p++) {
 		make_pwave_overlap_matrices(pps+p);
 		add_num_cart_gridpts(pps+p, wf->lattice, fftg);
+		double* ks = (double*) malloc(pps[p].wave_gridsize * sizeof(double));
+		sbt_desciptor_t* d = spherical_bessel_transform_setup(520, 1000, 2, pps[p].wave_gridsize, pps[p].wave_grid);
+		for (int i = 0; i < pps[p].num_projs; i++)
+			wave_spherical_bessel_transform(d, pps[p].wave_grid, pps[p].funcs[i].aewave, ks, pps[p].funcs[i].l);
+		free(ks);
 	}
 	int NUM_KPTS = wf->nwk * wf->nspin;
 	int NUM_BANDS = wf->nband;
@@ -321,7 +327,7 @@ void setup_projections(pswf_t* wf, ppot_t* pps, int num_elems,
 		onto_projector(kpt, band_num, sites, num_sites, labels,
 			wf->G_bounds, wf->lattice, wf->reclattice, pps, fftg);
 	}
-	free_real_proj_site_list(sites, num_sites);
+	free_real_proj_site_list(sites, num_sites);	
 	generate_rayleigh_expansion_terms(wf, pps, num_elems);
 }
 
@@ -393,7 +399,7 @@ double* compensation_terms(int BAND_NUM, pswf_t* wf_proj, pswf_t* wf_ref, ppot_t
 	int l1 = 0, l2 = 0;
 	double complex** N_RS_overlaps = overlap_setup(wf_ref, wf_proj, pps, ref_labels, proj_labels,
 		ref_coords, proj_coords, N_RS_R, N_RS_S, num_N_RS);
-	double inv_sqrt_vol = pow(determinant(wf->lattice), -0.5);
+	double inv_sqrt_vol = pow(determinant(wf_ref->lattice), -0.5);
 
 	#pragma omp parallel for
 	for (int w = 0; w < NUM_BANDS * NUM_KPTS; w++) {

### 2018-02-06 pawpyseed/radial.c

@@ -49,7 +49,7 @@ double complex offsite_wave_overlap(double* coord1, double* r1, double* f1, doub
 				}
 			}
 		}
-		dr = r1[rstep+1] - r1[rstep];
+		if (rstep+1 != size1) dr = r1[rstep+1] - r1[rstep];
 	}
 
 	dr = r2[0];
@@ -76,7 +76,7 @@ double complex offsite_wave_overlap(double* coord1, double* r1, double* f1, doub
 				}
 			}
 		}
-		dr = r2[rstep+1] - r2[rstep];
+		if (rstep+1 != size2) dr = r2[rstep+1] - r2[rstep];
 	}
 
 	return integral;

### 2018-02-06 pawpyseed/sbt.c

@@ -20,50 +20,44 @@ Talman, J. Computer Physics Communications 2009, 180, 332 –338.
 The code is distributed under the Standard CPC license.
 */
 
-typedef struct sbt_setup {
-	double kmin;
-	double kappamin;
-	double rmin;
-	double rhomin;
-	double rho; //drho == dkappa
-	double dt;
-	double N;
-	double complex** mult_table;
-} sbt_desciptor_t;
-
 sbt_desciptor_t* spherical_bessel_transform_setup(double encut, double enbuf, int lmax, int N, double* r) {
 
+	setbuf(stdout, NULL);
 	sbt_desciptor_t* descriptor = (sbt_desciptor_t*) malloc(sizeof(sbt_desciptor_t));
 
-	double kmin = pow((encut+enbuf) * c, 0.5) * exp(-(N-1) * drho);
-	double kappamin = log(kmin);
-	double complex** mult_table = (double complex**) malloc(lmax * sizeof(double complex*));
+	if (lmax == 0) lmax = 1;
+	double complex** mult_table = (double complex**) malloc((lmax+1) * sizeof(double complex*));
 	double drho = log(r[1] / r[0]);
 	double rhomin = log(r[0]);
 	double dt = 2 * PI / N / drho;
 	double rmin = r[0];
+	double kmin = pow((encut+enbuf) * c, 0.5) * exp(-(N-1) * drho);
+	double kappamin = log(kmin);
 	mult_table[0] = (double complex*) calloc(N, sizeof(double complex));
 	mult_table[1] = (double complex*) calloc(N, sizeof(double complex));
+	for (int i = 2; i <= lmax; i++)
+		mult_table[i] = (double complex*) calloc(N, sizeof(double complex));
+	double t=0, rad=0, phi=0, phi1=0, phi2=0, phi3=0;
 	for (int i = 0; i < N; i++) {
 		t = i * dt;
 		rad = pow(10.5*10.5+t*t, 0.5);
 		phi3 = (kappamin + rhomin) * t;
 		phi = atan((2*t)/21);
-		phi1 = -10*phi - t*log(rad) + t + sin(phi)/(12*red)
+		phi1 = -10*phi - t*log(rad) + t + sin(phi)/(12*rad)
[…]

### 2018-02-06 pawpyseed/tests.c

@@ -7,6 +7,7 @@
 #include "utils.h"
 #include "fft.h"
 #include "projector.h"
+#include "sbt.h"
 #include <mkl.h>
 #include <mkl_types.h>
 #include <assert.h>
@@ -17,25 +18,31 @@ double Ylmr(int l, int m, double theta, double phi) { return creal(Ylm(l, m, the
 
 double Ylmi(int l, int m, double theta, double phi) { return cimag(Ylm(l, m, theta, phi)); }
 
+double* real_wave_spherical_bessel_transform(sbt_desciptor_t* d,
+        double* r, double* f, double* ks, int l) {
+
+	double complex* vals = wave_spherical_bessel_transform(d, r, f, ks, l);
+	double* res = (double*) malloc(2 * d->N * sizeof(double));
+	for (int i = 0; i < d->N; i++) {
+		res[2*i] = creal(vals[i]);
+		res[2*i+1] = cimag(vals[i]);
+	}
+	free(vals);
+	return res;
+}
+
 int fft_check(char* wavecar, double* kpt_weights, int* fftg) {
 	
-	freopen("mytest.out", "w", stdout);
 	setbuf(stdout, NULL);
 
-	printf("made it 0");
 	pswf_t* wf = read_wavefunctions("WAVECAR", kpt_weights);
 	MKL_Complex16* x = (MKL_Complex16*) mkl_calloc(fftg[0]*fftg[1]*fftg[2], sizeof(MKL_Complex16), 64);
-	printf("%d\n", fftg[0]);
-	printf("%d\n", fftg[1]);
-	printf("%d\n", fftg[2]);
-	printf("made it 1");
 	fft3d(x, wf->G_bounds, wf->lattice, wf->kpts[0]->k, wf->kpts[0]->Gs, wf->kpts[0]->bands[0]->Cs, wf->kpts[0]->bands[0]->num_waves, fftg);
 	int* Gs = wf->kpts[0]->Gs;
 	float complex* Cs = wf->kpts[0]->bands[0]->Cs;
 	double inv_sqrt_vol = pow(determinant(wf->lattice), -0.5);
 	double dv = determinant(wf->lattice) / fftg[0] / fftg[1] / fftg[2];
 	double* kpt = wf->kpts[0]->k;
-	printf("made it 2\n");
 	double total1 = 0;
 	double total2 = 0;
 	double total3 = 0;
[…]

### 2018-02-06 pawpyseed/tests.h

@@ -1,8 +1,12 @@
 #ifndef TESTS_H
 #define TESTS_H
+#include "sbt.h"
 
 double Ylmr(int l, int m, double theta, double phi);
 double Ylmi(int l, int m, double theta, double phi);
+
+double* real_wave_spherical_bessel_transform(sbt_desciptor_t* d,
+        double* r, double* f, double* ks, int l);
 
 int fft_check(char* wavecar, double* kpt_weights, int* fftg);
 

### 2018-02-06 pawpyseed/tests.py

@@ -1,5 +1,5 @@
 import unittest
-import os, subprocess
+import os, subprocess, sys
 import time
 import scipy
 
@@ -24,6 +24,7 @@ PAWC.Ylmi.restype = c_double
 PAWC.spline_coeff.restype = POINTER(POINTER(c_double))
 PAWC.proj_interpolate.restype = c_double
 PAWC.spherical_bessel_transform_setup.restype = POINTER(None)
+PAWC.real_wave_spherical_bessel_transform.restype = POINTER(c_double)
 
 def cdouble_to_numpy(arr, length):
 	arr = cast(arr, POINTER(c_double))
@@ -238,19 +239,30 @@ class TestC:
 		PAWC.fft_check("WAVECAR", kws, numpy_to_cint(np.array([40,40,40])))
 
 	def test_sbt(self):
-		import scipy.special.spherical_jn as jn
-		k = 4
+		from scipy.special import spherical_jn as jn
+		k = 0.152
 		cr = CoreRegion(Potcar.from_file("POTCAR"))
-		r = cr.pps['Ga'].wavegrid
-		f = cr.pps['Ga'].aewaves[2] - cr.pps['Ga'].aewaves[2];
+		r = cr.pps['Ga'].grid
+		f = cr.pps['Ga'].aewaves[0] - cr.pps['Ga'].pswaves[0];
 		ks = (c_double * len(r))()
-		sbtd = PAWC.spherical_bessel_transform_setup(520, 520, 2, 323, r)
-		res = wave_spherical_bessel_transform(sbtd, numpy_to_cdouble(r),
-			numpy_to_cdouble(f), ks, 1)
-		vals = jn(1, r * k) * f
+		print ('yo')
+		print (len(r), len(numpy_to_cdouble(r)))
+		sys.stdout.flush()
+		sbtd = PAWC.spherical_bessel_transform_setup(c_double(520), c_double(5000), 2, len(r), numpy_to_cdouble(r))
+		print ('yo')
+		sys.stdout.flush()
+		res = PAWC.real_wave_spherical_bessel_transform(sbtd, numpy_to_cdouble(r),
+			numpy_to_cdouble(f), ks, 0)
+		print ('hi')
+		sys.stdout.flush()
+		print (r, f)
+		vals = jn(0, r * k) * f * r
 		integral = np.trapz(vals, r)
-		print(ks)
+		#print (cdouble_to_numpy(ks, 388)[334])
[…]

### 2018-02-06 pawpyseed/wavefunction.py

@@ -125,7 +125,8 @@ class Pseudopotential:
 		for projstr in projstrs:
 			lst = projstr.split("Reciprocal Space Part")
 			nonlocalvals, projs = lst[0], lst[1:]
-			self.rmaxstr = c_char_p(nonlocalvals.split()[2])
+			self.rmaxstr = c_char_p()
+			self.rmaxstr.value = nonlocalvals.split()[2].encode('utf-8')
 			nonlocalvals = self.make_nums(nonlocalvals)
 			l = nonlocalvals[0]
 			count = nonlocalvals[1]
@@ -397,13 +398,13 @@ class Wavefunction:
 		pswaves = np.array([], np.float64)
 		wgrids = np.array([], np.float64)
 		pgrids = np.array([], np.float64)
-		rmaxstrs = []
+		rmaxstrs = (c_char_p * len(pps))()
 		num_els = 0
 
 		for num in pps:
 			pp = pps[num]
 			clabels = np.append(clabels, [num, len(pp.ls), pp.ndata, len(pp.grid)])
-			rmaxstrs.append(pp.rmaxstr)
+			rmaxstrs[num_els] = pp.rmaxstr
 			ls = np.append(ls, pp.ls)
 			wgrids = np.append(wgrids, pp.grid)
 			pgrids = np.append(pgrids, pp.projgrid)
@@ -420,7 +421,7 @@ class Wavefunction:
 		projector_list = self.projector.get_projector_list(num_els, numpy_to_cint(clabels),
 			numpy_to_cint(ls), numpy_to_cdouble(pgrids), numpy_to_cdouble(wgrids),
 			numpy_to_cdouble(projectors), numpy_to_cdouble(aewaves), numpy_to_cdouble(pswaves),
-			(c_char_p * 4)(rmaxstrs))
+			rmaxstrs)
 		selfnums = np.array([labels[el(s)] for s in self.structure], dtype=np.int32)
 		basisnums = np.array([labels[el(s)] for s in basis.structure], dtype=np.int32)
 		selfcoords = np.array([], np.float64)
@@ -452,7 +453,7 @@ if __name__ == '__main__':
 	wf1 = Wavefunction(posb, pwf1, CoreRegion(pot), (30,30,30))
 	wf2 = Wavefunction(posd, pwf2, CoreRegion(pot), (30,30,30))
 	wf2.setup_projection(wf1)
-	for i in range(0,24):
+	for i in range(0,12):
 		wf2.single_band_projection(i, wf1)
 
 	wf1.free_all()

### 2018-02-06 docs/paper.tex
plane wave decomposition

@@
 \section{Implementation}
+
+\subsection{Projection of Pseudowavefunctions onto Partial Waves}
+
+\begin{equation}
+e^{i\mathbf{k} \cdot \mathbf{r}} = 4\pi \sum_{l=0}^{\infty}\sum_{m=-l}^{l}
+i^l j_l(kr)Y_l^{m*}(\mathbf{\hat{k}})Y_l^m(\mathbf{\hat{r}})
+\label{eq:pwexp}
+\end{equation}
+$\mathbf{r_A} = \mathbf{r} - \mathbf{R_A}$, $\phi_i(\mathbf{r})=R_i(r)Y_l^m(\mathbf{\hat{r}})$,
+$\widetilde{\phi}_i(\mathbf{r})=\widetilde{R}_i(r)Y_l^m(\mathbf{\hat{r}})$,
+$\mathbf{k'}=\mathbf{k}+\mathbf{G}$\\
+$$\widetilde{\psi}_{n\mathbf{k}}=\frac{1}{\sqrt{V}}\sum_{\mathbf{G}}
+C_{n\mathbf{k}\mathbf{G}}e^{i\mathbf{k'}\cdot \mathbf{r}}$$
+$$\widetilde{\psi}_{n\mathbf{k}}=\frac{4\pi}{\sqrt{V}}\sum_{\mathbf{G}}
+C_{n\mathbf{k}\mathbf{G}}\sum_{l=0}^{\infty}\sum_{m=-l}^{l}
+i^l j_l(k'r_A)Y_l^{m*}(\mathbf{\hat{k'}})Y_l^m(\mathbf{\hat{r}_A})$$
+$$\phi_i(\mathbf{r})\widetilde{\psi}_{n\mathbf{k}}=\frac{4\pi}{\sqrt{V}}\sum_{\mathbf{G}}
+C_{n\mathbf{k}\mathbf{G}}\sum_{l'=0}^{\infty}\sum_{m'=-l'}^{l'}
+i^{l'} j_{l'}(k'r_A)Y_{l'}^{m'*}(\mathbf{\hat{k'}})Y_{l'}^{m'}(\mathbf{\hat{r}_A})
+Y_l^{m*}(\mathbf{\hat{r}}_A)R_i(r_A)$$
+$$\braket{\phi_i(\mathbf{r})|\widetilde{\psi}_{n\mathbf{k}}}=
+\frac{4\pi i^l}{\sqrt{V}}\sum_{\mathbf{G}} C_{n\mathbf{k}\mathbf{G}}
+Y_l^{m*}(\mathbf{\hat{k'}})\int_0^{\infty}drr^2R_i(r_A)j_l(k'r_A)$$
+$$\braket{\phi_i-\widetilde{\phi}_i|\widetilde{\psi}_{n\mathbf{k}}}=
+\frac{4\pi i^l}{\sqrt{V}}\sum_{\mathbf{G}} C_{n\mathbf{k}\mathbf{G}}
+Y_l^{m*}(\mathbf{\hat{k'}})\int_0^{\infty}drr^2R_i(r_A)j_l(k'r_A)$$
+
+After the projection is decomposed into a summation over integrals of spherical
+Bessel functions, it can be calculated via spherical Bessel transform. This code
+uses the fast spherical Bessel transform method NumSBT developed by Talman.\cite{TALMAN}
+It runs in $O(NlnN)$ time and works on a logarithmic grid, making it convenient for use with
+the POTCAR representations of the partial waves. The resulting logarithmic k-space
+grid can be used to calculate the values of the relevant integrals via interpolation.
 

### 2018-02-07 pawpyseed/projector.c
begin interfacing sbt with the main projector code

@@ -33,6 +33,8 @@ ppot_t* get_projector_list(int num_els, int* labels, int* ls, double* proj_grids
 		printf("vals %d %d %d\n", pps[i].num_projs, pps[i].proj_gridsize, pps[i].wave_gridsize);
 		pps[i].total_projs = 0;
 		pps[i].wave_grid = (double*) malloc((pps[i].wave_gridsize)*sizeof(double));
+		pps[i].kwave_grid = (double*) malloc((pps[i].wave_gridsize)*sizeof(double));
+		pps[i].lmax = 0;
 		pps[i].pspw_overlap_matrix = NULL;
 		pps[i].aepw_overlap_matrix = NULL;
 		pps[i].diff_overlap_matrix = NULL;
@@ -52,6 +54,8 @@ ppot_t* get_projector_list(int num_els, int* labels, int* ls, double* proj_grids
 			funcs[k].pswave = (double*) malloc(sizeof(double)*pps[i].wave_gridsize);
 			funcs[k].diffwave = (double*) malloc(sizeof(double)*pps[i].wave_gridsize);
 			funcs[k].l = ls[l_num];
+			if (funcs[k].l > pps[i].maxl)
+				pps[i].lmax = funcs[k].l;
 			pps[i].total_projs += 2 * ls[l_num] + 1;
 			l_num++;
 			for (int j = 0; j < pps[i].wave_gridsize; j++) {
@@ -69,8 +73,19 @@ ppot_t* get_projector_list(int num_els, int* labels, int* ls, double* proj_grids
 			funcs[k].pswave_spline = spline_coeff(pps[i].wave_grid, funcs[k].pswave, pps[i].wave_gridsize);
 			funcs[k].diffwave_spline = spline_coeff(pps[i].wave_grid, funcs[k].diffwave, pps[i].wave_gridsize);
 		}
+		sbt_desciptor_t* d = spherical_bessel_transform_setup(520, 520*4, pps[i].lmax,
+			pps[i].wave_gridsize, pps[i].wave_grid, pps[i].kwave_grid);
+		for (int k = 0; k < pps[i].num_projs; k++) {
+			funcs[k].kwave = wave_spherical_bessel_transform(d, pps[i].wave_grid,
+				funcs[k].diffwave, pps[i].kwave_grid, funcs[k].l);
[…]

### 2018-02-07 pawpyseed/sbt.c

@@ -20,7 +20,8 @@ Talman, J. Computer Physics Communications 2009, 180, 332 –338.
 The code is distributed under the Standard CPC license.
 */
 
-sbt_desciptor_t* spherical_bessel_transform_setup(double encut, double enbuf, int lmax, int N, double* r) {
+sbt_desciptor_t* spherical_bessel_transform_setup(double encut, double enbuf, int lmax, int N,
+	double* r, double* ks) {
 
 	setbuf(stdout, NULL);
 	sbt_desciptor_t* descriptor = (sbt_desciptor_t*) malloc(sizeof(sbt_desciptor_t));
@@ -33,6 +34,9 @@ sbt_desciptor_t* spherical_bessel_transform_setup(double encut, double enbuf, in
 	double rmin = r[0];
 	double kmin = pow((encut+enbuf) * c, 0.5) * exp(-(N-1) * drho);
 	double kappamin = log(kmin);
+	for (int p = 0; p < N; p++) {
+		ks[p] = kmin * exp(p * drho);
+	}
 	mult_table[0] = (double complex*) calloc(N, sizeof(double complex));
 	mult_table[1] = (double complex*) calloc(N, sizeof(double complex));
 	for (int i = 2; i <= lmax; i++)
@@ -72,7 +76,7 @@ sbt_desciptor_t* spherical_bessel_transform_setup(double encut, double enbuf, in
 	return descriptor;
 }
 
-double complex* wave_spherical_bessel_transform(sbt_desciptor_t* d,
+double* wave_spherical_bessel_transform(sbt_desciptor_t* d,
 	double* r, double* f, double* ks, int l) {
 
 	double kmin = d->kmin;
@@ -101,14 +105,11 @@ double complex* wave_spherical_bessel_transform(sbt_desciptor_t* d,
 		x[m].real = pow(r[m], 0.5) * f[m]; // f is multiplied by r
 		x[m].imag = 0;
 	}
-	double rp=0.0, ip=0.0;
 	status = DftiComputeBackward(handle, x);
 	printf("status %ld\n", status);
 	for (int n = 0; n < N; n++) {
-		rp = x[n].real * creal(M[l][n]) - x[n].imag * cimag(M[l][n]);
-		ip = x[n].imag * creal(M[l][n]) + x[n].real * cimag(M[l][n]);
[…]

### 2018-02-07 pawpyseed/sbt.h

@@ -20,9 +20,10 @@ typedef struct sbt_setup {
         double complex** mult_table;
 } sbt_desciptor_t;
 
-sbt_desciptor_t* spherical_bessel_transform_setup(double encut, double enbuf, int lmax, int N, double* r);
+sbt_desciptor_t* spherical_bessel_transform_setup(double encut, double enbuf, int lmax, int N,
+	double* r, double* ks);
 
-double complex* wave_spherical_bessel_transform(sbt_desciptor_t* d,
+double* wave_spherical_bessel_transform(sbt_desciptor_t* d,
         double* r, double* f, double* ks, int l);
 
 #endif

### 2018-02-07 pawpyseed/utils.c

@@ -267,8 +267,8 @@ double proj_interpolate(double r, double rmax, double* x, double* proj, double**
 	return radval;
 }
 
-double wave_interpolate(double r, double* x, double* f, double** wave_spline) {
-	int ind = (int) (log(r/x[0]) / log(x[1] / x[0]));
+double wave_interpolate(double r, int size, double* x, double* f, double** wave_spline) {
+	int ind = min((int) (log(r/x[0]) / log(x[1]/x[0])), size-2);
 	double rem = r - x[ind];
 	return f[ind] + rem * (wave_spline[0][ind] + 
 				rem * (wave_spline[1][ind] +

### 2018-02-07 pawpyseed/utils.h

@@ -58,6 +58,8 @@ typedef struct proj_ae_ps {
 	double** pswave_spline;
 	double* diffwave;
 	double** diffwave_spline;
+	double* kwave;
+	double** kwave_spline;
 } funcset_t;
 
 typedef struct projgrid {
@@ -96,6 +98,7 @@ typedef struct pseudopot {
 	int wave_gridsize;
 	int num_cart_gridpts;
 	double* wave_grid;
+	double* kwave_grid;
 	double* proj_grid;
 } ppot_t;
 
@@ -153,7 +156,7 @@ double complex Ylm2(int l, int m, double costheta, double phi);
 
 double proj_interpolate(double r, double rmax, double* x, double* proj, double** proj_spline);
 
-double wave_interpolate(double r, double* x, double* f, double** wave_spline);
+double wave_interpolate(double r, int size, double* x, double* f, double** wave_spline);
 
 double complex proj_value(funcset_t funcs, double* x, int m, double rmax,
 	double* ion_pos, double* pos, double* lattice);

### 2018-02-10 pawpyseed/projector.c
tie in sbt to the main code

@@ -103,14 +103,12 @@ real_proj_site_t* projector_values(int num_sites, int* labels, double* coords,
 		sites[i].elem = labels[i];
 		sites[i].num_projs = pps[labels[i]].num_projs;
 		sites[i].rmax = pps[labels[i]].rmax;
-		sites[i].total_projs = 0;
+		sites[i].total_projs = pps[labels[i]].total_projs;
 		sites[i].num_indices = 0;
 		sites[i].coord = malloc(3 * sizeof(double));
 		sites[i].coord[0] = coords[3*i+0];
 		sites[i].coord[1] = coords[3*i+1];
 		sites[i].coord[2] = coords[3*i+2];
-		for (int j = 0; j < sites[i].num_projs; j++)
-			sites[i].total_projs += 2 * pps[labels[i]].funcs[j].l + 1;
 		sites[i].indices = calloc(pps[labels[i]].num_cart_gridpts, sizeof(int));
 		sites[i].projs = (real_proj_t*) malloc(sites[i].total_projs * sizeof(real_proj_t));
 		int p = 0;
@@ -325,11 +323,6 @@ void setup_projections(pswf_t* wf, ppot_t* pps, int num_elems,
 	for (int p = 0; p < num_elems; p++) {
 		make_pwave_overlap_matrices(pps+p);
 		add_num_cart_gridpts(pps+p, wf->lattice, fftg);
-		double* ks = (double*) malloc(pps[p].wave_gridsize * sizeof(double));
-		sbt_desciptor_t* d = spherical_bessel_transform_setup(520, 1000, 2, pps[p].wave_gridsize, pps[p].wave_grid);
-		for (int i = 0; i < pps[p].num_projs; i++)
-			wave_spherical_bessel_transform(d, pps[p].wave_grid, pps[p].funcs[i].aewave, ks, pps[p].funcs[i].l);
-		free(ks);
 	}
 	int NUM_KPTS = wf->nwk * wf->nspin;
 	int NUM_BANDS = wf->nband;
@@ -370,7 +363,7 @@ double complex** overlap_setup(pswf_t* wf_R, pswf_t* wf_S, ppot_t* pps,
 					l2 = pp2.funcs[k].l;
 					for (int m2 = -l2; m2 <= l2; m2++) {
[…]

### 2018-02-10 pawpyseed/sbt.c

@@ -95,7 +95,7 @@ double* wave_spherical_bessel_transform(sbt_desciptor_t* d,
 	MKL_LONG length = N;
 	MKL_LONG status = 0;
 
-	double complex* vals = malloc(N * sizeof(double complex));
+	double* vals = malloc(N * sizeof(double complex));
 
 	status = DftiCreateDescriptor(&handle, DFTI_DOUBLE, DFTI_COMPLEX, dim, length);
 	status = DftiCommitDescriptor(handle);

### 2018-02-10 pawpyseed/utils.c

@@ -397,7 +397,7 @@ double sph_bessel(double k, double r, int l) {
 }
 
 double complex rayexp(double* kpt, int* Gs, float complex* Cs, int l, int m,
-	int num_waves, double complex* sum_terms, double* ionp) {
+	int num_waves, double* grid, double* wave, double* spline, double* ionp) {
 
 	double complex result = 0;
 	double pvec[3] = {0,0,0};
@@ -410,14 +410,13 @@ double complex rayexp(double* kpt, int* Gs, float complex* Cs, int l, int m,
 		result += phase * Cs[w] * sum_terms[(2*l+1)*w+l+m];
 	}
 
-	return result;
+	return result * 4 * PI * cpow(I, l);
 }
 
 double complex* rayexp_terms(double* kpt, int* Gs, int num_waves,
-	int l, int wave_gridsize, double* wave_grid,
-	double* aewave, double* pswave, double* reclattice) {
+	int l, int wave_gridsize, double* grid,
+	double* wave, double* spline, double* reclattice) {
 
-	double complex phase = 4 * PI * cpow(I, l);
 	double complex ylmdir = 0;
 	double k = 0;
 	double complex* terms = (double complex*) malloc((2*l+1) * num_waves * sizeof(double complex));
@@ -431,24 +430,9 @@ double complex* rayexp_terms(double* kpt, int* Gs, int num_waves,
 		frac_to_cartesian(pvec, reclattice);
 		k = mag(pvec);
 		direction(pvec, phat);
-		for (int m = -l; m <= l; m++) {
-			ylmdir = conj(Ylm(l, m, phat[0], phat[1]));
-			double overlap = 0;
-			double dr = wave_grid[0];
-			double r = wave_grid[0];
-			for (int i = 0; i < wave_gridsize - 1; i++) {
-				r = wave_grid[i];
-				dr = wave_grid[i+1] - wave_grid[i];
-				overlap += r * sph_bessel(k, r, l) * (aewave[i]-pswave[i]) * dr/2;
-			}
-			for (int i = 1; i < wave_gridsize; i++) {
-				r = wave_grid[i];
-				dr = wave_grid[i] - wave_grid[i-1];
-				overlap += r * sph_bessel(k, r, l) * (aewave[i]-pswave[i]) * dr/2; 
-			}
-			terms[(2*l+1)*w+l+m] = ylmdir * overlap * phase;
-		}
-
[…]

### 2018-02-10 pawpyseed/utils.h

@@ -20,6 +20,7 @@ typedef struct band {
 	double complex energy;
 	float complex* Cs;
 	projection_t* projections;
+	projection_t* wave_projections;
 } band_t;
 
 typedef struct rayleigh_terms {
@@ -168,7 +169,7 @@ void frac_from_index(int index, double* coord, int* fftg);
 double sph_bessel(double k, double r, int l);
 
 double complex rayexp(double* kpt, int* Gs, float complex* Cs, int l, int m,
-	int num_waves, double complex* sum_terms, double* ionp);
+	int num_waves, double* grid, double* wave, double* spline, double* ionp);
 
 double complex* rayexp_terms(double* kpt, int* Gs, int num_waves,
 	int l, int wave_gridsize, double* wave_grid,

### 2018-02-10 pawpyseed/wavefunction.py

@@ -16,6 +16,7 @@ PAWC = CDLL(os.path.join(MODULE_DIR, "pawpy.so"))
 PAWC.read_wavefunctions.restype = POINTER(None)
 PAWC.get_projector_list.restype = POINTER(None)
 PAWC.read_wavefunctions.restype = POINTER(None)
+PAWC.overlap_setup.restype = POINTER(None)
 PAWC.compensation_terms.restype = POINTER(c_double)
 PAWC.get_occs.restype = POINTER(c_double)
 PAWC.get_nband.restype = c_int

### 2018-02-10 pawpyseed/projector.c
fixed syntax errors and removed extra number from wave grid

@@ -54,7 +54,7 @@ ppot_t* get_projector_list(int num_els, int* labels, int* ls, double* proj_grids
 			funcs[k].pswave = (double*) malloc(sizeof(double)*pps[i].wave_gridsize);
 			funcs[k].diffwave = (double*) malloc(sizeof(double)*pps[i].wave_gridsize);
 			funcs[k].l = ls[l_num];
-			if (funcs[k].l > pps[i].maxl)
+			if (funcs[k].l > pps[i].lmax)
 				pps[i].lmax = funcs[k].l;
 			pps[i].total_projs += 2 * ls[l_num] + 1;
 			l_num++;
@@ -73,7 +73,7 @@ ppot_t* get_projector_list(int num_els, int* labels, int* ls, double* proj_grids
 			funcs[k].pswave_spline = spline_coeff(pps[i].wave_grid, funcs[k].pswave, pps[i].wave_gridsize);
 			funcs[k].diffwave_spline = spline_coeff(pps[i].wave_grid, funcs[k].diffwave, pps[i].wave_gridsize);
 		}
-		sbt_desciptor_t* d = spherical_bessel_transform_setup(520, 520*4, pps[i].lmax,
+		sbt_descriptor_t* d = spherical_bessel_transform_setup(520, 520*4, pps[i].lmax,
 			pps[i].wave_gridsize, pps[i].wave_grid, pps[i].kwave_grid);
 		for (int k = 0; k < pps[i].num_projs; k++) {
 			funcs[k].kwave = wave_spherical_bessel_transform(d, pps[i].wave_grid,
@@ -81,7 +81,7 @@ ppot_t* get_projector_list(int num_els, int* labels, int* ls, double* proj_grids
 			funcs[k].kwave_spline = spline_coeff(pps[i].kwave_grid, funcs[k].kwave, pps[i].wave_gridsize);
 		}
 		for (int l = 0; l <= pps[i].lmax; l++) {
-			free(d->mult_table[i]);
+			free(d->mult_table[l]);
 		}
 		free(d->mult_table);
 		free(d);
@@ -354,6 +354,7 @@ double complex** overlap_setup(pswf_t* wf_R, pswf_t* wf_S, ppot_t* pps,
 		overlaps[i] = calloc(pp1.total_projs * pp2.total_projs, sizeof(double complex));
[…]

### 2018-02-10 pawpyseed/radial.c

@@ -20,7 +20,8 @@ double complex offsite_wave_overlap(double* coord1, double* r1, double* f1, doub
 	double r1max = r1[size1-1];
 	double r2max = r2[size2-1];
 	double dphi = PI / 30;
-	double THETA, PHI, R1, R2, costheta, dcostheta, sintheta, phi, F1, F2, integral = 0;
+	double THETA, PHI, R1, R2, costheta, dcostheta, sintheta, phi, integral = 0;
+	double complex F1, F2;
 
 	//loop over 1st coord
 	double dr = r1[0];
@@ -43,7 +44,7 @@ double complex offsite_wave_overlap(double* coord1, double* r1, double* f1, doub
 					if (R2 - fabs(temp[2]) == 0) PHI = 0;
 					else PHI = acos(temp[0] / pow(temp[0]*temp[0] + temp[1]*temp[1], 0.5));
 					if (temp[1] < 0) PHI = 2*PI - PHI;
-					F2 = wave_interpolate(R2, r2, f2, spline2) * Ylm(l2, m2, THETA, PHI);
+					F2 = wave_interpolate(R2, size2, r2, f2, spline2) * Ylm(l2, m2, THETA, PHI);
 					F1 = f1[rstep] * Ylm2(l1, m1, costheta, phi);
 					integral += conj(F1) * F2 * R1 / R2 * dr * dcostheta * dphi;
 				}
@@ -70,7 +71,7 @@ double complex offsite_wave_overlap(double* coord1, double* r1, double* f1, doub
 					if (R1 - fabs(temp[2]) == 0) PHI = 0;
 					else PHI = acos(temp[0] / pow(temp[0]*temp[0] + temp[1]*temp[1], 0.5));
 					if (temp[1] < 0) PHI = 2*PI - PHI;
-					F1 = wave_interpolate(R1, r1, f1, spline1) * Ylm(l1, m1, THETA, PHI);
+					F1 = wave_interpolate(R1, size1, r1, f1, spline1) * Ylm(l1, m1, THETA, PHI);
 					F2 = f2[rstep] * Ylm2(l2, m2, costheta, phi);
 					integral += conj(F1) * F2 * R2 / R1 * dr * dcostheta * dphi;
 				}
@@ -78,6 +79,5 @@ double complex offsite_wave_overlap(double* coord1, double* r1, double* f1, doub
 		}
 		if (rstep+1 != size2) dr = r2[rstep+1] - r2[rstep];
 	}
-
 	return integral;
 }

### 2018-02-10 pawpyseed/sbt.c

@@ -20,11 +20,11 @@ Talman, J. Computer Physics Communications 2009, 180, 332 –338.
 The code is distributed under the Standard CPC license.
 */
 
-sbt_desciptor_t* spherical_bessel_transform_setup(double encut, double enbuf, int lmax, int N,
+sbt_descriptor_t* spherical_bessel_transform_setup(double encut, double enbuf, int lmax, int N,
 	double* r, double* ks) {
 
 	setbuf(stdout, NULL);
-	sbt_desciptor_t* descriptor = (sbt_desciptor_t*) malloc(sizeof(sbt_desciptor_t));
+	sbt_descriptor_t* descriptor = (sbt_descriptor_t*) malloc(sizeof(sbt_descriptor_t));
 
 	if (lmax == 0) lmax = 1;
 	double complex** mult_table = (double complex**) malloc((lmax+1) * sizeof(double complex*));
@@ -76,7 +76,7 @@ sbt_desciptor_t* spherical_bessel_transform_setup(double encut, double enbuf, in
 	return descriptor;
 }
 
-double* wave_spherical_bessel_transform(sbt_desciptor_t* d,
+double* wave_spherical_bessel_transform(sbt_descriptor_t* d,
 	double* r, double* f, double* ks, int l) {
 
 	double kmin = d->kmin;

### 2018-02-10 pawpyseed/sbt.h

@@ -18,12 +18,12 @@ typedef struct sbt_setup {
         double dt;
         double N;
         double complex** mult_table;
-} sbt_desciptor_t;
+} sbt_descriptor_t;
 
-sbt_desciptor_t* spherical_bessel_transform_setup(double encut, double enbuf, int lmax, int N,
+sbt_descriptor_t* spherical_bessel_transform_setup(double encut, double enbuf, int lmax, int N,
 	double* r, double* ks);
 
-double* wave_spherical_bessel_transform(sbt_desciptor_t* d,
+double* wave_spherical_bessel_transform(sbt_descriptor_t* d,
         double* r, double* f, double* ks, int l);
 
 #endif

### 2018-02-10 pawpyseed/tests.c

@@ -18,17 +18,11 @@ double Ylmr(int l, int m, double theta, double phi) { return creal(Ylm(l, m, the
 
 double Ylmi(int l, int m, double theta, double phi) { return cimag(Ylm(l, m, theta, phi)); }
 
-double* real_wave_spherical_bessel_transform(sbt_desciptor_t* d,
+double* real_wave_spherical_bessel_transform(sbt_descriptor_t* d,
         double* r, double* f, double* ks, int l) {
 
-	double complex* vals = wave_spherical_bessel_transform(d, r, f, ks, l);
-	double* res = (double*) malloc(2 * d->N * sizeof(double));
-	for (int i = 0; i < d->N; i++) {
-		res[2*i] = creal(vals[i]);
-		res[2*i+1] = cimag(vals[i]);
-	}
-	free(vals);
-	return res;
+	double* vals = wave_spherical_bessel_transform(d, r, f, ks, l);
+	return vals;
 }
 
 int fft_check(char* wavecar, double* kpt_weights, int* fftg) {

### 2018-02-10 pawpyseed/tests.h

@@ -5,7 +5,7 @@
 double Ylmr(int l, int m, double theta, double phi);
 double Ylmi(int l, int m, double theta, double phi);
 
-double* real_wave_spherical_bessel_transform(sbt_desciptor_t* d,
+double* real_wave_spherical_bessel_transform(sbt_descriptor_t* d,
         double* r, double* f, double* ks, int l);
 
 int fft_check(char* wavecar, double* kpt_weights, int* fftg);

### 2018-02-10 pawpyseed/utils.c

@@ -397,7 +397,7 @@ double sph_bessel(double k, double r, int l) {
 }
 
 double complex rayexp(double* kpt, int* Gs, float complex* Cs, int l, int m,
-	int num_waves, double* grid, double* wave, double* spline, double* ionp) {
+	int num_waves, double complex* sum_terms, double* ionp) {
 
 	double complex result = 0;
 	double pvec[3] = {0,0,0};
@@ -415,12 +415,13 @@ double complex rayexp(double* kpt, int* Gs, float complex* Cs, int l, int m,
 
 double complex* rayexp_terms(double* kpt, int* Gs, int num_waves,
 	int l, int wave_gridsize, double* grid,
-	double* wave, double* spline, double* reclattice) {
+	double* wave, double** spline, double* reclattice) {
 
 	double complex ylmdir = 0;
 	double k = 0;
 	double complex* terms = (double complex*) malloc((2*l+1) * num_waves * sizeof(double complex));
 
+	double overlap = 0;
 	double pvec[3] = {0,0,0};
 	double phat[2] = {0,0};
 	for (int w = 0; w < num_waves; w++) {
@@ -430,9 +431,11 @@ double complex* rayexp_terms(double* kpt, int* Gs, int num_waves,
 		frac_to_cartesian(pvec, reclattice);
 		k = mag(pvec);
 		direction(pvec, phat);
-		ylmdir = conj(Ylm(l, m, phat[0], phat[1]));
 		overlap = wave_interpolate(k, wave_gridsize, grid, wave, spline);
-		terms[(2*l+1)*w+l+m] = ylmdir * overlap;
+		for (int m = -l; m <= l; m++) {
+			ylmdir = conj(Ylm(l, m, phat[0], phat[1]));
+			terms[(2*l+1)*w+l+m] = ylmdir * overlap;
+		}
 	}
 	return terms;
 }
@@ -447,7 +450,7 @@ void generate_rayleigh_expansion_terms(pswf_t* wf, ppot_t* pps, int num_elems) {
 			for (int j = 0; j < pp.num_projs; j++) {
 				double complex* terms = rayexp_terms(kpt->k, kpt->Gs, kpt->num_waves,
 					pp.funcs[j].l, pp.wave_gridsize, pp.wave_grid,
-					pp.funcs[j].aewave, pp.funcs[j].pswave, wf->reclattice);
[…]

### 2018-02-10 pawpyseed/utils.h

@@ -90,6 +90,7 @@ typedef struct real_proj_site {
 typedef struct pseudopot {
 	int num_projs;
 	int total_projs;
+	int lmax;
 	funcset_t* funcs;
 	double rmax;
 	double* pspw_overlap_matrix;
@@ -169,11 +170,11 @@ void frac_from_index(int index, double* coord, int* fftg);
 double sph_bessel(double k, double r, int l);
 
 double complex rayexp(double* kpt, int* Gs, float complex* Cs, int l, int m,
-	int num_waves, double* grid, double* wave, double* spline, double* ionp);
+        int num_waves, double complex* sum_terms, double* ionp);
 
 double complex* rayexp_terms(double* kpt, int* Gs, int num_waves,
-	int l, int wave_gridsize, double* wave_grid,
-	double* aewave, double* pswave, double* reclattice);
+        int l, int wave_gridsize, double* grid,
+        double* wave, double** spline, double* reclattice);
 
 void generate_rayleigh_expansion_terms(pswf_t* wf, ppot_t* pps, int num_elems);
 

### 2018-02-10 pawpyseed/wavefunction.py

@@ -97,7 +97,7 @@ class Pseudopotential:
 		corechgstr, kenstr = corechgstr.split("kinetic energy-density", 1)
 		kenstr, pspotstr = kenstr.split("pspotential", 1)
 		pspotstr, pscorechgstr = pspotstr.split("core charge-density (pseudized)", 1)
-		self.grid = self.make_nums(gridstr+' 0')
+		self.grid = self.make_nums(gridstr)
 		self.aepotential = self.make_nums(aepotstr)
 		self.aecorecharge = self.make_nums(corechgstr)
 		self.kinetic = self.make_nums(kenstr)
@@ -306,22 +306,13 @@ class Wavefunction:
 			N_RS_R, N_RS_S = [], []
 		projector_list, selfnums, selfcoords, basisnums, basiscoords = self.projector_list, self.selfnums, self.selfcoords, self.basisnums, self.basiscoords
 		"""
-		projector_list, selfnums, selfcoords, basisnums, basiscoords = self.make_c_projectors(basis)
-		
-		self.projector.setup_projections(self.pwf.wf_ptr, projector_list, len(self.cr.pps),
-			len(self.structure), numpy_to_cint(self.dim), numpy_to_cint(selfnums),
-			numpy_to_cdouble(selfcoords))
-		self.projector.setup_projections(basis.pwf.wf_ptr, projector_list, len(self.cr.pps),
-			len(basis.structure), numpy_to_cint(self.dim), numpy_to_cint(basisnums),
-			numpy_to_cdouble(basiscoords))
-		"""
 		ct = self.projector.compensation_terms(band_num, self.pwf.wf_ptr, basis.pwf.wf_ptr, projector_list, 
 			len(self.cr.pps), len(M_R), len(N_R), len(N_S), num_N_RS, numpy_to_cint(M_R), numpy_to_cint(M_S),
 			numpy_to_cint(N_R), numpy_to_cint(N_S), numpy_to_cint(N_RS_R), numpy_to_cint(N_RS_S),
 			numpy_to_cint(selfnums),
 			numpy_to_cdouble(selfcoords), numpy_to_cint(basisnums), numpy_to_cdouble(basiscoords),
 			numpy_to_cint(self.dim))
-		"""
+		
 		N_RS_R, N_RS_S = M_R, M_S
[…]

### 2018-02-10 pawpyseed/projector.c
only do offsite overlap setup once per structure

@@ -384,7 +384,7 @@ double* compensation_terms(int BAND_NUM, pswf_t* wf_proj, pswf_t* wf_ref, ppot_t
 	int num_elems, int num_M, int num_N_R, int num_N_S, int num_N_RS,
 	int* M_R, int* M_S, int* N_R, int* N_S, int* N_RS_R, int* N_RS_S,
 	int* proj_labels, double* proj_coords, int* ref_labels, double* ref_coords,
-	int* fft_grid) {
+	int* fft_grid, double complex** N_RS_overlaps) {
 
 	printf("fftg %d\n", fft_grid[0]);
 	printf("fftg %d\n", fft_grid[1]);
@@ -407,8 +407,6 @@ double* compensation_terms(int BAND_NUM, pswf_t* wf_proj, pswf_t* wf_ref, ppot_t
   0,0,0,0,  .697731914902E-01};
 
 	int l1 = 0, l2 = 0;
-	double complex** N_RS_overlaps = overlap_setup(wf_ref, wf_proj, pps, ref_labels, proj_labels,
-		ref_coords, proj_coords, N_RS_R, N_RS_S, num_N_RS);
 	double inv_sqrt_vol = pow(determinant(wf_ref->lattice), -0.5);
 
 	#pragma omp parallel for

### 2018-02-10 pawpyseed/projector.h

@@ -29,7 +29,7 @@ double* compensation_terms(int BAND_NUM, pswf_t* wf_proj, pswf_t* wf_ref, ppot_t
 	int num_elems, int num_M, int num_N_R, int num_N_S, int num_N_RS,
 	int* M_R, int* M_S, int* N_R, int* N_S, int* N_RS_R, int* N_RS_S,
 	int* proj_labels, double* proj_coords, int* ref_labels, double* ref_coords,
-	int* fft_grid);
+	int* fft_grid, double complex** N_RS_overlaps);
 
 #endif
 

### 2018-02-10 pawpyseed/wavefunction.py

@@ -285,11 +285,18 @@ class Wavefunction:
 		self.projector.setup_projections(basis.pwf.wf_ptr, projector_list, len(self.cr.pps),
 			len(basis.structure), numpy_to_cint(self.dim), numpy_to_cint(basisnums),
 			numpy_to_cdouble(basiscoords))
-		self.projector_list = projector_list
-		self.selfnums = selfnums
-		self.selfcoords = selfcoords
-		self.basiscoords = basiscoords
-		self.basisnums = basisnums
+		self.projection_data = [projector_list, selfnums, selfcoords, basis_nums, basiscoords]
+		M_R, M_S, N_R, N_S, N_RS = self.make_site_lists(basis)
+		num_N_RS, N_RS = len(N_RS), np.array(N_RS).flatten()
+		if N_RS:
+			N_RS_R, N_RS_S = zip(*N_RS)
+		else:
+			N_RS_R, N_RS_S = [], []
+		self.site_cat = [M_R, M_S, N_R, N_S, N_RS_R, N_RS_S]
+		self.offsite = self.projector.overlap_setup(basis.pwf.wf_ptr, self.pwf.wf_ptr, projector_list,
+			numpy_to_cint(basisnums), numpy_to_cint(selfnums),
+			numpy_to_cdouble(basiscoords), numpy_to_cdouble(selfcoords),
+			numpy_to_cint(N_RS_R), numpy_to_cint(N_RS_S), len(N_RS_R));
 
 	def single_band_projection(self, band_num, basis):
 		res = self.projector.pseudoprojection(basis.pwf.wf_ptr, self.pwf.wf_ptr, band_num)
@@ -298,13 +305,8 @@ class Wavefunction:
 		nspin = self.projector.get_nspin(basis.pwf.wf_ptr)
 		print("datsa", nband, nwk, nspin)
 		res = cdouble_to_numpy(res, 2*nband*nwk*nspin)
-		M_R, M_S, N_R, N_S, N_RS = self.make_site_lists(basis)
-		num_N_RS, N_RS = len(N_RS), np.array(N_RS).flatten()
-		if N_RS:
-			N_RS_R, N_RS_S = zip(*N_RS)
-		else:
-			N_RS_R, N_RS_S = [], []
[…]

### 2018-02-11 pawpyseed/memtest.c
removed mem errors, offsite term too small and rayexp to positive

@@ -141,13 +141,14 @@ void test_compensation_terms() {
 	pswf_t* wf_ref = read_wavefunctions("WAVECAR", kws);
 	pswf_t* wf_proj = read_wavefunctions("WAVECAR", kws);
 
+	double complex** overlaps = overlap_setup(wf_ref, wf_proj, pps, selfnums, selfnums, selfcoords, selfcoords, M, M, 4);
 	printf("terms\n");
 	setup_projections(wf_proj, pps, num_els, 4, fftg, selfnums, selfcoords);
 	setup_projections(wf_ref, pps, num_els, 4, fftg, selfnums, selfcoords);
 	double* terms = compensation_terms(0, wf_proj, wf_ref, pps, num_els,
-		4, 0, 0, 0, M, M, N_S, N_S, N_S, N_S, selfnums, selfcoords, selfnums, selfcoords, fftg);
+		4, 0, 0, 0, M, M, N_S, N_S, N_S, N_S, selfnums, selfcoords, selfnums, selfcoords, fftg, overlaps);
 	double* terms2 = compensation_terms(0, wf_proj, wf_ref, pps, num_els,
-		0, 4, 4, 4, N_S, N_S, M, M, M, M, selfnums, selfcoords, selfnums, selfcoords, fftg);
+		0, 4, 4, 4, N_S, N_S, M, M, M, M, selfnums, selfcoords, selfnums, selfcoords, fftg, overlaps);
 
 	free_ppot_list(pps, 1);
 	free(ls);

### 2018-02-11 pawpyseed/projector.c

@@ -339,7 +339,7 @@ void setup_projections(pswf_t* wf, ppot_t* pps, int num_elems,
 	generate_rayleigh_expansion_terms(wf, pps, num_elems);
 }
 
-double complex** overlap_setup(pswf_t* wf_R, pswf_t* wf_S, ppot_t* pps,
+void overlap_setup(pswf_t* wf_R, pswf_t* wf_S, ppot_t* pps,
 	int* labels_R, int* labels_S, double* coords_R, double* coords_S,
 	int* N_RS_R, int* N_RS_S, int num_N_RS) {
 
@@ -377,14 +377,15 @@ double complex** overlap_setup(pswf_t* wf_R, pswf_t* wf_S, ppot_t* pps,
 			tj++;
 		}
 	}
-	return overlaps;
+	printf("%p %p %p %p\n", overlaps[0], overlaps[1], overlaps[2], overlaps[3]);
+	wf_S->overlaps = overlaps;
 }
 
 double* compensation_terms(int BAND_NUM, pswf_t* wf_proj, pswf_t* wf_ref, ppot_t* pps,
 	int num_elems, int num_M, int num_N_R, int num_N_S, int num_N_RS,
 	int* M_R, int* M_S, int* N_R, int* N_S, int* N_RS_R, int* N_RS_S,
 	int* proj_labels, double* proj_coords, int* ref_labels, double* ref_coords,
-	int* fft_grid, double complex** N_RS_overlaps) {
+	int* fft_grid) {
 
 	printf("fftg %d\n", fft_grid[0]);
 	printf("fftg %d\n", fft_grid[1]);
@@ -405,6 +406,8 @@ double* compensation_terms(int BAND_NUM, pswf_t* wf_proj, pswf_t* wf_ref, ppot_t
 0,0,  -.407149241649E-01,  -.490280055892E-02,  0,
   0,0,-.490280055892E-02  ,-.955532870297E-03,  0,
   0,0,0,0,  .697731914902E-01};
+
+	double complex** N_RS_overlaps = wf_proj->overlaps;
 
 	int l1 = 0, l2 = 0;
 	double inv_sqrt_vol = pow(determinant(wf_ref->lattice), -0.5);
@@ -481,7 +484,8 @@ double* compensation_terms(int BAND_NUM, pswf_t* wf_proj, pswf_t* wf_ref, ppot_t
[…]

### 2018-02-11 pawpyseed/projector.h

@@ -21,7 +21,7 @@ void make_pwave_overlap_matrices(ppot_t* pp_ptr);
 void setup_projections(pswf_t* wf, ppot_t* pps, int num_elems,
 	int num_sites, int* fftg, int* labels, double* coords);
 
-double complex** overlap_setup(pswf_t* wf_R, pswf_t* wf_S, ppot_t* pps,
+void overlap_setup(pswf_t* wf_R, pswf_t* wf_S, ppot_t* pps,
 	int* labels_R, int* labels_S, double* coords_R, double* coords_S,
 	int* N_RS_R, int* N_RS_S, int num_N_RS);
 
@@ -29,7 +29,7 @@ double* compensation_terms(int BAND_NUM, pswf_t* wf_proj, pswf_t* wf_ref, ppot_t
 	int num_elems, int num_M, int num_N_R, int num_N_S, int num_N_RS,
 	int* M_R, int* M_S, int* N_R, int* N_S, int* N_RS_R, int* N_RS_S,
 	int* proj_labels, double* proj_coords, int* ref_labels, double* ref_coords,
-	int* fft_grid, double complex** N_RS_overlaps);
+	int* fft_grid);
 
 #endif
 

### 2018-02-11 pawpyseed/radial.c

@@ -33,7 +33,7 @@ double complex offsite_wave_overlap(double* coord1, double* r1, double* f1, doub
 			costheta = costhetas[thetastep];
 			dcostheta = dcosthetas[thetastep];
 			sintheta = pow(1 - pow(costheta, 2), 0.5);
-			for (int phistep = 0; phistep < 60; phistep++) {
+			for (int phistep = 0; phistep < 1; phistep++) {
 				phi = phistep * dphi;
 				temp[0] = R1 * sintheta * cos(phi) - dcoord[0];
 				temp[1] = R1 * sintheta * sin(phi) - dcoord[1];
@@ -60,7 +60,7 @@ double complex offsite_wave_overlap(double* coord1, double* r1, double* f1, doub
 			costheta = costhetas[thetastep];
 			dcostheta = dcosthetas[thetastep];
 			sintheta = pow(1 - pow(costheta, 2), 0.5);
-			for (int phistep = 0; phistep < 60; phistep++) {
+			for (int phistep = 0; phistep < 1; phistep++) {
 				phi = phistep * dphi;
 				temp[0] = R2 * sintheta * cos(phi) + dcoord[0];
 				temp[1] = R2 * sintheta * sin(phi) + dcoord[1];

### 2018-02-11 pawpyseed/utils.h

@@ -47,6 +47,7 @@ typedef struct pswf {
 	int nwk;
 	double* lattice;
 	double* reclattice;
+	double complex** overlaps;
 } pswf_t;
 
 typedef struct proj_ae_ps {

### 2018-02-11 pawpyseed/wavefunction.py

@@ -16,7 +16,7 @@ PAWC = CDLL(os.path.join(MODULE_DIR, "pawpy.so"))
 PAWC.read_wavefunctions.restype = POINTER(None)
 PAWC.get_projector_list.restype = POINTER(None)
 PAWC.read_wavefunctions.restype = POINTER(None)
-PAWC.overlap_setup.restype = POINTER(None)
+PAWC.overlap_setup.restype = None
 PAWC.compensation_terms.restype = POINTER(c_double)
 PAWC.get_occs.restype = POINTER(c_double)
 PAWC.get_nband.restype = c_int
@@ -106,8 +106,8 @@ class Pseudopotential:
 
 		for pwave in partial_waves:
 			lst = pwave.split("ae wavefunction", 1)
-			self.pswaves.append(self.make_nums(lst[0]+' 0'))
-			self.aewaves.append(self.make_nums(lst[1]+' 0'))
+			self.pswaves.append(self.make_nums(lst[0]))
+			self.aewaves.append(self.make_nums(lst[1]))
 
 		projstrs = nonradial.split("Non local Part")
 		topstr, projstrs = projstrs[0], projstrs[1:]
@@ -285,7 +285,7 @@ class Wavefunction:
 		self.projector.setup_projections(basis.pwf.wf_ptr, projector_list, len(self.cr.pps),
 			len(basis.structure), numpy_to_cint(self.dim), numpy_to_cint(basisnums),
 			numpy_to_cdouble(basiscoords))
-		self.projection_data = [projector_list, selfnums, selfcoords, basis_nums, basiscoords]
+		self.projection_data = [projector_list, selfnums, selfcoords, basisnums, basiscoords]
 		M_R, M_S, N_R, N_S, N_RS = self.make_site_lists(basis)
 		num_N_RS, N_RS = len(N_RS), np.array(N_RS).flatten()
 		if N_RS:
@@ -293,10 +293,11 @@ class Wavefunction:
 		else:
 			N_RS_R, N_RS_S = [], []
 		self.site_cat = [M_R, M_S, N_R, N_S, N_RS_R, N_RS_S]
-		self.offsite = self.projector.overlap_setup(basis.pwf.wf_ptr, self.pwf.wf_ptr, projector_list,
[…]

### 2018-02-13 pawpyseed/projector.c
sbt tail and nonfast sbt

@@ -77,6 +77,7 @@ ppot_t* get_projector_list(int num_els, int* labels, int* ls, double* proj_grids
 			pps[i].wave_gridsize, pps[i].wave_grid, pps[i].kwave_grid);
 		for (int k = 0; k < pps[i].num_projs; k++) {
 			funcs[k].kwave = wave_spherical_bessel_transform(d, funcs[k].diffwave, funcs[k].l);
+			//funcs[k].kwave = besselt(pps[i].wave_grid, pps[i].kwave_grid, funcs[k].diffwave, 520.0, pps[i].wave_gridsize, funcs[k].l);
 			funcs[k].kwave_spline = spline_coeff(pps[i].kwave_grid, funcs[k].kwave, pps[i].wave_gridsize);
 		}
 		for (int l = 0; l <= pps[i].lmax; l++) {
@@ -87,6 +88,25 @@ ppot_t* get_projector_list(int num_els, int* labels, int* ls, double* proj_grids
 		pps[i].funcs = funcs;
 	}
 	return pps;
+}
+
+double* besselt(double* r, double* k, double* f, double encut, int N, int l) {
+	
+	double kmax = pow(encut*c, 0.5);
+	double drho = log(r[1]/r[0]);
+	double kmin = kmax * exp((1-N)*drho);
+	double* g = (double*) malloc(N*sizeof(double));
+	for (int i = 0; i < N; i++) {
+		double dr = r[0];
+		g[i] = 0;
+		k[i] = kmin * exp(i*drho);
+		for (int j = 0; j < N; j++) {
+			g[i] += f[j] * r[j] * sph_bessel(k[i], r[j], l) * dr; 
+			if (j != N-1) dr = r[j+1]-r[j];
+		}
+	}
+	return g;
+
 }
 
 real_proj_site_t* projector_values(int num_sites, int* labels, double* coords,
@@ -454,12 +474,14 @@ double* compensation_terms(int BAND_NUM, pswf_t* wf_proj, pswf_t* wf_ref, ppot_t
 			ppot_t pp = pps[ref_labels[N_R[s]]];
 			for (int i = 0; i < pp.num_projs; i++) {
 				for (int m = -pp.funcs[i].l; m <= pp.funcs[i].l; m++) {
-					temp += rayexp(wf_proj->kpts[w%NUM_KPTS]->k, wf_proj->kpts[w%NUM_KPTS]->Gs,
[…]

### 2018-02-13 pawpyseed/projector.h

@@ -31,5 +31,7 @@ double* compensation_terms(int BAND_NUM, pswf_t* wf_proj, pswf_t* wf_ref, ppot_t
 	int* proj_labels, double* proj_coords, int* ref_labels, double* ref_coords,
 	int* fft_grid);
 
+double* besselt(double* r, double* k, double* f, double encut, int N, int l);
+
 #endif
 

### 2018-02-13 pawpyseed/sbt.c

@@ -35,14 +35,16 @@ sbt_descriptor_t* spherical_bessel_transform_setup(double encut, double enbuf, i
 	double rhomin = log(r[0]);
 	double dt = 2 * PI / N / drho;
 	double rmin = r[0];
-	double kmin = pow((encut+enbuf) * c, 0.5) * exp(-(N-1) * drho);
+	double kmin = pow((encut+enbuf) * c, 0.5) * exp(-(N/2-1) * drho);
 	double kappamin = log(kmin);
-	for (int i = 0; i < N; i++)
+	for (int i = 0; i < N; i++) {
 		ks[i] = kmin * exp(i*drho);
 		rs[i] = rmin * exp((i-N/2)*drho);
+	}
 	for (int i = 0; i < N/2; i++) {
 		inpks[i] = ks[i];
 	}
+	rhomin = log(rs[0]);
 	mult_table[0] = (double complex*) calloc(N, sizeof(double complex));
 	mult_table[1] = (double complex*) calloc(N, sizeof(double complex));
 	for (int i = 2; i <= lmax; i++)
@@ -138,7 +140,7 @@ double* wave_spherical_bessel_transform(sbt_descriptor_t* d, double* f, int l) {
 	status = DftiComputeBackward(handle, x);
 	printf("status %ld\n", status);
 	double kp = 0;
-	for (int p = 0; p < N/2; p++) {
+	for (int p = 0; p < N / 2; p++) {
 		kp = kmin * exp(p * drho);
 		vals[p] = x[p].real;
 		vals[p] *= 2 / pow(ks[p], 1.5);

### 2018-02-13 pawpyseed/projector.c
refactoring linear overlap term

@@ -344,6 +344,50 @@ void overlap_setup(pswf_t* wf_R, pswf_t* wf_S, ppot_t* pps,
 
 	double complex** overlaps = (double complex**) malloc(num_N_RS * sizeof(double complex*));
 
+	int NUM_KPTS = wf->nwk * wf->nspin;
+	int NUM_BANDS = wf->nband;
+	for (int w = 0; w < NUM_BANDS * NUM_KPTS; w++) {
+		projection_t* wps = (projection_t*) malloc(num_N_R * sizeof(projection_t));
+		for (int m = 0; m < num_N_R; i++) {
+			int s = N_R[m];
+			ppot_t pp = pps[labels_R[s]];
+			wps[m]->overlaps = (double complex*) malloc(pp.total_projs * sizeof(double complex));
+			int t = 0;
+			for (int i = 0; i < pp.total_projs; i++) {
+				for (int m = -pp.funcs[i].l; m <= pp.funcs[i].l; m++) {
+					wps[m].overlaps[i] = rayexp(wf_proj->kpts[w%NUM_KPTS]->k, wf_proj->kpts[w%NUM_KPTS]->Gs,
+						wf_proj->kpts[w%NUM_KPTS]->bands[w/NUM_KPTS]->Cs, pp.funcs[i].l, m,
+						wf_proj->kpts[w%NUM_KPTS]->num_waves,
+						wf_ref->kpts[w%NUM_KPTS]->expansion[labels_R[s]][i].terms,
+						coords_R + s*3) * inv_sqrt_vol;
+					t++;
+				}
+			}
+		}
+		wf_proj->kpts[w%NUM_KPTS]->bands[w/NUM_KPTS]->wave_projections = wps;
+	}
+
+	for (int w = 0; w < NUM_BANDS * NUM_KPTS; w++) {
+		projection_t* wps = (projection_t*) malloc(num_N_S * sizeof(projection_t));
+		for (int m = 0; m < num_N_S; i++) {
+			int s = N_S[m];
+			ppot_t pp = pps[labels_S[s]];
+			wps[m]->overlaps = (double complex*) malloc(pp.total_projs * sizeof(double complex));
+			int t = 0;
+			for (int i = 0; i < pp.total_projs; i++) {
+				for (int m = -pp.funcs[i].l; m <= pp.funcs[i].l; m++) {
[…]

### 2018-02-14 pawpyseed/projector.c
MOSTLY WORKING CROSS TERMS (orthogonality not quite on point, but assuming for now that's numerical errors); fixed offsite indexing and rayexp phase

@@ -73,12 +73,13 @@ ppot_t* get_projector_list(int num_els, int* labels, int* ls, double* proj_grids
 			funcs[k].pswave_spline = spline_coeff(pps[i].wave_grid, funcs[k].pswave, pps[i].wave_gridsize);
 			funcs[k].diffwave_spline = spline_coeff(pps[i].wave_grid, funcs[k].diffwave, pps[i].wave_gridsize);
 		}
-		sbt_descriptor_t* d = spherical_bessel_transform_setup(520, 0, pps[i].lmax,
+		sbt_descriptor_t* d = spherical_bessel_transform_setup(520.0, 5000.0, pps[i].lmax,
 			pps[i].wave_gridsize, pps[i].wave_grid, pps[i].kwave_grid);
 		for (int k = 0; k < pps[i].num_projs; k++) {
 			funcs[k].kwave = wave_spherical_bessel_transform(d, funcs[k].diffwave, funcs[k].l);
 			//funcs[k].kwave = besselt(pps[i].wave_grid, pps[i].kwave_grid, funcs[k].diffwave, 520.0, pps[i].wave_gridsize, funcs[k].l);
 			funcs[k].kwave_spline = spline_coeff(pps[i].kwave_grid, funcs[k].kwave, pps[i].wave_gridsize);
+			printf("KVAL %lf\n", wave_interpolate(0.7, 387, pps[i].kwave_grid, funcs[k].kwave, funcs[k].kwave_spline));
 		}
 		for (int l = 0; l <= pps[i].lmax; l++) {
 			free(d->mult_table[l]);
@@ -360,52 +361,53 @@ void setup_projections(pswf_t* wf, ppot_t* pps, int num_elems,
 
 void overlap_setup(pswf_t* wf_R, pswf_t* wf_S, ppot_t* pps,
 	int* labels_R, int* labels_S, double* coords_R, double* coords_S,
-	int* N_RS_R, int* N_RS_S, int num_N_RS) {
+	int* N_R, int* N_S, int* N_RS_R, int* N_RS_S, int num_N_R, int num_N_S, int num_N_RS) {
 
 	double complex** overlaps = (double complex**) malloc(num_N_RS * sizeof(double complex*));
 
-	int NUM_KPTS = wf->nwk * wf->nspin;
[…]

### 2018-02-14 pawpyseed/projector.h

@@ -22,8 +22,8 @@ void setup_projections(pswf_t* wf, ppot_t* pps, int num_elems,
 	int num_sites, int* fftg, int* labels, double* coords);
 
 void overlap_setup(pswf_t* wf_R, pswf_t* wf_S, ppot_t* pps,
-	int* labels_R, int* labels_S, double* coords_R, double* coords_S,
-	int* N_RS_R, int* N_RS_S, int num_N_RS);
+        int* labels_R, int* labels_S, double* coords_R, double* coords_S,
+        int* N_R, int* N_S, int* N_RS_R, int* N_RS_S, int num_N_R, int num_N_S, int num_N_RS);
 
 double* compensation_terms(int BAND_NUM, pswf_t* wf_proj, pswf_t* wf_ref, ppot_t* pps,
 	int num_elems, int num_M, int num_N_R, int num_N_S, int num_N_RS,

### 2018-02-14 pawpyseed/utils.c

@@ -405,13 +405,13 @@ double complex rayexp(double* kpt, int* Gs, float complex* Cs, int l, int m,
 	double pvec[3] = {0,0,0};
 	double complex phase = 0;
 	for (int w = 0; w < num_waves; w++) {
-		pvec[0] = kpt[0] + Gs[3*w+0];
-		pvec[1] = kpt[1] + Gs[3*w+1];
-		pvec[2] = kpt[2] + Gs[3*w+2];
+		pvec[0] = Gs[3*w+0];
+		pvec[1] = Gs[3*w+1];
+		pvec[2] = Gs[3*w+2];
 		phase = cexp(2*PI*I*dot(ionp, pvec));
 		result += phase * Cs[w] * sum_terms[(2*l+1)*w+l+m];
 	}
-
+	printf ("ISSUE? %lf %lf\n", creal(cpow(I,l)), cimag(cpow(I,l)));
 	return result * 4 * PI * cpow(I, l);
 }
 
@@ -432,10 +432,9 @@ double complex* rayexp_terms(double* kpt, int* Gs, int num_waves,
 		pvec[1] = kpt[1] + Gs[3*w+1];
 		pvec[2] = kpt[2] + Gs[3*w+2];
 		frac_to_cartesian(pvec, reclattice);
-		if (l == 0) printf("PVECART %lf %lf %lf\n", pvec[0], pvec[1], pvec[2]);
+		//if (l == 0) printf("PVECART %lf %lf %lf\n", pvec[0], pvec[1], pvec[2]);
 		k = mag(pvec);
 		direction(pvec, phat);
-		printf("DIRECTION %lf %lf\n", phat[0], phat[1]);
 		overlap = wave_interpolate(k, wave_gridsize, grid, wave, spline);
 		for (int m = -l; m <= l; m++) {
 			ylmdir = conj(Ylm(l, m, phat[0], phat[1]));

### 2018-02-14 pawpyseed/paper.tex

--- 2018-01-23 docs/paper.tex
@@
 \section*{Appendix B: Comprehensive POTCAR Guide}
-The PAWpySeed module makes use of the POTCAR files provided with the VASP source code, which
-contain the projector functions, partial waves, pseudopotentials, and core charge densities
-for each element. The format of the POTCAR file is not intuitive to non-developers, so this
-appendix seeks to comprehensively document the format of the VASP POTCAR files.
-
-\subsection*{Overview}
-A single POTCAR contains the data for one element; a POTCAR file to a multi-element system
-is made by simply concatenating elemental POTCAR files. Each PAW POTCAR file follows
-the following format.
-
-\begin{enumerate}
-	\item
-	Settings
-	\item
-	adsf
-	\item
-	\textbf{Non local Part}: This section contains the \emph{non local projector functions}.
-	The first line after "Non local Part" gives the $l$ quantum number of the projector,
-	the number of projectors for that $l$ quantum number, and the radius of the real
-	space projector region.
-	\begin{enumerate}
-		\item
-		\textbf{Reciprocal Space Part}: The reciprocal space projection operator.
-		\item
-		\textbf{Real Space Part}: The real space projection operator values on a radial
-		grid. The radius at a given index $I$ is $RMAX*I/NDATA$, where RMAX and NDATA
-		are given in the settings section. Since $I$ is 0-indexed, the true maximal
-		radius of the projector is actually $RMAX*(NDATA-1)/NDATA$. Unlike the
-		\emph{partial wave} values (see \textbf{pseudo wavefunction},
-		the projector values are not mulitplied by $r$.
-		$$p(\mathbf{r})=realspacepart(index)Y_l^m(\hat{\mathbf{r}})$$
-	\end{enumerate}
-	\item
-	PAW Radial Sets
-	\begin{enumerate}
-		\item
-		Augmentation charges
-		\item
-		Occupancies
-		\item
-		\textbf{grid}: The exponential grid on which calculations related
-		to the \emph{partial waves} are performed.
-		\item
-		\textbf{pseudo wavefunction}: A pseudo \emph{partial wave} on the provided
-		radial grid, multiplied by $r$ for easy radial integration. I.e.
-		$$\phi(\mathbf{r}(index))=\frac{pseudowavefunction(index)}{r(index)}Y_l^m(\hat{\mathbf{r}})$$
-		Listed in the same order as the projector functions.
-		\item
-		\textbf{ae wavefunction}: Same pseudo wavefunction, but for the all electron \emph{partial wave}.
-	\end{enumerate}
-\end{enumerate}
-
-\subsection*{}
 

### 2018-02-14 pawpyseed/projector.c
set N_RS_overlaps to diff overlaps for testing

@@ -411,6 +411,8 @@ void overlap_setup(pswf_t* wf_R, pswf_t* wf_S, ppot_t* pps,
 	}
 
 	int l1, l2;
+	double dummy[3] = {0};
+	double R = 0;
 	for (int i = 0; i < num_N_RS; i++) {
 		int s1 = N_RS_R[i];
 		int s2 = N_RS_S[i];
@@ -419,6 +421,7 @@ void overlap_setup(pswf_t* wf_R, pswf_t* wf_S, ppot_t* pps,
 		overlaps[i] = calloc(pp1.total_projs * pp2.total_projs, sizeof(double complex));
 		double* coord1 = coords_R + 3 * s1;
 		double* coord2 = coords_S + 3 * s2;
+		min_cart_path(coord1, coord2, dummy, &R);
 		printf("herewego %lf %lf %lf\nherewego%lf %lf %lf\n", coord1[0], coord1[1], coord1[2], coord2[0], coord2[1], coord2[2]);
 		int tj = 0;
 		for (int j = 0; j < pp1.num_projs; j++) {
@@ -428,13 +431,17 @@ void overlap_setup(pswf_t* wf_R, pswf_t* wf_S, ppot_t* pps,
 				for (int k = 0; k < pp2.num_projs; k++) {
 					l2 = pp2.funcs[k].l;
 					for (int m2 = -l2; m2 <= l2; m2++) {
-						overlaps[i][tj*pp2.total_projs+tk] =
-							offsite_wave_overlap(coord1, pp1.wave_grid,
-							pp1.funcs[j].diffwave,
-							pp1.funcs[j].diffwave_spline, pp1.wave_gridsize,
-							coord2, pp2.wave_grid, pp2.funcs[k].diffwave,
-							pp2.funcs[k].diffwave_spline, pp2.wave_gridsize,
-							wf_R->lattice, l1, m1, l2, m2);
+						if (R > 0.001) {
+							overlaps[i][tj*pp2.total_projs+tk] =
+								offsite_wave_overlap(coord1, pp1.wave_grid,
+								pp1.funcs[j].diffwave,
+								pp1.funcs[j].diffwave_spline, pp1.wave_gridsize,
+								coord2, pp2.wave_grid, pp2.funcs[k].diffwave,
+								pp2.funcs[k].diffwave_spline, pp2.wave_gridsize,
+								wf_R->lattice, l1, m1, l2, m2);
[…]

### 2018-02-14 pawpyseed/projector.c
ACTUALLY WORKING CROSS TERMS

@@ -421,7 +421,7 @@ void overlap_setup(pswf_t* wf_R, pswf_t* wf_S, ppot_t* pps,
 		overlaps[i] = calloc(pp1.total_projs * pp2.total_projs, sizeof(double complex));
 		double* coord1 = coords_R + 3 * s1;
 		double* coord2 = coords_S + 3 * s2;
-		min_cart_path(coord1, coord2, dummy, &R);
+		min_cart_path(coord1, coord2, wf_R->lattice, dummy, &R);
 		printf("herewego %lf %lf %lf\nherewego%lf %lf %lf\n", coord1[0], coord1[1], coord1[2], coord2[0], coord2[1], coord2[2]);
 		int tj = 0;
 		for (int j = 0; j < pp1.num_projs; j++) {
@@ -486,18 +486,25 @@ double* compensation_terms(int BAND_NUM, pswf_t* wf_proj, pswf_t* wf_ref, ppot_t
 
 	#pragma omp parallel for
 	for (int w = 0; w < NUM_BANDS * NUM_KPTS; w++) {
+		projection_t pro = wf_ref->kpts[w%NUM_KPTS]->bands[w/NUM_KPTS]->projections[0];
+		projection_t ppro = wf_proj->kpts[w%NUM_KPTS]->bands[BAND_NUM]->projections[0];
+                printf("CHECKVAL1 %lf %lf %lf %lf\n", creal(pro.overlaps[0]), cimag(pro.overlaps[0]),
+                        creal(ppro.overlaps[0]), cimag(ppro.overlaps[0]));
 		double complex temp = 0 + 0 * I;
 		int t = 0;
 		for (int s = 0; s < num_M; s++) {
+			//REMEMBER THAT M_R[s] and M_S[s] ARE NOT ALWAYS THE SAME!!!
+			//FIX THIS!!! please :)
 			ppot_t pp = pps[ref_labels[M_R[s]]];
 			int site_num = M_R[s];
-			//printf("site num %d\n", site_num);
-			//printf("kpt band %d %d", w%NUM_KPTS, w/NUM_KPTS);
 			kpoint_t* tmpk = wf_ref->kpts[w%NUM_KPTS];
 			band_t* tmpb = tmpk->bands[w/NUM_KPTS];
 			projection_t* tmpp = tmpb->projections;
 			projection_t pron = tmpp[site_num];
[…]

### 2018-03-06 docs/paper.tex
tie in sbt to the main code
update paper with additional info and revisions

--- 2018-01-23 docs/paper.tex
@@
 \newcommand{\ind}{lm\epsilon}
+
+\title{PAWpySeed: A parallelized Python/C package for analyzing
+DFT wavefunctions in the PAW formalism}
+\author{Kyle Bystrom\\
+        kylebystrom@berkeley.edu\\
+		UC Berkeley Department of Materials Science and Engineering}
+\date{\today}
+\maketitle
+\abstract{A parallelized Python and C package has been developed
+to perform analysis of density functional theory (DFT) wavefunctions in the
+projector augmented wave (PAW) formalism. The primary function of this code
+is to calculate the overlap operator of two single-particle Kohn-Sham states
+from different periodic structures with the same lattice, which is made nontrivial
+by the depency of PAW augmentation regions on the basis of the structure.
+The code is potentially useful for the analysis of point defect levels in
+solids because it can determine the composition of defect levels in the basis
+of the single-particle states of the bulk system.}
 
@@
 as a weakly perturbed host state. Such an understanding of defect levels could help select
-corrections to perform on the defect system.\ref{eq:1}
+corrections to perform on the defect system.\cite{lany}
 \begin{equation}
@@
 \begin{split}
-\braket{\psi_{Rn_1\mathbf{k}}|\psi_{Sn_2\mathbf{k}}}=\widetilde{O}+O_M+O_R+O_S+O_N\\
-O_M=\sum_{a\in M_{RS}}\sum_{l,m}\sum_{\epsilon_1}\sum_{\epsilon_2}
+\braket{\psi_{Rn_1\mathbf{k}}|\psi_{Sn_2\mathbf{k}}} & =\widetilde{O}+O_M+O_R+O_S+O_N\\
+O_M & =\sum_{a\in M_{RS}}\sum_{l,m}\sum_{\epsilon_1}\sum_{\epsilon_2}
 \braket{\widetilde{\psi}_{Rn_1\mathbf{k}}|\widetilde{p}_{a\ind _1}}
@@
 \braket{\widetilde{p}_{a\ind _2}|\widetilde{\psi}_{Sn_2\mathbf{k}}}\\
-O_R=\sum_{i\in N_R}\braket{\widetilde{\psi}_{Rn_1\mathbf{k}}|\widetilde{p}_i}
+O_R & =\sum_{i\in N_R}\braket{\widetilde{\psi}_{Rn_1\mathbf{k}}|\widetilde{p}_i}
 (\bra{\phi_i}-\bra{\widetilde{\phi}_i})
 \ket{\widetilde{\psi}_{Sn_2\mathbf{k}}}\\
-O_S=\sum_{j\in N_S}\bra{\widetilde{\psi}_{Rn_1\mathbf{k}}}(\ket{\phi_j}-\ket{\widetilde{\phi}_j})
+O_S & =\sum_{j\in N_S}\bra{\widetilde{\psi}_{Rn_1\mathbf{k}}}(\ket{\phi_j}-\ket{\widetilde{\phi}_j})
 \braket{\widetilde{p}_j|\widetilde{\psi}_{Sn_2\mathbf{k}}}\\
-O_N=\sum_{i,j\in N_{RS}}\braket{\widetilde{\psi}_{Rn_1\mathbf{k}}|
+O_N & =\sum_{i,j\in N_{RS}}\braket{\widetilde{\psi}_{Rn_1\mathbf{k}}|
 \widetilde{p}_i}(\bra{\phi_i}-\bra{\widetilde{\phi}_i})
@@
 
+\begin{table}
+\centering
+\begin{tabular}{|c|c|c|}
+\hline
+Computational Task & $\Theta$ & Frequency*\\
+\hline
+$\widetilde{O}$ & $BKSW$ & per band\\
+$O_M$ & $BKSNP$ & per band\\
+$O_R$ and $O_S$ & $BKSNP$ & per band\\
+$O_N$ & $BKSNP$ & per band\\
+$\braket{\widetilde{p}_i|\widetilde{\psi}_{n\mathbf{k}}}$ & $BKSF\mathrm{log}(F)$ & per structure\\
+$(\bra{\phi_i}-\bra{\widetilde{\phi}_i})
+\ket{\widetilde{\psi}_{n\mathbf{k}}}$ & $BKSNPW$ & per structure\\
+spherical Bessel transform partial waves & $NPG\mathrm{log}(G)$ & per structure pair\\
+project plane waves onto partial waves & $EPKW$ & per structure pair\\
+projections for overlapping aug spheres & $NPL$ & per structure pair\\
+\hline
+\end{tabular}
+
+\begin{tabular}{c|c}
+Symbol & Definition\\
+\hline
+B & number of bands\\
+E & number of elements\\
+F & size of FFT grid\\
+G & size of partial wave radial grid\\
+K & number of k-points\\
+L & size of Legendre-Gauss grid around ions\\
+N & number of sites**\\
+P & number of projector functions\\
+S & number of spin states\\
+W & number of plane waves\\
+\end{tabular}
+\caption{Runtime scaling functions for each component of the code and
+definitions for shorthand symbols to express runtime.
+*The frequency refers to how often the routine is called. "Per band"
+indicates that the routine runs once every time a band from one structure
+is projected onto all the bands of a basis structure. "Per structure"
+indicates that the routine is a "setup" routine that must be called once
+for each structure and corresponding band structure to do perform projections.
+"Per structure pair" is the same as "per structure" except that the routine
+is only run once for a pair of structures with the same lattice and plane-wave
+basis set, the bands of one such structure to be used as a basis set for the other.
+**Number of sites flexibly refers to the number of sites relevant to the calculation,
+which worst-case scales with the total number of sites in the structure. For example,
+calculating $O_M$ and $O_N$ only require the sites in sets $M$ and $N_RS$, respectively.}
+\label{tab:runtime}
+\end{table}
+
+The program is implemented as a Python package that interfaces with C functions through
+the Python ctypes package. Time consuming routines are performed in C and parallelized
+using openmp, meaning that the code will automatically parallelize on all the resources
+of a shared memory computing node. Detailed runtime scaling for each routine is
+provided in Table \ref{tab:runtime}. An explanation of how each term is calculated
+so as to maximize computational efficiency is summarized in the following subsections.
+
+\subsection{Projection of Pseudowavefunctions onto Partial Waves}
+
+The all electron partial waves fluctuate rapidly near the nucleus,
+so the pseudowavefunction cannot be projected onto the partial waves
+via a uniform Cartesian grid as is doen with the projector functions.
+However, A plane wave can be expanded as a sum of spherical
+Bessel functions via Rayleigh expansion.
+\begin{equation}
+e^{i\mathbf{k} \cdot \mathbf{r}} = 4\pi \sum_{l=0}^{\infty}\sum_{m=-l}^{l}
+i^l j_l(kr)Y_l^{m*}(\mathbf{\hat{k}})Y_l^m(\mathbf{\hat{r}})
+\label{eq:pwexp}
+\end{equation}
+Therefore, the overlap operator between a partial wave and plane wave can be evaluated as a summation
+of spherical Bessel function overlap integrals. The following definitions are
+used in this derivation:
+
+$\mathbf{r_A} = \mathbf{r} - \mathbf{R_A}$, $\phi_i(\mathbf{r})=R_i(r)Y_l^m(\mathbf{\hat{r}})$,
+$\widetilde{\phi}_i(\mathbf{r})=\widetilde{R}_i(r)Y_l^m(\mathbf{\hat{r}})$,
+$\mathbf{k'}=\mathbf{k}+\mathbf{G}$\\
+The derivation goes as follows, with the last line being that needed to 
+calculate $O_R$ and $O_S$:
+
+\begin{equation}
+\begin{split}
+\widetilde{\psi}_{n\mathbf{k}} & =\frac{1}{\sqrt{V}}\sum_{\mathbf{G}}
+C_{n\mathbf{k}\mathbf{G}}e^{i\mathbf{k'}\cdot \mathbf{r}}\\
+\widetilde{\psi}_{n\mathbf{k}} & =\frac{4\pi}{\sqrt{V}}\sum_{\mathbf{G}}
+C_{n\mathbf{k}\mathbf{G}}\sum_{l=0}^{\infty}\sum_{m=-l}^{l}
+i^l j_l(k'r_A)Y_l^{m*}(\mathbf{\hat{k'}})Y_l^m(\mathbf{\hat{r}_A})\\
+\phi_i(\mathbf{r})\widetilde{\psi}_{n\mathbf{k}} & =\frac{4\pi}{\sqrt{V}}\sum_{\mathbf{G}}
+C_{n\mathbf{k}\mathbf{G}}\sum_{l'=0}^{\infty}\sum_{m'=-l'}^{l'}
+i^{l'} j_{l'}(k'r_A)Y_{l'}^{m'*}(\mathbf{\hat{k'}})Y_{l'}^{m'}(\mathbf{\hat{r}_A})
+Y_l^{m*}(\mathbf{\hat{r}}_A)R_i(r_A)\\
+\braket{\phi_i(\mathbf{r})|\widetilde{\psi}_{n\mathbf{k}}} & =
+\frac{4\pi i^l}{\sqrt{V}}\sum_{\mathbf{G}} C_{n\mathbf{k}\mathbf{G}}
+Y_l^{m*}(\mathbf{\hat{k'}})\int_0^{\infty}drr^2R_i(r_A)j_l(k'r_A)\\
+\braket{\phi_i-\widetilde{\phi}_i|\widetilde{\psi}_{n\mathbf{k}}} & =
+\frac{4\pi i^l}{\sqrt{V}}\sum_{\mathbf{G}} C_{n\mathbf{k}\mathbf{G}}
+Y_l^{m*}(\mathbf{\hat{k'}})\int_0^{\infty}drr^2(R_i(r_A)-\widetilde{R}_i(r_A))j_l(k'r_A)
+\end{split}
+\end{equation}
+
+After the projection is decomposed into a summation over integrals of spherical
+Bessel functions, it can be calculated via spherical Bessel transform. This code
+uses the fast spherical Bessel transform method NumSBT developed by Talman.\cite{TALMAN}
+It runs in $O(NlnN)$ time and works on a logarithmic grid, making it convenient for use with
+the POTCAR representations of the partial waves. The resulting logarithmic k-space
+grid can be used to calculate the values of the relevant integrals via interpolation.
+
 \section*{Appendix A: Derivation of Overlap Operators from PAW Formalism}
+
+The following section derives an equation for the overlap operator between one
+Kohn-Sham single particle state of one structure R and one Kohn-Sham single
+particle state of another structure S, where R and S share a common lattice
+and the DFT wavefunctions are constructed with the same plane-wave PAW basis set.
+It should be noted this derivation might better be described as a manipulation
+of terms of the PAW pseudo-operator, because its main purpose is to present
+the overlap operator in a method convenient for computation rather than to derive
+an entirely new expression. The derivation also makes particular note of how
+the expression of the overlap operator relates to interfacing with the VASP code,
+though the expressions are applicable to any PAW code.
+
 The starting point for this derivation is the transformation operator that
@@
 and construction of the partial waves and projector functions, see Blochl's original paper
-and Kresse and Joubert's paper relating ultrasoft pseudopotentials and PAW.\cite{blochl}
-The next step is to define and pseudo operator $\widetilde{A}$ for each operator $A$
+and Kresse and Joubert's paper relating ultrasoft pseudopotentials and PAW.\cite{blochl,kresse_joubert}
+The next step is to define a pseudo operator $\widetilde{A}$ for each operator $A$
 such that $\bra{\psi}A\ket{\psi}=\bra{\widetilde{\psi}}\widetilde{A}\ket{\widetilde{\psi}}$.
@@
 One can then plug Equation \ref{eq:T} into Equation \ref{eq:op} to find
-$$\widetilde{A}=[1+\sum_i\ket{\widetilde{p}_i}(\bra{\phi_i}-\bra{\widetilde{\phi}_i})]
+\begin{equation}
+\begin{split}
+\widetilde{A} = & [1+\sum_i\ket{\widetilde{p}_i}(\bra{\phi_i}-\bra{\widetilde{\phi}_i})]
 A[1+\sum_j(\ket{\phi_j}-\ket{\widetilde{\phi}_j})
-\bra{\widetilde{p}_j}]$$
-\begin{equation}
-\widetilde{A}=A+\sum_i\ket{\widetilde{p}_i}(\bra{\phi_i}-\bra{\widetilde{\phi}_i})A
-+\sum_j A(\ket{\phi_j}-\ket{\widetilde{\phi}_j})\bra{\widetilde{p}_j}
-+\sum_i\sum_j\ket{\widetilde{p}_i}(\bra{\phi_i}-\bra{\widetilde{\phi}_i})A
+\bra{\widetilde{p}_j}]\\
+\widetilde{A} = & A+\sum_i\ket{\widetilde{p}_i}(\bra{\phi_i}-\bra{\widetilde{\phi}_i})A
++\sum_j A(\ket{\phi_j}-\ket{\widetilde{\phi}_j})\bra{\widetilde{p}_j}\\
+& +\sum_i\sum_j\ket{\widetilde{p}_i}(\bra{\phi_i}-\bra{\widetilde{\phi}_i})A
 (\ket{\phi_j}-\ket{\widetilde{\phi}_j})\bra{\widetilde{p}_j}
+\end{split}
 \label{eq:res}
 \end{equation}
+
 Using the following relation,
-$$(\bra{\phi_i}-\bra{\widetilde{\phi}_i})A(\ket{\phi_j}-\ket{\widetilde{\phi}_j})
-=\bra{\phi_i}A\ket{\phi_j}-\bra{\widetilde{\phi}_i}A\ket{\phi_j}
--(\bra{\phi_i}-\bra{\widetilde{\phi}_i})A\ket{\widetilde{\phi}_j}$$
-$$=\bra{\phi_i}A\ket{\phi_j}-\bra{\widetilde{\phi}_i}A(\ket{\phi_j}-\ket{\widetilde{\phi_j}})
+\begin{equation}
+\begin{split}
+(\bra{\phi_i}-\bra{\widetilde{\phi}_i})A(\ket{\phi_j}-\ket{\widetilde{\phi}_j})
+& =\bra{\phi_i}A\ket{\phi_j}-\bra{\widetilde{\phi}_i}A\ket{\phi_j}
+-(\bra{\phi_i}-\bra{\widetilde{\phi}_i})A\ket{\widetilde{\phi}_j}\\
+& =\bra{\phi_i}A\ket{\phi_j}-\bra{\widetilde{\phi}_i}A(\ket{\phi_j}-\ket{\widetilde{\phi_j}})
 -(\bra{\phi_i}-\bra{\widetilde{\phi}_i})A\ket{\widetilde{\phi}_j}
--\bra{\widetilde{\phi_i}}A\ket{\widetilde{\phi_j}}$$
+-\bra{\widetilde{\phi_i}}A\ket{\widetilde{\phi_j}}
+\end{split}
+\end{equation}
+
 one can rearrange Equation \ref{eq:res} in the manner of Blochl\cite{blochl}:
@@
 \begin{split}
-\widetilde{A}=A+\sum_i\sum_j[\ket{\widetilde{p}_i}(\bra{\phi_i}A\ket{\phi_j}
+\widetilde{A}= & A+\sum_i\sum_j[\ket{\widetilde{p}_i}(\bra{\phi_i}A\ket{\phi_j}
 -\bra{\widetilde{\phi_i}}A\ket{\widetilde{\phi_j}})\bra{\widetilde{p}_j}] \\
-+\sum_i[(1-\sum_j\ket{\widetilde{p}_j}\bra{\widetilde{\phi}_j})A(\ket{\phi_i}-\ket{\widetilde{\phi_i}})
+& +\sum_i[(1-\sum_j\ket{\widetilde{p}_j}\bra{\widetilde{\phi}_j})A(\ket{\phi_i}-\ket{\widetilde{\phi_i}})
 \bra{\widetilde{p}_i}+\ket{\widetilde{p}_i}
@@
 \begin{equation}
-\braket{\psi_{Rn_1\mathbf{k}}|\psi_{Sn_2\mathbf{k}}}=\widetilde{O}+O_1+O_2+O_3
+\begin{split}
+\braket{\psi_{Rn_1\mathbf{k}}|\psi_{Sn_2\mathbf{k}}} & =\widetilde{O}+O_1+O_2+O_3\\
+\widetilde{O} & =\braket{\widetilde{\psi}_{Rn_1\mathbf{k}}|\widetilde{\psi}_{Sn_2\mathbf{k}}}\\
+O_1 & =\sum_i\braket{\widetilde{\psi}_{Rn_1\mathbf{k}}|\widetilde{p}_i}(\bra{\phi_i}-\bra{\widetilde{\phi}_i})
+\ket{\widetilde{\psi}_{Sn_2\mathbf{k}}}\\
+O_2 & =\sum_j\bra{\widetilde{\psi}_{Rn_1\mathbf{k}}}(\ket{\phi_j}-\ket{\widetilde{\phi}_j})
+\braket{\widetilde{p}_j|\widetilde{\psi}_{Sn_2\mathbf{k}}}\\
+O_3 & =\sum_i\sum_j\braket{\widetilde{\psi}_{Rn_1\mathbf{k}}|
+\widetilde{p}_i}(\bra{\phi_i}-\bra{\widetilde{\phi}_i})
+(\ket{\phi_j}-\ket{\widetilde{\phi}_j})\braket{\widetilde{p}_j|\widetilde{\psi}_{Sn_2\mathbf{k}}}
+\end{split}
 \label{eq:ov1}
 \end{equation}
-$$\widetilde{O}=\braket{\widetilde{\psi}_{Rn_1\mathbf{k}}|\widetilde{\psi}_{Sn_2\mathbf{k}}}$$
-$$O_1=\sum_i\braket{\widetilde{\psi}_{Rn_1\mathbf{k}}|\widetilde{p}_i}(\bra{\phi_i}-\bra{\widetilde{\phi}_i})
-\ket{\widetilde{\psi}_{Sn_2\mathbf{k}}}$$
-$$O_2=\sum_j\bra{\widetilde{\psi}_{Rn_1\mathbf{k}}}(\ket{\phi_j}-\ket{\widetilde{\phi}_j})
-\braket{\widetilde{p}_j|\widetilde{\psi}_{Sn_2\mathbf{k}}}$$
-$$O_3=\sum_i\sum_j\braket{\widetilde{\psi}_{Rn_1\mathbf{k}}|
-\widetilde{p}_i}(\bra{\phi_i}-\bra{\widetilde{\phi}_i})
-(\ket{\phi_j}-\ket{\widetilde{\phi}_j})\braket{\widetilde{p}_j|\widetilde{\psi}_{Sn_2\mathbf{k}}}$$
+
 The pseudowavefunctions can be expanded as a summation of plane waves,
@@
 \omega_{\mathbf{k}} \sum_{\mathbf{G}} C^*_{n_1\mathbf{k}_1\mathbf{G}}C_{n_2\mathbf{k}_2\mathbf{G}}$$
+
 In VASP, structures with the same energy, k-points, and lattice will have the same basis set,
@@
 (\braket{\phi_{a\ind _1}|{\phi_{a\ind _2}}}
--\bra{\widetilde{\phi}_{a\ind _1}}\ket{\widetilde{\phi}_{a\ind _2}})
+-\braket{\widetilde{\phi}_{a\ind _1}|\widetilde{\phi}_{a\ind _2}})
 \braket{\widetilde{p}_{a\ind _2}|\widetilde{\psi}_{Sn_2\mathbf{k}}}$$
@@
 (\braket{\phi_{a\ind _1}|{\phi_{a\ind _2}}}
--\bra{\widetilde{\phi}_{a\ind _1}}\ket{\widetilde{\phi}_{a\ind _2}})
+-\braket{\widetilde{\phi}_{a\ind _1}|\widetilde{\phi}_{a\ind _2}})
 \braket{\widetilde{p}_{a\ind _2}|\widetilde{\psi}_{Sn_2\mathbf{k}}}

### 2018-03-06 pawpyseed/utils.py

@@ -21,6 +21,19 @@ PAWC.free_ptr.restype = None
 PAWC.free_ppot_list.restype = None
 PAWC.free_pswf.restype = None
 
+class PAWpyError(Exception):
+
+	def __init__(self, msg):
+		self.msg = msg
+
+def check_spin(spin, nspin):
+	if spin >= 0:
+		if spin >= nspin:
+			raise PAWpyError('spin must be less than nspin. spin is %d, nspin is %d' % (spin, nspin))
+		else:
+			return 1
+	return nspin
+
 def cdouble_to_numpy(arr, length):
 	"""
 	Convert a pointer to length doubles

### 2018-03-07 setup.py
setup files

@@ -1,0 +1,17 @@
+from distutils.core import setup
+
+cargs = ['-std=c11', '-lmkl_rt', '-fopenmp', '-lpthread', '-ldl', '-lm', '-O3', '-fPIC', '-Wall']
+
+setup(name='PAWpySeed',
+	version='0.0.1',
+	description='Parallelized DFT wavefunction analysis utilities',
+	author='Kyle Bystrom',
+	author_email='kylebystrom@berkeley.edu',
+	packages=['pawpyseed'],
+	ext_modules=[Extension('pawpy', ['pseudoprojector.c', 'projector.c', 'fft.c', 'quadrature.c', \
+                'reader.c', 'utils.c', 'radial.c', 'tests.c', 'sbt.c'],
+                library_dirs=['${MKLROOT}/lib/intel64'],
+                include_dirs=['${MKLROOT}/include'],
+                extra_compile_args=cargs,
+                extra_link_args=cargs)]
+	)

### 2018-03-07 setup.py
package setup

@@ -1,17 +1,27 @@
-from distutils.core import setup
+from distutils.core import setup, Extension
+import os, subprocess
+import sys
 
-cargs = ['-std=c11', '-lmkl_rt', '-fopenmp', '-lpthread', '-ldl', '-lm', '-O3', '-fPIC', '-Wall']
+os.environ["CC"] = "icc"
+os.environ["CXX"] = "icc"
 
-setup(name='PAWpySeed',
+srcfiles = ['fft', 'projector', 'pseudoprojector', 'quadrature', 'radial', 'reader', 'sbt', 'tests', 'utils']
+cfiles = [f+'.c' for f in srcfiles]
+hfiles = [f+'.h' for f in srcfiles]
+
+setup(name='pawpyseed',
 	version='0.0.1',
 	description='Parallelized DFT wavefunction analysis utilities',
 	author='Kyle Bystrom',
 	author_email='kylebystrom@berkeley.edu',
 	packages=['pawpyseed'],
-	ext_modules=[Extension('pawpy', ['pseudoprojector.c', 'projector.c', 'fft.c', 'quadrature.c', \
-                'reader.c', 'utils.c', 'radial.c', 'tests.c', 'sbt.c'],
-                library_dirs=['${MKLROOT}/lib/intel64'],
-                include_dirs=['${MKLROOT}/include'],
-                extra_compile_args=cargs,
-                extra_link_args=cargs)]
-	)
+	package_data={'pawpyseed': cfiles+hfiles+['Makefile', 'pawpy.so']},
+	scripts=['pawpy_example.py']
+)
+
+if len(sys.argv) > 1 and sys.argv[1] == 'build':
+	currdir = os.getcwd()
+	os.chdir(os.path.join(currdir,'build/lib/pawpyseed/'))
+	subprocess.call('make projector'.split())
+	os.chdir(currdir)
+

### 2018-03-07 setup.py
setup fix

@@ -1,4 +1,4 @@
-from distutils.core import setup
+from distutils.core import setup, Extension
 
 cargs = ['-std=c11', '-lmkl_rt', '-fopenmp', '-lpthread', '-ldl', '-lm', '-O3', '-fPIC', '-Wall']
 

### 2018-03-21 pawpyseed/data/projector.c
resolve #15

@@ -165,9 +165,9 @@ real_proj_site_t* projector_values(int num_sites, int* labels, double* coords,
 		}
 	}
 
-	double path[3] = {0,0,0};
-	double r = 0;
 	for (int i = 0; i < fftg[0]; i++) {
+		double path[3] = {0,0,0};
+		double r = 0;
 		for (int j = 0; j < fftg[1]; j++) {
 			for (int k = 0; k  < fftg[2]; k++) {
 				double frac[3] = {(double)i/fftg[0], (double)j/fftg[1], (double)k/fftg[2]};

### 2018-03-21 pawpyseed/data/wavefunction.py

@@ -64,8 +64,12 @@ class Pseudopotential:
 		auguccstr, gridstr = gridstr.split("grid", 1)
 		gridstr, aepotstr = gridstr.split("aepotential", 1)
 		aepotstr, corechgstr = aepotstr.split("core charge-density", 1)
-		corechgstr, kenstr = corechgstr.split("kinetic energy-density", 1)
-		kenstr, pspotstr = kenstr.split("pspotential", 1)
+		try:
+			corechgstr, kenstr = corechgstr.split("kinetic energy-density", 1)
+			kenstr, pspotstr = kenstr.split("pspotential", 1)
+		except:
+			kenstr = "0 0"
+			corechgstr, pspotstr = corechgstr.split("pspotential", 1)
 		pspotstr, pscorechgstr = pspotstr.split("core charge-density (pseudized)", 1)
 		self.grid = self.make_nums(gridstr)
 		self.aepotential = self.make_nums(aepotstr)
@@ -87,8 +91,12 @@ class Pseudopotential:
 		topstr, projstrs = projstrs[0], projstrs[1:]
 		self.T = float(topstr[-22:-4])
 		topstr, atpschgstr = topstr[:-22].split("atomic pseudo charge-density", 1)
-		topstr, corechgstr = topstr.split("core charge-density (partial)", 1)
-		settingstr, localstr = topstr.split("local part", 1)
+		try:
+			topstr, corechgstr = topstr.split("core charge-density (partial)", 1)
+			settingstr, localstr = topstr.split("local part", 1)
+		except:
+			corechgstr = "0 0"
+			settingstr, localstr = topstr.split("local part", 1)
 		localstr, self.gradxc = localstr.split("gradient corrections used for XC", 1)
 		self.gradxc = int(self.gradxc)
 		self.localpart = self.make_nums(localstr)
@@ -305,17 +313,16 @@ class Wavefunction:
 		selfnums = self.nums
 		selfcoords = self.coords
 
-		print(selfnums, selfcoords, basisnums, basiscoords)
 		print(hex(projector_list), hex(self.pwf.wf_ptr))
 		sys.stdout.flush()
 		
 		if setup_basis:
 			self.projector.setup_projections(c_void_p(basis.pwf.wf_ptr),
-				c_void_p(projector_list), len(self.cr.pps),
[…]

### 2018-03-21 pawpyseed/data/wavefunction.py
remember to free your memory

@@ -491,7 +491,7 @@ class Wavefunction:
 				yield [wf_dir, basis, wf]
 				print ("DONE WITH A YIELD")
 				sys.stdout.flush()
-				#wf.free_all()
+				wf.free_all()
 				print ("FREED MEM")
 			except:
 				if ignore_errors:

### 2018-03-21 pawpyseed/analysis/defect_composition.py
rough draft defect composition analyzer script

@@ -1,0 +1,39 @@
+import yaml
+import matplotlib.pyplot as plt 
+import numpy as np 
+
+f = open('res.yaml', 'r')
+data = yaml.load(f)
+f.close()
+
+bs = []
+vs = []
+cs = []
+
+for defect in data:
+	bs = []
+	vs = []
+	cs = []
+	dat = data[defect]
+	for b in dat:
+		bs.append(b)
+		#bs.append(2*b)
+		#bs.append(2*b+1)
+		vs.append(dat[b][0][0])
+		#vs.append(dat[b][0][1])
+		cs.append(dat[b][1][0])
+		#cs.append(dat[b][1][1])
+
+	fig, ax1 = plt.subplots()
+	ax1.set_xlabel('band')
+	ax1.set_ylabel('valence', color='b')
+	ax1.bar(bs, vs, color='b')
+	ax1.set_ylim(0,1)
+	ax2 = ax1.twinx()
+	ax2.set_ylabel('conduction', color='r')
+	ax2.bar(bs, cs, color='r')
+	ax2.set_ylim(0,1)
+	ax2.invert_yaxis()
+	plt.title(defect)
+	plt.savefig('Si_stuff/'+defect+'.png')
+

### 2018-03-21 docs/paper.tex

@@
 \hline
-$\widetilde{O}$ & $BKSW$ & per band\\
-$O_M$ & $BKSNP$ & per band\\
-$O_R$ and $O_S$ & $BKSNP$ & per band\\
-$O_N$ & $BKSNP$ & per band\\
-$\braket{\widetilde{p}_i|\widetilde{\psi}_{n\mathbf{k}}}$ & $BKSF\mathrm{log}(F)$ & per structure\\
+$\widetilde{O}$ & $BKSW \sim n^2$ & per band\\
+$O_M$ & $BKSNP \sim n^2$ & per band\\
+$O_R$ and $O_S$ & $BKSNP \sim n^2$ & per band\\
+$O_N$ & $BKSNP \sim n^2$ & per band\\
+$\braket{\widetilde{p}_i|\widetilde{\psi}_{n\mathbf{k}}}$ & $BKSF\mathrm{log}(F)
+\sim n^2\mathrm{log}(n)$ & per structure\\
 $(\bra{\phi_i}-\bra{\widetilde{\phi}_i})
-\ket{\widetilde{\psi}_{n\mathbf{k}}}$ & $BKSNPW$ & per structure\\
-spherical Bessel transform partial waves & $NPG\mathrm{log}(G)$ & per structure pair\\
-project plane waves onto partial waves & $EPKW$ & per structure pair\\
-projections for overlapping aug spheres & $NPL$ & per structure pair\\
+\ket{\widetilde{\psi}_{n\mathbf{k}}}$ & $BKSNPW \sim n^3$ & per structure\\
+spherical Bessel transform partial waves & $NPG\mathrm{log}(G) \sim n$ & per structure pair\\
+project plane waves onto partial waves & $EPKW \sim n$ & per structure pair\\
+projections for overlapping aug spheres & $NPL \sim n$ & per structure pair\\
 \hline
@@
 W & number of plane waves\\
+n & number of electrons (approximate scaling)
 \end{tabular}
 \caption{Runtime scaling functions for each component of the code and
-definitions for shorthand symbols to express runtime.
+definitions for shorthand symbols to express runtime. Approximate
+scales with the number of electrons are also shown.
 *The frequency refers to how often the routine is called. "Per band"
@@
 	\item
-	Settings
+	\textbf{Settings}: The parameters used for the generation of the psuedopotentials,
+	as described thoroughly in VASP and pymatgen documentation.
 	\item
-	adsf
+	A bunch of stuff I still don't understand and which has no discernible grid.
 	\item
@@
 	\item
-	PAW Radial Sets
+	\textbf{PAW Radial Sets}
 	\begin{enumerate}

### 2018-03-21 setup.py
updates to setup stuff

@@ -18,13 +18,15 @@ setup(name='pawpyseed',
 	author='Kyle Bystrom',
 	author_email='kylebystrom@berkeley.edu',
 	packages=['pawpyseed', 'pawpyseed.data', 'pawpyseed.analysis'],
-	package_data={'pawpyseed': cfiles+hfiles+['Makefile', 'pawpy.so']},
-	scripts=['scripts/pawpy_example.py']
+	package_data={'pawpyseed.data': cfiles+hfiles+['Makefile', 'pawpy.so']},
+#	scripts=['scripts/pawpy_example.py']
 )
 
 if len(sys.argv) > 1 and sys.argv[1] == 'build':
 	currdir = os.getcwd()
-	os.chdir(os.path.join(currdir,'build/lib/pawpyseed/'))
+	os.chdir(os.path.join(currdir,'build/lib/pawpyseed/data'))
+	shutil.copyfile('mkl_linalg.c', 'linalg.c')
+	shutil.copyfile('mkl_linalg.h', 'linalg.h')
 	subprocess.call('make pawpy_icc'.split())
 	os.chdir(currdir)
 

### 2018-03-22 pawpyseed/data/projector.c
more precise radial.c and faster projector_values

@@ -165,6 +165,49 @@ real_proj_site_t* projector_values(int num_sites, int* labels, double* coords,
 		}
 	}
 
+	#pragma omp parallel for
+	for (int p = 0; p < num_sites; p++) {
+		double res[3] = {0,0,0};
+		double testcoord[3] = {0,0,0};
+		vcross(res, lattice+3, lattice+6);
+		int grid1 = (int) (mag(res) * sites[p].rmax / vol * fftg[0]) + 1;
+		vcross(res, lattice+0, lattice+6);
+		int grid2 = (int) (mag(res) * sites[p].rmax / vol * fftg[1]) + 1;
+		vcross(res, lattice+0, lattice+3);
+		int grid3 = (int) (mag(res) * sites[p].rmax / vol * fftg[2]) + 1;
+		int center1 = (int) round(coords[3*p+0] * fftg[0]);
+		int center2 = (int) round(coords[3*p+1] * fftg[1]);
+		int center3 = (int) round(coords[3*p+2] * fftg[2]);
+		int ii=0, jj=0; kk=0;
+		for (int i = -grid1 + center1; i <= grid1 + center1; i++) {
+			for (int j = -grid2 + center2; j <= grid2 + center2; j++) {
+				for (int k = -grid3 + center3; k <= grid3 + center3; k++) {
+					testcoord[0] = (double) i / fftg[0] - coord[3*p+0];
+					testcoord[1] = (double) j / fftg[1] - coord[3*p+1];
+					testcoord[2] = (double) k / fftg[2] - coord[3*p+2];
+					frac_to_cartesian(testcoord, lattice);
+					if (mag(testcoord) < 0.99 * sites[p].rmax) {
+						ii = (i%fftg[0] + fftg[0]) % fftg[0];
+						jj = (j%fftg[1] + fftg[1]) % fftg[1];
+						kk = (k%fftg[2] + fftg[2]) % fftg[2];
+						sites[p].indices[sites[p].num_indices] = ii*fftg[1]*fftg[2] + jj*fftg[2] + kk;
+						for (int n = 0; n < sites[p].total_projs; n++) {
+							sites[p].projs[n].paths[3*sites[p].num_indices+0] = testcoord[0];
+							sites[p].projs[n].paths[3*sites[p].num_indices+1] = testcoord[1];
+							sites[p].projs[n].paths[3*sites[p].num_indices+2] = testcoord[2];
[…]

### 2018-03-22 pawpyseed/data/projector.c
resolve #12 and #30, still want to test a bit on the Ga test case

@@ -168,6 +168,7 @@ real_proj_site_t* projector_values(int num_sites, int* labels, double* coords,
 	#pragma omp parallel for
 	for (int p = 0; p < num_sites; p++) {
 		double res[3] = {0,0,0};
+		double frac[3] = {0,0,0};
 		double testcoord[3] = {0,0,0};
 		vcross(res, lattice+3, lattice+6);
 		int grid1 = (int) (mag(res) * sites[p].rmax / vol * fftg[0]) + 1;
@@ -178,18 +179,21 @@ real_proj_site_t* projector_values(int num_sites, int* labels, double* coords,
 		int center1 = (int) round(coords[3*p+0] * fftg[0]);
 		int center2 = (int) round(coords[3*p+1] * fftg[1]);
 		int center3 = (int) round(coords[3*p+2] * fftg[2]);
-		int ii=0, jj=0; kk=0;
+		int ii=0, jj=0, kk=0;
 		for (int i = -grid1 + center1; i <= grid1 + center1; i++) {
 			for (int j = -grid2 + center2; j <= grid2 + center2; j++) {
 				for (int k = -grid3 + center3; k <= grid3 + center3; k++) {
-					testcoord[0] = (double) i / fftg[0] - coord[3*p+0];
-					testcoord[1] = (double) j / fftg[1] - coord[3*p+1];
-					testcoord[2] = (double) k / fftg[2] - coord[3*p+2];
+					testcoord[0] = (double) i / fftg[0] - coords[3*p+0];
+					testcoord[1] = (double) j / fftg[1] - coords[3*p+1];
+					testcoord[2] = (double) k / fftg[2] - coords[3*p+2];
 					frac_to_cartesian(testcoord, lattice);
 					if (mag(testcoord) < 0.99 * sites[p].rmax) {
 						ii = (i%fftg[0] + fftg[0]) % fftg[0];
 						jj = (j%fftg[1] + fftg[1]) % fftg[1];
 						kk = (k%fftg[2] + fftg[2]) % fftg[2];
+						frac[0] = (double) ii / fftg[0];
+						frac[1] = (double) jj / fftg[1];
+						frac[2] = (double) kk / fftg[2];
 						sites[p].indices[sites[p].num_indices] = ii*fftg[1]*fftg[2] + jj*fftg[2] + kk;
 						for (int n = 0; n < sites[p].total_projs; n++) {
 							sites[p].projs[n].paths[3*sites[p].num_indices+0] = testcoord[0];

### 2018-03-22 pawpyseed/data/wavefunction.py
fix a couple bugs, probably need to still dive into the precision a bit more

@@ -307,6 +307,8 @@ class Wavefunction:
 		#if not basis.projection_data:
 		#	basis.projection_data = self.make_c_projectors(basis)
 		#projector_list, selfnums, selfcoords, basisnums, basiscoords = basis.projection_data
+		if setup_basis:
+			basis.projector_list, self.nums, self.coords, basis.nums, basis.coords = self.make_c_projectors(basis)
 		projector_list = basis.projector_list
 		basisnums = basis.nums
 		basiscoords = basis.coords
@@ -545,6 +547,8 @@ class Wavefunction:
 		selfcoords = np.array([], np.float64)
 		basiscoords = np.array([], np.float64)
 
+		self.num_proj_els = len(pps)
+		basis.num_proj_els = len(pps)
 		for s in self.structure:
 			selfcoords = np.append(selfcoords, s.frac_coords)
 		if basis != None:

### 2018-04-19 pawpyseed/core/radial.c
radial.c precision improvements

@@ -8,9 +8,6 @@
 #include "radial.h"
 
 #define PI 3.14159265358979323846
-#define NUM_RADIAL_SUBSTEPS 3
-#define NUM_THETA 29
-#define NUM_PHI 60
 
 double complex offsite_wave_overlap(double* dcoord, double* r1, double* f1, double** spline1, int size1,
 	double* r2, double* f2, double** spline2, int size2,
@@ -19,23 +16,29 @@ double complex offsite_wave_overlap(double* dcoord, double* r1, double* f1, doub
 	double temp[3] = {0,0,0};
 	double r1max = r1[size1-1];
 	double r2max = r2[size2-1];
-	double dphi = 2 * PI / NUM_PHI;
+	double dphi = 0;
 	double THETA, PHI, R1, R2, costheta, dcostheta, sintheta, phi, integral = 0;
 	double complex F1, F2;
+	int NUM_RADIAL_SUBSTEPS, NUM_PHI, NUM_THETA = 0;
 
 	//loop over 1st coord
 	double dr = 0;
-	double* costhetas = QUADRATURE_POINTS[NUM_THETA-3];
-	double* dcosthetas = QUADRATURE_WEIGHTS[NUM_THETA-3];
 
 	for (int rstep = 0; rstep < size1-1; rstep++) {
-		dr = (r1[rstep+1] - r1[rstep]) / NUM_RADIAL_SUBSTEPS;
+		dr = (r1[rstep+1] - r1[rstep]);
+		NUM_RADIAL_SUBSTEPS = max(1, (int) (dr/0.01));
+		dr /= NUM_RADIAL_SUBSTEPS;
+		NUM_THETA = min(100, max(3, (int) (r1[rstep] * PI / 0.02)));
+		double* costhetas = QUADRATURE_POINTS[NUM_THETA-3];
+		double* dcosthetas = QUADRATURE_WEIGHTS[NUM_THETA-3];
 		for (int substep = 0; substep < NUM_RADIAL_SUBSTEPS; substep++) {
 			R1 = r1[rstep] + (substep+0.5)*dr;
 			for (int thetastep = 0; thetastep < NUM_THETA; thetastep++) {
 				costheta = costhetas[thetastep];
 				dcostheta = dcosthetas[thetastep];
 				sintheta = pow(1 - pow(costheta, 2), 0.5);
+				NUM_PHI = max((int) ((NUM_THETA+1)*2*sintheta), 6);
[…]

### 2018-04-19 pawpyseed/core/quadrature.c
update quadrature

@@ -1,6 +1,6 @@
 #include "quadrature.h"
 
-double QUADRATURE_POINTS[27][30] = {
+double QUADRATURE_POINTS[98][101] = {
 	{-0.7745966692414834, 0.0, 0.7745966692414834},
 	{-0.8611363115940526, -0.33998104358485626, 0.33998104358485626, 0.8611363115940526},
 	{-0.906179845938664, -0.5384693101056831, 0.0, 0.5384693101056831, 0.906179845938664},
@@ -28,9 +28,80 @@ double QUADRATURE_POINTS[27][30] = {
 	{-0.9961792628889885, -0.9799234759615012, -0.9509005578147051, -0.9094823206774911, -0.8562079080182945, -0.7917716390705083, -0.7170134737394237, -0.6329079719464952, -0.540551564579457, -0.44114825175002687, -0.3359939036385089, -0.22645936543953685, -0.11397258560952997, 0.0, 0.11397258560952997, 0.22645936543953685, 0.3359939036385089, 0.44114825175002687, 0.540551564579457, 0.6329079719464952, 0.7170134737394237, 0.7917716390705083, 0.8562079080182945, 0.9094823206774911, 0.9509005578147051, 0.9799234759615012, 0.9961792628889885},
 	{-0.9964424975739544, -0.9813031653708728, -0.9542592806289382, -0.9156330263921321, -0.865892522574395, -0.8056413709171791, -0.7356108780136318, -0.656651094038865, -0.5697204718114017, -0.4758742249551183, -0.3762515160890787, -0.2720616276351781, -0.1645692821333808, -0.055079289884034266, 0.055079289884034266, 0.1645692821333808, 0.2720616276351781, 0.3762515160890787, 0.4758742249551183, 0.5697204718114017, 0.656651094038865, 0.7356108780136318, 0.8056413709171791, 0.865892522574395, 0.9156330263921321, 0.9542592806289382, 0.9813031653708728, 0.9964424975739544},
[…]

### 2018-04-19 pawpyseed/core/quadrature.py

@@ -1,30 +1,32 @@
 import numpy as np
 
+MAXSIZE = 100
+
 f = open("quadrature.c", "w")
 
 f.write('#include "quadrature.h"\n\n')
 
 x = []
 
-for i in range(3, 30):
+for i in range(3, MAXSIZE+1):
 	x.append( np.polynomial.legendre.leggauss(i) )
 
-f.write('double QUADRATURE_POINTS[27][30] = {\n')
+f.write('double QUADRATURE_POINTS[%d][%d] = {\n' % (MAXSIZE-2, MAXSIZE+1))
 
-for i in range(27):
+for i in range(MAXSIZE-2):
 	print(i)
 	currstr = str(x[i][0].tolist()).replace("[", "{").replace("]", "}")
 	f.write("\t" + currstr)
-	if i != 29: f.write(',\n')
+	if i != MAXSIZE: f.write(',\n')
 
 f.write('}\n\n')
 
-f.write('double QUADRATURE_WEIGHTS[27][30] = {\n')
+f.write('double QUADRATURE_WEIGHTS[%d][%d] = {\n' % (MAXSIZE-2, MAXSIZE+1))
 
-for i in range(27):
+for i in range(MAXSIZE-2):
 	currstr = str(x[i][1].tolist()).replace("[", "{").replace("]", "}")
 	f.write("\t" + currstr)
-	if i != 29: f.write(',\n')
+	if i != MAXSIZE: f.write(',\n')
 
 f.write('}\n')
 

### 2018-04-19 docs/paper.tex
trying a new overlapping spheres integration technique

@@
 from different periodic structures with the same lattice, which is made nontrivial
-by the depency of PAW augmentation regions on the basis of the structure.
+by the dependency of PAW augmentation regions on the basis of the structure.
 The code is potentially useful for the analysis of point defect levels in
@@
 
-\subsection{Projector Augmented Wave (PAW) Method}
+%\subsection{Projector Augmented Wave (PAW) Method}
 
 \subsection{Projections}
+
+The equation of a PAW wavefunction is\cite{blochl}
 \begin{equation}
 \ket{\psi_{n\mathbf{k}}}=\ket{\widetilde{\psi}_{n\mathbf{k}}}+
-\sum_{a,n,l,m}(\ket{\phi_{a\ind}}-\ket{\widetilde{\phi}_{a\ind}})
+\sum_{a,l,m,\epsilon}(\ket{\phi_{a\ind}}-\ket{\widetilde{\phi}_{a\ind}})
 \braket{\widetilde{p}_{a\ind}|\widetilde{\psi}_{n\mathbf{k}}}
@@
 \end{equation}
+where the sum is over the sites $a$ in the structure and a set of
+angular and radial quantum nubers $l$, $m$, and $\epsilon$ at each site.
+The conventional overlap operator used for these wavefunctions is
+\begin{equation}
+\widetilde{A}=A+\sum_i\sum_j\ket{\widetilde{p}_i}(\bra{\phi_i}A\ket{\phi_j}
+-\bra{\widetilde{\phi_i}}A\ket{\widetilde{\phi_j}})\bra{\widetilde{p}_j}
+\label{eq:loc}
+\end{equation}
+where $i$ and $j$ are abbreviations for a particular index set
+$a,l,m,\epsilon$. This overlap operator requires that the augmentation
+regions of the two wavefunctions are same. Since these augmentation regions
+are defined by the sites in the structure, the structures must be the same,
+so a new formalism is necessary to calculate overlap operators for wavefunctions
+in different structures.
 
@@
 corrections to perform on the defect system.\cite{lany}
+For two structures (denoted R and S) with the same
+lattice but different bases, the overlap operator of two Kohn-Sham single particle states
+is described by the following terms:
 \begin{equation}
@@
 (\braket{\phi_{a\ind _1}|{\phi_{a\ind _2}}}
--\bra{\widetilde{\phi}_{a\ind _1}}\ket{\widetilde{\phi}_{a\ind _2}})
+-\braket{\widetilde{\phi}_{a\ind _1}|\widetilde{\phi}_{a\ind _2}})
 \braket{\widetilde{p}_{a\ind _2}|\widetilde{\psi}_{Sn_2\mathbf{k}}}\\
@@
 \end{equation}
-Equation \ref{eq:finp} is derived in Appendix A.
+Here, $M_{RS}$ is the set of sites that are identical in structures R and S,
+$N_R$ and $N_S$ are all other sites in these structures,
+and $N_{RS}$ is teh set of all pairs of sites, one in structure R and one in structure
+S, with overlapping augmentation spheres. Equation \ref{eq:finp} is derived in Appendix A.
 
@@
 \centering
+\caption{Runtime scaling functions for each component of the code and
+definitions for shorthand symbols to express runtime. Approximate
+scales with the number of electrons are also shown.
+*The frequency refers to how often the routine is called. "Per band"
+indicates that the routine runs once every time a band from one structure
+is projected onto all the bands of a basis structure. "Per structure"
+indicates that the routine is a "setup" routine that must be called once
+for each structure and corresponding band structure to do perform projections. "Per lattice"
+operations are required once per unique lattice used.
+"Per structure pair" is the same as "per structure" except that the routine
+is only run once for a pair of structures with the same lattice and plane-wave
+basis set, the bands of one such structure to be used as a basis set for the other.
+**Number of sites flexibly refers to the number of sites relevant to the calculation,
+which worst-case scales with the total number of sites in the structure. For example,
+calculating $O_M$ and $O_N$ only require the sites in sets $M$ and $N_RS$, respectively.}
+\label{tab:runtime}
+
 \begin{tabular}{|c|c|c|}
@@
 spherical Bessel transform partial waves & $NPG\mathrm{log}(G) \sim n$ & per structure pair\\
-project plane waves onto partial waves & $EPKW \sim n$ & per structure pair\\
+project plane waves onto partial waves & $EPKW \sim n$ & per lattice\\
 projections for overlapping aug spheres & $NPL \sim n$ & per structure pair\\
@@
 \end{tabular}
-\caption{Runtime scaling functions for each component of the code and
-definitions for shorthand symbols to express runtime. Approximate
-scales with the number of electrons are also shown.
-*The frequency refers to how often the routine is called. "Per band"
-indicates that the routine runs once every time a band from one structure
-is projected onto all the bands of a basis structure. "Per structure"
-indicates that the routine is a "setup" routine that must be called once
-for each structure and corresponding band structure to do perform projections.
-"Per structure pair" is the same as "per structure" except that the routine
-is only run once for a pair of structures with the same lattice and plane-wave
-basis set, the bands of one such structure to be used as a basis set for the other.
-**Number of sites flexibly refers to the number of sites relevant to the calculation,
-which worst-case scales with the total number of sites in the structure. For example,
-calculating $O_M$ and $O_N$ only require the sites in sets $M$ and $N_RS$, respectively.}
-\label{tab:runtime}
 \end{table}
@@
 so the pseudowavefunction cannot be projected onto the partial waves
-via a uniform Cartesian grid as is doen with the projector functions.
+via coarse Cartesian grid as is doen with the projector functions.
 However, A plane wave can be expanded as a sum of spherical
@@
 grid can be used to calculate the values of the relevant integrals via interpolation.
+
+\section{Projector function evaluation}
+
+The projector function overlaps with the plane-wave states are calculated using the same
+algorithm as VASP.\cite{vasp,vasp2,vasp3,vasp4}
+
+\section{Projections for Overlapping Augmentation Spheres}
+
+For two different structures, it is possible for atoms to have augmentation spheres
+that overlap but are not directly on top of each other, or to have atoms of different elements
+with the same position. In these cases, the overlap integrals of the partial waves
+must be evaluated numerically on a per structure pair basis. The current method is a relatively
+crude discrete integral in 3D space, which likely harms the precision of the overlap integral evaluation.
+More precise and efficient methods are being considered.
+
+\section{Results and Example Usage}
+
+To test the program for its primary purpose of defect level analysis, the projection
+of a defect level wavefunction onto the valence band of the bulk is defined:
+\begin{equation}
+v_d=\sum_{\mathbf{k}}\sum_{i\in \mathbb{V}}|\braket{\psi_{Bn_i\mathbf{k}}|\psi_{Dn_d\mathbf{k}}}|^2
+\label{eq:vproj}
+\end{equation}
+where $i$ are the band indices of valence bands $\mathbb{V}$ in the bulk structure, the $B$
+subscript denotes the bulk band structure, and the $D$ subscript denotes the point defect
+band structure. This value, as well as the similarly defined $c_d$ for the conduction band,
+were calculate for several charge states of the Silicon single vacancy, Phosphorus substitutional,
+and Boron substitutional. The results are plotted in Figure \ref{fig:plots}.
+As expected, the phosphorous and boron substitutional defects show litting mixing
+of valence and conduction character in the defect levels because they are very shallow
+defects, whereas the deeper vacancy character is shown by the mixing of conduction
+and valence character in three nearly degenerate bands in the band gap.
+
+\section{Conclusions}
+
+PAWpySeed provides useful utilities for reading and analyzing PAW wavefunctions
+from VASP, particularly for point defect levels. However, the current capabilities
+of PAWpySeed are primarily qualitative because of mediocre numerical precision
+and a lack of quantitative applications of the code. One potential quantitative
+application to be developed in the future is the perturbation theory correction
+proposedby Lany and Zunger for correcting defect level energies.\cite{lany}
+The main barriers to such a correction are currently the lack of adequate
+description of the deep level character of the defects and the difference
+between the single particle states of DFT and higher level-of-theory
+single-particle states. Work to resolve such issues is currently in development.
+Namely, code is being written to construct atomic vacuum states onto which
+PAW wavefunctions can be projected. In addition, the SCDM-k decomposition method
+will written into PAWpySeed to construct localized orbitals for energy
+corrections.\cite{scdm,scdmk}
 

### 2018-04-19 pawpyseed/core/radial2.c

@@ -1,0 +1,95 @@
+#include <stdio.h>
+#include <stdlib.h>
+#include <complex.h>
+#include <math.h>
+#include <omp.h>
+#include "quadrature.h"
+#include "utils.h"
+#include "radial.h"
+
+#define PI 3.14159265358979323846
+#define RHO_PREC 0.008
+
+double complex offsite_wave_overlap(double* dcoord, double* r1, double* f1, double** spline1, int size1,
+	double* r2, double* f2, double** spline2, int size2,
+	double* lattice, int l1, int m1, int l2, int m2) {
+
+	double r1max = r1[size1-1];
+	double r2max = r2[size2-1];
+	double min_R = 0, max_R = 0;
+	double sepdist = mag(dcoord);
+	double basis[3] = {0,0,0};
+	if (sepdist < 10e-5) {
+		basis[2] = 1;
+	} else {
+		basis[0] = dcoord[0] / sepdist;
+		basis[1] = dcoord[1] / sepdist;
+		basis[2] = dcoord[2] / sepdist;
+		double temp = pow(bais[1]*basis[1]+basis[0]+basis[0], -0.5);
+		basis[3] = -basis[1] * temp;
+		basis[4] = basis[0] * temp;
+		basis[5] = 0;
+		vcross(basis+6, basis+0, basis+3);
+	}
+	if (sepdist + r2max < r1max) {
+		max_R = sepdist + r2max;
+	} else {
+		max_R = r1max;
+	}
+	if (sepdist - r2max < -r1max) {
+		min_R = -r1max;
+	} else {
+		min_R = sepdist - r2max;
+	}
+
+
+	double R = min_R - 0.01;
+	double dR = 10e-4;
+	double rho = 9, drho = 0, dtheta = 0, rhomax = 0;
+	int NUM_THETA = 0;
+	if (r1max > r2max) {
+		rhomax = r1max;
+	} else {
+		rhomax = r2max;
+	}
+	double coord1[3] = {0,0,0};
+	double coord2[3] = {0,0,0};
+	double complex integral = 0;
+	while (R < max_R + 0.01) {
+		if (fabs(R) < 10e-8 || fabs(R-sepdist) < 10e-8)
+			dR = 10e-4;
+		else {
+			dR = log(0.28*fabs(R));
+			if dR > 0.01
+				dR = log(0.28*fabs(R-sepdist)) ;
+			if dR > 0.01
+				dR = 0.01;
[…]

### 2018-04-19 pawpyseed/core/utils.c

@@ -338,6 +338,26 @@ double complex wave_value(funcset_t funcs, int size, double* x, int m,
 	return radial_val * sph_val;
 }
 
+double complex wave_value2(double* x, double* wave, double* spline, int size,
+	int l, int m, double* pos) {
+
+	double temp[3] = {0,0,0};
+	double r = 0;
+	min_cart_path(pos, ion_pos, lattice, temp, &r);
+
+	double ae_radial_val = wave_interpolate(r, size, x, wave, spline);
+	double radial_val = (ae_radial_val - ps_radial_val) / r;
+
+	if (r==0) return Ylm(l, m, 0, 0) * radial_val;
+	double theta = 0, phi = 0;
+	theta = acos(temp[2]/r);
+	if (r - fabs(temp[2]) == 0) phi = 0;
+	else phi = acos(temp[0] / pow(temp[0]*temp[0] + temp[1]*temp[1], 0.5));
+	if (temp[1] < 0) phi = 2*PI - phi;
+	double complex sph_val = Ylm(l, m, theta, phi);
+	return radial_val * sph_val;
+}
+
 double complex proj_value(funcset_t funcs, double* x, int m, double rmax,
 	double* ion_pos, double* pos, double* lattice) {
 

### 2018-04-19 pawpyseed/core/utils.h

@@ -269,6 +269,9 @@ grid x center at 3D vector ion_pos, at position pos, given the real space lattic
 double complex wave_value(funcset_t funcs, int size, double* x, int m,
         double* ion_pos, double* pos, double* lattice);
 
+double complex wave_value2(double* x, double* wave, double* spline, int size,
+	int l, int m, double* pos);
+
 /**
 Set up spline coefficients for spline interpolation.
 Essentially a translation into C of the VASP SPLCOF function.

### 2018-04-26 docs/paper.tex
update paper for end of Spring 2018 semester

@@
 \documentclass[12pt]{article}
+\usepackage{authblk}
 \usepackage{enumitem}
@@
 \usepackage[style=chem-acs,backend=bibtex,articletitle=false]{biblatex}
-\graphicspath{ {images/} }
+\graphicspath{ {../../Si_stuff/} }
 \bibliography{mybib}
@@
 DFT wavefunctions in the PAW formalism}
-\author{Kyle Bystrom\\
-        kylebystrom@berkeley.edu\\
-		UC Berkeley Department of Materials Science and Engineering}
+\author[1]{Kyle Bystrom (kylebystrom@berkeley.edu)}
+\affil[1]{UC Berkeley Department of Materials Science and Engineering}
 \date{\today}
 \maketitle
-\abstract{A parallelized Python and C package has been developed
+\abstract{\emph{Note: My current plan is to build this work into a senior thesis,
+but currently it is quite messy and incomplete because I still have a lot of work
+to do before I will feel comfortable presenting this as a complete work. I would appreciate
+any feedback on what I have done so far.}
+
+A parallelized Python and C package has been developed
 to perform analysis of density functional theory (DFT) wavefunctions in the
@@
 
+\section{Overview}
+
+In the pure physical picture of a quantum mechanical system, the eigenfunctions of the time
+independent Hamiltonian form a complete basis for any function in real space. By expressing
+a wavefunction from a system in the basis of the eigenstates of another system, one might
+be able to learn about the nature of the wavefunction in question. For example, projecting
+the wavefunction of a defect level in a periodic crystal onto the eigenfunctions of the
+bulk crystal might yield information about how the defect level is constructed. For example,
+the defect state might project primarily onto the conduction band, characterizing it
+as a weakly perturbed host state. Such an understanding of defect levels could help select
+corrections to perform on the defect system.\cite{lany}
+
+The program developed here is designed to evaluate the overlap operators necessary for the
+above projections in the projector augmented wave formalism (PAW) developed by Blochl.\cite{blochl}
+pawpyseed interfaces with the Vienna \emph{ab initio} Simulaton
+Package (VASP)\cite{vasp,vasp1,vasp2,vasp3,vasp4}, but will interface with other plane wave
+codes in the future.
+
+The main purpose of this code is to analyze defect wavefunctions, as explained above;
+however, the formalism adn interface developed is relatively general in purpose, and
+may suit other uses. The code can perform convenient operations not included in VASP,
+such as writing all electron wavefunctions with phases to volumetric data files, which may
+be useful for visualization. In addition, one future application plan is to use a given
+set of norm-conserving pseudopotentials to convert PAW wavefunctions to NC wavefunctions,
+which could be useful for researchers working with GW codes, which usually require
+NC wavefunctions. Lastly, operators besides overlap operators can hypothetically be evaluated
+in this formalism, which might be useful for optical applications, since materials can
+change structure when absorbing a photon.
+
 \section{Theory}
 
-%\subsection{Projector Augmented Wave (PAW) Method}
+The projector augmented wave (PAW) method defines a transformation between the all electron
+(AE) single particle states of the Kohn Sham wavefunction and a pseudo (PS) wavefunction
+that is smooth throughout the lattice and therefore can be expressed in a plane wave basis set.\cite{blochl}
+This means that the AE wavefunction is a sum of plane waves and site-localized atomic states,
+which makes calculating operators difficult if the ion positions change.
 
@@
 \subsubsection{Projection onto Basis from Different Structure}
-In the pure physical picture of a quantum mechanical system, the eigenfunctions of the time
-independent Hamiltonian form a complete basis for any function in real space. By expressing
-a wavefunction from a system in the basis of the eigenstates of another system, one might
-be able to learn about the nature of the wavefunction in question. For example, projecting
-the wavefunction of a defect level in a periodic crystal onto the eigenfunctions of the
-bulk crystal might yield information about how the defect level is constructed. For example,
-the defect state might project primarily onto the conduction band, characterizing it
-as a weakly perturbed host state. Such an understanding of defect levels could help select
-corrections to perform on the defect system.\cite{lany}
 For two structures (denoted R and S) with the same
@@
 
+\subsection{Projector function evaluation}
+
+The projector function overlaps with the plane-wave states are calculated using the same
+algorithm as VASP.\cite{vasp}
+
 \subsection{Projection of Pseudowavefunctions onto Partial Waves}
@@
 
-\section{Projector function evaluation}
+The current implementation uses the "high-k" algorithm developed by Talman. At low
+values of k, this algorithm becomes imprecise, though the precision
+of the current implementation has been tested and found to be about
+$10^{-3}$ for a bulk Ga test system. Future versions of the code
+will select the most precise of the "low-k" and "high-k" algorithms for each point,
+and the density of the momentum space grid will be increased.
 
-The projector function overlaps with the plane-wave states are calculated using the same
-algorithm as VASP.\cite{vasp,vasp2,vasp3,vasp4}
+The main problem with this algorithm is that it is the slowest component of the code
+and consumes the majority of the computational time even when only a few sites out
+of a structure with hundreds of sites require the calculation. A potential fix is,
+rather than integrating in reciprocal space, which becomes prohibitively slow for large
+lattices, to remove the high-frequency components of the partial waves via Fourier transform.
+This is counterintuitive because the purpose of the partial waves is to preserve the high-frequency
+components of the atomic wavefunctions, but when projecting onto the smooth pseudowavefunction,
+the high-frequency components have no impact because they are not present in the pseudowavefunction.
+Removing the high frequency components, therefore, allows the projection onto the partial waves
+to be done in real space without aliasing.
 
-\section{Projections for Overlapping Augmentation Spheres}
+\subsection{Projections for Overlapping Augmentation Spheres}
 
@@
 must be evaluated numerically on a per structure pair basis. The current method is a relatively
-crude discrete integral in 3D space, which likely harms the precision of the overlap integral evaluation.
-More precise and efficient methods are being considered.
+crude discrete integral in 3D space, which is the limiting factor in the precision of the code.
+The current precision of this two-center overlap integral is about $10^{-2}$, which is adequate
+for qualitative evaluations of band composition but not for quantitative charge corrections.
+
+An implementation is in development in which a kernel function developed by Hierse and
+Oppeneer is used to reduce the 3-dimensional discrete integrals
+to the integral of an analytical term over the two radial distribution functions.\cite{hierse_kernel} 
+This method has the potential to vastly improve both the performance and precision of
+this step of the code, but the relevant kernel function for overlap integrals
+scales inversely with the internuclear separation, so detailed tests are required
+to design the implementation in a numerically precise fashion. Most likely, it will be
+best to divide the integrals into three cases: (1) internuclear separation is very small
+and can be assumed to vanish, (2) internuclear separation is small, but not small enough
+to be ignored numerically, but the kernel function at a given $r_1$ is very narrow
+in $r_2$, (3) the internuclear separation is large and the kernel function smooth everywhere
+relative to the partial wave grid density.
+
+The Gaunt coefficients are required for the evaluation of the kernel function, and these
+are calculated and stored efficiently with sympy and the selection rules for \cite{gaunt_selection}.
 
@@
 band structure. This value, as well as the similarly defined $c_d$ for the conduction band,
-were calculate for several charge states of the Silicon single vacancy, Phosphorus substitutional,
-and Boron substitutional. The results are plotted in Figure \ref{fig:plots}.
-As expected, the phosphorous and boron substitutional defects show litting mixing
-of valence and conduction character in the defect levels because they are very shallow
-defects, whereas the deeper vacancy character is shown by the mixing of conduction
-and valence character in three nearly degenerate bands in the band gap.
+were calculated for several charge states of the silicon single vacancy, phosphorus substitutional,
+and boron substitutional. A 128-atom supercell was used (127 for the vacancy), with
+the PBE GGA functional in VASP.\cite{gga,ggaerr} A Monkhorst-Pack 2x2x2 k-point mesh was used.
 
-\section{Conclusions}
+\begin{figure}
+\includegraphics[width=0.32\textwidth]{Bcharge_0.png}
+\includegraphics[width=0.32\textwidth]{Bcharge_-1.png}
+\includegraphics[width=0.32\textwidth]{Pcharge_0.png}
+\includegraphics[width=0.32\textwidth]{Pcharge_1.png}
+\includegraphics[width=0.32\textwidth]{charge_-2.png}
+\includegraphics[width=0.32\textwidth]{charge_-1.png}
+\includegraphics[width=0.32\textwidth]{charge_0.png}
+\includegraphics[width=0.32\textwidth]{charge_1.png}
+\includegraphics[width=0.32\textwidth]{charge_2.png}
+\caption{Valence and conduction band character of several charge states
+of three Si point defects, determined by evaluating the overlap
+operator between all electron wavefunctions. The charge states prefixed by B are
+boron substitutionals, those prefixed by P are phosphorous substitutionals,
+and those without a prefix are Si single vacancies.}
+\label{fig:ae_proj}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=0.32\textwidth]{pseudo/Bcharge_0.png}
+\includegraphics[width=0.32\textwidth]{pseudo/Bcharge_-1.png}
+\includegraphics[width=0.32\textwidth]{pseudo/Pcharge_0.png}
+\includegraphics[width=0.32\textwidth]{pseudo/Pcharge_1.png}
+\includegraphics[width=0.32\textwidth]{pseudo/charge_-2.png}
+\includegraphics[width=0.32\textwidth]{pseudo/charge_-1.png}
+\includegraphics[width=0.32\textwidth]{pseudo/charge_0.png}
+\includegraphics[width=0.32\textwidth]{pseudo/charge_1.png}
+\includegraphics[width=0.32\textwidth]{pseudo/charge_2.png}
+\caption{Valence and conduction band character of several charge states
+of three Si point defects, determined by only evaluating
+the overlap operator between pseudowavefunctions and then forcibly
+normalizing the result to 1. The charge states prefixed by B are
+boron substitutionals, those prefixed by P ar phosphorous substitutionals,
+and those without a prefix are Si single vacancies.}
+\label{fig:ps_proj}
+\end{figure}
+
+Figure \ref{fig:ae_proj} shows the valence and conduction band characters of
+each defect and charge state. The shallow character of the phosphorous and boron
+substitutionals result in each band being strongly associated with either the bulk
+or conduction bands. In the Si vacancy, three bands have some mixing of conduction
+and valence character, which is sensible because the vacancy is a deeper defect.
+
+The same defects are analyzed in Figure \ref{fig:ps_proj}, except that the overlap
+operators were evaluated using pseudowavefunctions, which is much faster but
+less physically meaningful because the pseudowavefunctions are unnormalized
+and not orthogonal (the
+diagram forcibly normalizes valence and conduction character) and
+different in shape than the true AE single-particle states. However, as shown
+for these simple Si systems, the same qualitative valence-conduction character is
+observed, indicating that such qualitative methods might be useful for more quickly
+analyzing bands.
+
+The sulfur substitutional in silicon was analyzed in a 216-atom supercell,
+but further work is required to interpret the results meaningfully, so they
+will be released in future work.
+
+\section{Conclusions and Future Work}
+
+Most of the work performed thus far has centered on the writing and testing of
+PAWpySeed for basic functionality on various systems. As elaborated below,
+a major goal for future work is to add new functionality to PAWpySeed and increase
+its precision. However, the most prescient matter is taking the results
+accumulated on test defect systems and comparing the output of PAWpySeed to the
+DFT formation energies and eigenvalues of the systems. The results above
+verify the functionality of the code but not its usefulness, which will only
+be discernible in comparision with the quantitative output of the DFT calculations.
+This, along with increasing the efficiency and precision of the code, will be
+the main goal of work over the next several months.
 
@@
 application to be developed in the future is the perturbation theory correction
-proposedby Lany and Zunger for correcting defect level energies.\cite{lany}
+proposed by Lany and Zunger for correcting defect level energies.\cite{lany}
 The main barriers to such a correction are currently the lack of adequate
@@
 PAW wavefunctions can be projected. In addition, the SCDM-k decomposition method
-will written into PAWpySeed to construct localized orbitals for energy
+will be written into PAWpySeed to construct localized orbitals for energy
 corrections.\cite{scdm,scdmk}
+
+\section{Acknowledgments}
+
+I would like to thank Danny Broberg and Mark Asta for excellent advising
+and encouragement throughout my work with the Asta Research Group at UC Berkeley,
+as well as all the members of the Asta Research Group and Hacking Materials
+Research Group at Lawrence Berkeley National Laboratory for various
+valuable research and learning opportunities. My summer 2017 undergraduate
+research, mainly related to development of an open-source data science code
+called matminer, was supported
+by a summer research stipend from the UC Berkeley College of Chemistry.
 
@@
 and construction of the partial waves and projector functions, see Blochl's original paper
-and Kresse and Joubert's paper relating ultrasoft pseudopotentials and PAW.\cite{blochl,kresse_joubert}
+and Kresse and Joubert's paper relating ultrasoft pseudopotentials and PAW.\cite{blochl,vasp4}
 The next step is to define a pseudo operator $\widetilde{A}$ for each operator $A$
@@
 -\bra{\widetilde{\phi_i}}A\ket{\widetilde{\phi_j}})\bra{\widetilde{p}_j}
-\label{eq:loc}
+\label{eq:loc1}
 \end{equation}
 
-However, while the overlap operator is local, the simplification in Equation \ref{eq:loc} assumes that
+However, while the overlap operator is local, the simplification in Equation \ref{eq:loc1} assumes that
 the summations over $i$ and $j$ go over the same species at the same locations in the same lattice;
@@
 \end{split}
-\label{eq:ov1}
+\label{eq:ov1a}
 \end{equation}
@@
 
-It is important to simplify the calculation of the other terms in equation \ref{eq:ov1} as much
+It is important to simplify the calculation of the other terms in equation \ref{eq:ov1a} as much
 as possible because their calculation can be quite computationally intensive, and the number of

### 2018-04-26 pawpyseed/core/sbt.c
inverse sbt

@@ -156,3 +156,78 @@ double* wave_spherical_bessel_transform(sbt_descriptor_t* d, double* f, int l) {
 	free(fs);
 	return vals;
 }
+
+double* inverse_wave_spherical_bessel_transform(sbt_descriptor_t* d, double* f, int l) {
+
+	//double kmin = d->kmin;
+	//double kappamin = d->kappamin;
+	//double rmin = d->rmin;
+	//double rhomin = d->rhomin;
+	//double drho = d->drho;
+	double kmin = d->rmin;
+	double kappamin = d->rhomin;
+	double rmin = d->kmin;
+	double rhomin = d->kappamin;
+	double drho = d->drho;
+	double dt = d->dt;
+	int N = d->N;
+	double complex** M = d->mult_table;
+	//double* ks = d->ks;
+	//double* r = d->rs;
+	double* ks = d->rs;
+	double* r = d->ks;
+	double* fs = (double*) malloc(N*sizeof(double));
+	CHECK_ALLOCATION(fs);
+	double C = f[0] / pow(r[N/2], l+1);
+	for (int i = 0; i < N/2; i++) {
+		fs[i] = C * pow(r[i], l+1);
+	}
+	for (int i = N/2; i < N; i++) {
+		fs[i] = f[i-N/2];
+	}
+
+	MKL_Complex16* x = mkl_malloc(N * sizeof(MKL_Complex16), 64);
+
+	DFTI_DESCRIPTOR_HANDLE handle = 0;
+	MKL_LONG dim = 1;
+	MKL_LONG length = N;
+	MKL_LONG status = 0;
+
+	double* vals = malloc(N / 2 * sizeof(double));
+
+	status = DftiCreateDescriptor(&handle, DFTI_DOUBLE, DFTI_COMPLEX, dim, length);
+	status = DftiCommitDescriptor(handle);
+
+	double phase = 0;
+	for (int m = 0; m < N; m++) {
+		//x[m].real = pow(r[m], 0.5) * fs[m]; // f is multiplied by r
+		x[m].real = pow(r[m], 1.5) * fs[m];
+		x[m].imag = 0;
+	}
+	double rp=0.0, ip=0.0;
+	status = DftiComputeBackward(handle, x);
+	printf("status %ld\n", status);
+	for (int n = 0; n < N; n++) {
[…]

### 2018-04-27 pawpyseed/core/sbt.c
inverse sbt works

@@ -95,7 +95,6 @@ double* wave_spherical_bessel_transform(sbt_descriptor_t* d, double* f, int l) {
 
 	double kmin = d->kmin;
 	double kappamin = d->kappamin;
-	double rmin = d->rmin;
 	double rhomin = d->rhomin;
 	double drho = d->drho;
 	double dt = d->dt;
@@ -166,7 +165,6 @@ double* inverse_wave_spherical_bessel_transform(sbt_descriptor_t* d, double* f, 
 	//double drho = d->drho;
 	double kmin = d->rmin;
 	double kappamin = d->rhomin;
-	double rmin = d->kmin;
 	double rhomin = d->kappamin;
 	double drho = d->drho;
 	double dt = d->dt;
@@ -178,12 +176,11 @@ double* inverse_wave_spherical_bessel_transform(sbt_descriptor_t* d, double* f, 
 	double* r = d->ks;
 	double* fs = (double*) malloc(N*sizeof(double));
 	CHECK_ALLOCATION(fs);
-	double C = f[0] / pow(r[N/2], l+1);
 	for (int i = 0; i < N/2; i++) {
-		fs[i] = C * pow(r[i], l+1);
+		fs[i] = f[i];
 	}
 	for (int i = N/2; i < N; i++) {
-		fs[i] = f[i-N/2];
+		fs[i] = 0;
 	}
 
 	MKL_Complex16* x = mkl_malloc(N * sizeof(MKL_Complex16), 64);
@@ -222,9 +219,9 @@ double* inverse_wave_spherical_bessel_transform(sbt_descriptor_t* d, double* f, 
 	double kp = 0;
 	for (int p = 0; p < N / 2; p++) {
 		kp = kmin * exp(p * drho);
-		vals[p] = x[p].real;
+		vals[p] = x[p + N / 2].real / PI * 2;
 		//vals[p] *= 2 / pow(ks[p], 1.5);
-		vals[p] *= 2 / pow(ks[p], 1.5);
+		vals[p] *= 2 / pow(ks[p + N / 2], 1.5);
 	}
 
 	mkl_free(x);

### 2018-08-21 pawpyseed/analysis/defect_composition.py
start operators branch to improve code organization

@@ -109,7 +109,7 @@ class BulkCharacter(PawpyData):
 	def makeit(generator):
 		#Example: 
 		#>>> def_lst = ['charge_1', 'charge_0', 'charge_-1']
-		#>>> generator = Wavefunction.setup_multiple_protections('bulk', def_lst)
+		#>>> generator = Projector.setup_multiple_protections('bulk', def_lst)
 		#>>> objs = BulkComposition.makeit()
 
 		bcs = {}
@@ -145,9 +145,9 @@ class BasisExpansion(PawpyData):
 	def makeit(generator):
 		#Example: 
 		#>>> def_lst = ['charge_1', 'charge_0', 'charge_-1']
-		#>>> generator = Wavefunction.setup_multiple_protections('bulk', def_lst)
+		#>>> generator = Projector.setup_multiple_protections('bulk', def_lst)
 		#OR
-		#>>> generator = Wavefunction.setup_multiple_projections(*pycdt_dirs('.'))
+		#>>> generator = Projector.setup_multiple_projections(*pycdt_dirs('.'))
 		#
 		#>>> objs = BasisExpansion.makeit()
 

### 2018-08-21 pawpyseed/core/projector.c

@@ -629,7 +629,7 @@ void overlap_setup_real(pswf_t* wf_R, pswf_t* wf_S, ppot_t* pps,
 		}
 		free_real_proj_site_list(sites_N_R, num_N_R);
 	}
-	printf("ONE THIRD DONE\n");
+	printf("PART 1 DONE\n");
 	if (num_N_S > 0) {
 		real_proj_site_t* sites_N_S = smooth_pw_values(num_N_S, N_S, labels_S, coords_S,
 			wf_R->lattice, wf_R->reclattice, pps, wf_R->fftg);
@@ -643,7 +643,7 @@ void overlap_setup_real(pswf_t* wf_R, pswf_t* wf_S, ppot_t* pps,
 		}
 		free_real_proj_site_list(sites_N_S, num_N_S);
 	}
-	printf("TWO THIRDS DONE\n");
+	printf("PART 2 DONE\n");
 	
 	double* dcoords =  NULL;
 	if (num_N_RS > 0) {
@@ -708,7 +708,7 @@ void overlap_setup_real(pswf_t* wf_R, pswf_t* wf_S, ppot_t* pps,
 	wf_S->dcoords = dcoords;
 	wf_S->num_aug_overlap_sites = num_N_RS;
 	wf_R->num_aug_overlap_sites = num_N_RS;
-	printf("finished overlap setup\n");
+	printf("PART 3 DONE\nFINISHED OVERLAP SETUP\n");
 }
 
 double* compensation_terms(int BAND_NUM, pswf_t* wf_S, pswf_t* wf_R, ppot_t* pps,

### 2018-08-21 pawpyseed/core/projector.py

@@ -1,324 +1,69 @@
-# coding: utf-8
+from pawpyseed.core.wavefunction import *
 
-## @package pawpyseed.core.wavefunction
-# Base class containing Python classes for parsing files
-# and storing and analyzing wavefunction data.
+class Projector(Wavefunction):
 
-
-from pymatgen.io.vasp.inputs import Potcar, Poscar
-from pymatgen.io.vasp.outputs import Vasprun, Outcar
-from pymatgen.core.structure import Structure
-import numpy as np
-from ctypes import *
-from pawpyseed.core.utils import *
-import os, time
-import numpy as np
-import json
-
-import sys
-
-class Timer:
-	@staticmethod
-	def setup_time(t):
-		Timer.ALL_SETUP_TIME += t
-	@staticmethod
-	def overlap_time(t):
-		Timer.ALL_OVERLAP_TIME += t
-	@staticmethod
-	def augmentation_time(t):
-		Timer.ALL_AUGMENTATION_TIME += t
-	ALL_SETUP_TIME = 0
-	ALL_OVERLAP_TIME = 0
-	ALL_AUGMENTATION_TIME = 0
-
-class Pseudopotential:
-	"""
-	Contains important attributes from a VASP pseudopotential files. POTCAR
-	"settings" can be read from the pymatgen POTCAR object
-
-	Note: for the following attributes, 'index' refers to an energy
-	quantum number epsilon and angular momentum quantum number l,
-	which define one set consisting of a projector function, all electron
-	partial waves, and pseudo partial waves.
-
-	Attributes:
-		rmaxstr (str): Maximum radius of the projection operators, as string
-			of double precision float
-		grid (np.array): radial grid on which partial waves are defined
-		aepotential (np.array): All electron potential defined radially on grid
-		aecorecharge (np.array): All electron core charge defined radially
-			on grid (i.e. charge due to core, and not valence, electrons)
-		kinetic (np.array): Core kinetic energy density, defined raidally on grid
-		pspotential (np.array): pseudopotential defined on grid
-		pscorecharge (np.array): pseudo core charge defined on grid
-		ls (list): l quantum number for each index
-		pswaves (list of np.array): pseudo partial waves for each index
-		aewaves (list of np.array): all electron partial waves for each index
[…]

### 2018-08-21 pawpyseed/core/tests/test_core.py

@@ -332,8 +332,21 @@ class TestMem:
 
 class TestPy:
 
-	def setup():
+	def setup(self):
 		pass
 
-	def teardown():
+	def teardown(self):
 		pass
+
+	def test_init(self):
+		wf = Wavefunction.from_directory('.', True)
+		wf.free_all()
+		wf = Wavefunction.from_directory('.', False)
+		wf.free_all()
+		wf = Wavefunction.from_files('CONTCAR', 'OUTCAR', 'WAVECAR',
+			'POTCAR', 'vasprun.xml', 'OUTCAR', True)
+		wf.free_all()
+		wf = Wavefunction.from_files('CONTCAR', 'OUTCAR', 'WAVECAR',
+			'POTCAR', 'vasprun.xml', 'OUTCAR', False)
+		wf.free_all()
+		wf = Wavefunction()

### 2018-08-22 docs/techref.tex
add technical reference

--- 2018-03-21 docs/paper.tex
@@
 DFT wavefunctions in the PAW formalism}
-\author{Kyle Bystrom\\
-        kylebystrom@berkeley.edu\\
-		UC Berkeley Department of Materials Science and Engineering}
+\author[1]{Kyle Bystrom (kylebystrom@berkeley.edu)}
+\affil[1]{UC Berkeley Department of Materials Science and Engineering}
 \date{\today}
 \maketitle
-\abstract{A parallelized Python and C package has been developed
-to perform analysis of density functional theory (DFT) wavefunctions in the
-projector augmented wave (PAW) formalism. The primary function of this code
-is to calculate the overlap operator of two single-particle Kohn-Sham states
-from different periodic structures with the same lattice, which is made nontrivial
-by the depency of PAW augmentation regions on the basis of the structure.
-The code is potentially useful for the analysis of point defect levels in
-solids because it can determine the composition of defect levels in the basis
-of the single-particle states of the bulk system.}
+\abstract{This document serves as a technical reference for PAWpySeed.
+The main novel development of PAWpySeed, covered in Section 1,
+is the ability to evaluate the overlap operators of Kohn-Sham states
+in the PAW formulism which belong to different structures. For examples,
+one might want to project a defect level in a point defect structure
+onto the bands of the bulk structure. Additional sections will
+cover other developments as they are made.}
 
-\section{Theory}
+\section{Overlap Operators in PAW for Different Structures}
 
-\subsection{Projector Augmented Wave (PAW) Method}
-
-\subsection{Projections}
+The equation of a PAW wavefunction is\cite{blochl}
 \begin{equation}
 \ket{\psi_{n\mathbf{k}}}=\ket{\widetilde{\psi}_{n\mathbf{k}}}+
-\sum_{a,n,l,m}(\ket{\phi_{a\ind}}-\ket{\widetilde{\phi}_{a\ind}})
+\sum_{a,l,m,\epsilon}(\ket{\phi_{a\ind}}-\ket{\widetilde{\phi}_{a\ind}})
 \braket{\widetilde{p}_{a\ind}|\widetilde{\psi}_{n\mathbf{k}}}
@@
 \end{equation}
+where the sum is over the sites $a$ in the structure and a set of
+angular and radial quantum nubers $l$, $m$, and $\epsilon$ at each site.
+The conventional overlap operator used for these wavefunctions is
+\begin{equation}
+\widetilde{A}=A+\sum_i\sum_j\ket{\widetilde{p}_i}(\bra{\phi_i}A\ket{\phi_j}
+-\bra{\widetilde{\phi_i}}A\ket{\widetilde{\phi_j}})\bra{\widetilde{p}_j}
+\label{eq:loc}
+\end{equation}
+where $i$ and $j$ are abbreviations for a particular index set
+$a,l,m,\epsilon$. This overlap operator requires that the augmentation
+regions of the two wavefunctions are same. Since these augmentation regions
+are defined by the sites in the structure, the structures must be the same,
+so a new formalism is necessary to calculate overlap operators for wavefunctions
+in different structures.
 
-\subsubsection{Projection onto Basis from Different Structure}
-In the pure physical picture of a quantum mechanical system, the eigenfunctions of the time
-independent Hamiltonian form a complete basis for any function in real space. By expressing
-a wavefunction from a system in the basis of the eigenstates of another system, one might
-be able to learn about the nature of the wavefunction in question. For example, projecting
-the wavefunction of a defect level in a periodic crystal onto the eigenfunctions of the
-bulk crystal might yield information about how the defect level is constructed. For example,
-the defect state might project primarily onto the conduction band, characterizing it
-as a weakly perturbed host state. Such an understanding of defect levels could help select
-corrections to perform on the defect system.\cite{lany}
-\begin{equation}
-\centering
-\begin{split}
-\braket{\psi_{Rn_1\mathbf{k}}|\psi_{Sn_2\mathbf{k}}} & =\widetilde{O}+O_M+O_R+O_S+O_N\\
-O_M & =\sum_{a\in M_{RS}}\sum_{l,m}\sum_{\epsilon_1}\sum_{\epsilon_2}
-\braket{\widetilde{\psi}_{Rn_1\mathbf{k}}|\widetilde{p}_{a\ind _1}}
-(\braket{\phi_{a\ind _1}|{\phi_{a\ind _2}}}
--\bra{\widetilde{\phi}_{a\ind _1}}\ket{\widetilde{\phi}_{a\ind _2}})
-\braket{\widetilde{p}_{a\ind _2}|\widetilde{\psi}_{Sn_2\mathbf{k}}}\\
-O_R & =\sum_{i\in N_R}\braket{\widetilde{\psi}_{Rn_1\mathbf{k}}|\widetilde{p}_i}
-(\bra{\phi_i}-\bra{\widetilde{\phi}_i})
-\ket{\widetilde{\psi}_{Sn_2\mathbf{k}}}\\
-O_S & =\sum_{j\in N_S}\bra{\widetilde{\psi}_{Rn_1\mathbf{k}}}(\ket{\phi_j}-\ket{\widetilde{\phi}_j})
-\braket{\widetilde{p}_j|\widetilde{\psi}_{Sn_2\mathbf{k}}}\\
-O_N & =\sum_{i,j\in N_{RS}}\braket{\widetilde{\psi}_{Rn_1\mathbf{k}}|
-\widetilde{p}_i}(\bra{\phi_i}-\bra{\widetilde{\phi}_i})
-(\ket{\phi_j}-\ket{\widetilde{\phi}_j})\braket{\widetilde{p}_j|\widetilde{\psi}_{Sn_2\mathbf{k}}}
-\end{split}
-\label{eq:finp}
-\end{equation}
-Equation \ref{eq:finp} is derived in Appendix A.
+This section procedes first by deriving the main formula for calculating
+the overlap operator for KS states in different structures, and then
+presents a runtime scaling table for each operation involved in evaluating
+the formula. The algorithm for each operation is then discussed
 
-\section{Implementation}
-
-\begin{table}
-\centering
-\begin{tabular}{|c|c|c|}
-\hline
-Computational Task & $\Theta$ & Frequency*\\
-\hline
-$\widetilde{O}$ & $BKSW \sim n^2$ & per band\\
-$O_M$ & $BKSNP \sim n^2$ & per band\\
-$O_R$ and $O_S$ & $BKSNP \sim n^2$ & per band\\
-$O_N$ & $BKSNP \sim n^2$ & per band\\
-$\braket{\widetilde{p}_i|\widetilde{\psi}_{n\mathbf{k}}}$ & $BKSF\mathrm{log}(F)
-\sim n^2\mathrm{log}(n)$ & per structure\\
-$(\bra{\phi_i}-\bra{\widetilde{\phi}_i})
-\ket{\widetilde{\psi}_{n\mathbf{k}}}$ & $BKSNPW \sim n^3$ & per structure\\
-spherical Bessel transform partial waves & $NPG\mathrm{log}(G) \sim n$ & per structure pair\\
-project plane waves onto partial waves & $EPKW \sim n$ & per structure pair\\
-projections for overlapping aug spheres & $NPL \sim n$ & per structure pair\\
-\hline
-\end{tabular}
-
-\begin{tabular}{c|c}
-Symbol & Definition\\
-\hline
-B & number of bands\\
-E & number of elements\\
-F & size of FFT grid\\
-G & size of partial wave radial grid\\
-K & number of k-points\\
-L & size of Legendre-Gauss grid around ions\\
-N & number of sites**\\
-P & number of projector functions\\
-S & number of spin states\\
-W & number of plane waves\\
-n & number of electrons (approximate scaling)
-\end{tabular}
-\caption{Runtime scaling functions for each component of the code and
-definitions for shorthand symbols to express runtime. Approximate
-scales with the number of electrons are also shown.
-*The frequency refers to how often the routine is called. "Per band"
-indicates that the routine runs once every time a band from one structure
-is projected onto all the bands of a basis structure. "Per structure"
-indicates that the routine is a "setup" routine that must be called once
-for each structure and corresponding band structure to do perform projections.
-"Per structure pair" is the same as "per structure" except that the routine
-is only run once for a pair of structures with the same lattice and plane-wave
-basis set, the bands of one such structure to be used as a basis set for the other.
-**Number of sites flexibly refers to the number of sites relevant to the calculation,
-which worst-case scales with the total number of sites in the structure. For example,
-calculating $O_M$ and $O_N$ only require the sites in sets $M$ and $N_RS$, respectively.}
-\label{tab:runtime}
-\end{table}
-
-The program is implemented as a Python package that interfaces with C functions through
-the Python ctypes package. Time consuming routines are performed in C and parallelized
-using openmp, meaning that the code will automatically parallelize on all the resources
-of a shared memory computing node. Detailed runtime scaling for each routine is
-provided in Table \ref{tab:runtime}. An explanation of how each term is calculated
-so as to maximize computational efficiency is summarized in the following subsections.
-
-\subsection{Projection of Pseudowavefunctions onto Partial Waves}
-
-The all electron partial waves fluctuate rapidly near the nucleus,
-so the pseudowavefunction cannot be projected onto the partial waves
-via a uniform Cartesian grid as is doen with the projector functions.
-However, A plane wave can be expanded as a sum of spherical
-Bessel functions via Rayleigh expansion.
-\begin{equation}
-e^{i\mathbf{k} \cdot \mathbf{r}} = 4\pi \sum_{l=0}^{\infty}\sum_{m=-l}^{l}
-i^l j_l(kr)Y_l^{m*}(\mathbf{\hat{k}})Y_l^m(\mathbf{\hat{r}})
-\label{eq:pwexp}
-\end{equation}
-Therefore, the overlap operator between a partial wave and plane wave can be evaluated as a summation
-of spherical Bessel function overlap integrals. The following definitions are
-used in this derivation:
-
-$\mathbf{r_A} = \mathbf{r} - \mathbf{R_A}$, $\phi_i(\mathbf{r})=R_i(r)Y_l^m(\mathbf{\hat{r}})$,
-$\widetilde{\phi}_i(\mathbf{r})=\widetilde{R}_i(r)Y_l^m(\mathbf{\hat{r}})$,
-$\mathbf{k'}=\mathbf{k}+\mathbf{G}$\\
-The derivation goes as follows, with the last line being that needed to 
-calculate $O_R$ and $O_S$:
-
-\begin{equation}
-\begin{split}
-\widetilde{\psi}_{n\mathbf{k}} & =\frac{1}{\sqrt{V}}\sum_{\mathbf{G}}
-C_{n\mathbf{k}\mathbf{G}}e^{i\mathbf{k'}\cdot \mathbf{r}}\\
-\widetilde{\psi}_{n\mathbf{k}} & =\frac{4\pi}{\sqrt{V}}\sum_{\mathbf{G}}
-C_{n\mathbf{k}\mathbf{G}}\sum_{l=0}^{\infty}\sum_{m=-l}^{l}
-i^l j_l(k'r_A)Y_l^{m*}(\mathbf{\hat{k'}})Y_l^m(\mathbf{\hat{r}_A})\\
-\phi_i(\mathbf{r})\widetilde{\psi}_{n\mathbf{k}} & =\frac{4\pi}{\sqrt{V}}\sum_{\mathbf{G}}
-C_{n\mathbf{k}\mathbf{G}}\sum_{l'=0}^{\infty}\sum_{m'=-l'}^{l'}
-i^{l'} j_{l'}(k'r_A)Y_{l'}^{m'*}(\mathbf{\hat{k'}})Y_{l'}^{m'}(\mathbf{\hat{r}_A})
-Y_l^{m*}(\mathbf{\hat{r}}_A)R_i(r_A)\\
-\braket{\phi_i(\mathbf{r})|\widetilde{\psi}_{n\mathbf{k}}} & =
-\frac{4\pi i^l}{\sqrt{V}}\sum_{\mathbf{G}} C_{n\mathbf{k}\mathbf{G}}
-Y_l^{m*}(\mathbf{\hat{k'}})\int_0^{\infty}drr^2R_i(r_A)j_l(k'r_A)\\
-\braket{\phi_i-\widetilde{\phi}_i|\widetilde{\psi}_{n\mathbf{k}}} & =
-\frac{4\pi i^l}{\sqrt{V}}\sum_{\mathbf{G}} C_{n\mathbf{k}\mathbf{G}}
-Y_l^{m*}(\mathbf{\hat{k'}})\int_0^{\infty}drr^2(R_i(r_A)-\widetilde{R}_i(r_A))j_l(k'r_A)
-\end{split}
-\end{equation}
-
-After the projection is decomposed into a summation over integrals of spherical
-Bessel functions, it can be calculated via spherical Bessel transform. This code
-uses the fast spherical Bessel transform method NumSBT developed by Talman.\cite{TALMAN}
-It runs in $O(NlnN)$ time and works on a logarithmic grid, making it convenient for use with
-the POTCAR representations of the partial waves. The resulting logarithmic k-space
-grid can be used to calculate the values of the relevant integrals via interpolation.
-
-\section*{Appendix A: Derivation of Overlap Operators from PAW Formalism}
+\subsection{Derivation of Formula}
 
@@
 $M$ with overlapping augmentation regions, then
-$$
-\braket{\psi_{Rn_1\mathbf{k}}|\psi_{Sn_2\mathbf{k}}}=\widetilde{O}+O_M+O_R+O_S+O_N
-$$
-$$
-O_M=\sum_{a\in M_{RS}}\sum_{l,m}\sum_{\epsilon_1}\sum_{\epsilon_2}
+\begin{align}
+\braket{\psi_{Rn_1\mathbf{k}}|\psi_{Sn_2\mathbf{k}}}&=\widetilde{O}+O_M+O_R+O_S+O_N\\
+O_M&=\sum_{a\in M_{RS}}\sum_{l,m}\sum_{\epsilon_1}\sum_{\epsilon_2}
 \braket{\widetilde{\psi}_{Rn_1\mathbf{k}}|\widetilde{p}_{a\ind _1}}
@@
 -\braket{\widetilde{\phi}_{a\ind _1}|\widetilde{\phi}_{a\ind _2}})
-\braket{\widetilde{p}_{a\ind _2}|\widetilde{\psi}_{Sn_2\mathbf{k}}}
-$$
-$$
-O_R=\sum_{i\in N_R}\braket{\widetilde{\psi}_{Rn_1\mathbf{k}}|\widetilde{p}_i}
+\braket{\widetilde{p}_{a\ind _2}|\widetilde{\psi}_{Sn_2\mathbf{k}}}\\
+O_R&=\sum_{i\in N_R}\braket{\widetilde{\psi}_{Rn_1\mathbf{k}}|\widetilde{p}_i}
 (\bra{\phi_i}-\bra{\widetilde{\phi}_i})
-\ket{\widetilde{\psi}_{Sn_2\mathbf{k}}}
-$$
-$$
-O_S=\sum_{j\in N_S}\bra{\widetilde{\psi}_{Rn_1\mathbf{k}}}(\ket{\phi_j}-\ket{\widetilde{\phi}_j})
+\ket{\widetilde{\psi}_{Sn_2\mathbf{k}}}\\
+O_S&=\sum_{j\in N_S}\bra{\widetilde{\psi}_{Rn_1\mathbf{k}}}(\ket{\phi_j}
+-\ket{\widetilde{\phi}_j})
+\braket{\widetilde{p}_j|\widetilde{\psi}_{Sn_2\mathbf{k}}}\\
+O_N&=\sum_{i,j\in N_{RS}}\braket{\widetilde{\psi}_{Rn_1\mathbf{k}}|
+\widetilde{p}_i}(\bra{\phi_i}-\bra{\widetilde{\phi}_i})
+(\ket{\phi_j}-\ket{\widetilde{\phi}_j})
 \braket{\widetilde{p}_j|\widetilde{\psi}_{Sn_2\mathbf{k}}}
-$$
-$$
-O_N=\sum_{i,j\in N_{RS}}\braket{\widetilde{\psi}_{Rn_1\mathbf{k}}|
-\widetilde{p}_i}(\bra{\phi_i}-\bra{\widetilde{\phi}_i})
-(\ket{\phi_j}-\ket{\widetilde{\phi}_j})\braket{\widetilde{p}_j|\widetilde{\psi}_{Sn_2\mathbf{k}}}
-$$
-which is Equation \ref{eq:finp}.
+\label{eq:overlap}
+\end{align}
 
-\section*{Appendix B: Comprehensive POTCAR Guide}
-The PAWpySeed module makes use of the POTCAR files provided with the VASP source code, which
-contain the projector functions, partial waves, pseudopotentials, and core charge densities
-for each element. The format of the POTCAR file is not intuitive to non-developers, so this
-appendix seeks to comprehensively document the format of the VASP POTCAR files.
+\begin{table}
+\centering
+\caption{Runtime scaling functions for each component of the code and
+definitions for shorthand symbols to express runtime. Approximate
+scales with the number of electrons are also shown.
+*The frequency refers to how often the routine is called. "Per band"
+indicates that the routine runs once every time a band from one structure
+is projected onto all the bands of a basis structure. "Per structure"
+indicates that the routine is a "setup" routine that must be called once
+for each structure and corresponding band structure to do perform projections. "Per lattice"
+operations are required once per unique lattice used.
+"Per structure pair" is the same as "per structure" except that the routine
+is only run once for a pair of structures with the same lattice and plane-wave
+basis set, the bands of one such structure to be used as a basis set for the other.
+**Number of sites flexibly refers to the number of sites relevant to the calculation,
+which worst-case scales with the total number of sites in the structure. For example,
+calculating $O_M$ and $O_N$ only require the sites in sets $M$ and $N_RS$, respectively.}
+\label{tab:runtime}
 
-\subsection*{Overview}
-A single POTCAR contains the data for one element; a POTCAR file to a multi-element system
-is made by simply concatenating elemental POTCAR files. Each PAW POTCAR file follows
-the following format.
+\begin{tabular}{|c|c|c|}
+\hline
+Computational Task & $\Theta$ & Frequency*\\
+\hline
+$\widetilde{O}$ & $BKSW \sim n^2$ & per band\\
+$O_M$ & $BKSNP \sim n^2$ & per band\\
+$O_R$ and $O_S$ & $BKSNP \sim n^2$ & per band\\
+$O_N$ & $BKSNP \sim n^2$ & per band\\
+$\braket{\widetilde{p}_i|\widetilde{\psi}_{n\mathbf{k}}}$ & $BKSF\mathrm{log}(F)
+\sim n^2\mathrm{log}(n)$ & per structure\\
+$(\bra{\phi_i}-\bra{\widetilde{\phi}_i})
+\ket{\widetilde{\psi}_{n\mathbf{k}}}$ & $BKSNPW \sim n^3$ & per structure\\
+spherical Bessel transform partial waves & $NPG\mathrm{log}(G) \sim n$ & per structure pair\\
+project plane waves onto partial waves & $EPKW \sim n$ & per lattice\\
+projections for overlapping aug spheres & $NPL \sim n$ & per structure pair\\
+\hline
+\end{tabular}
 
-\begin{enumerate}
-	\item
-	\textbf{Settings}: The parameters used for the generation of the psuedopotentials,
-	as described thoroughly in VASP and pymatgen documentation.
-	\item
-	A bunch of stuff I still don't understand and which has no discernible grid.
-	\item
-	\textbf{Non local Part}: This section contains the \emph{non local projector functions}.
-	The first line after "Non local Part" gives the $l$ quantum number of the projector,
-	the number of projectors for that $l$ quantum number, and the radius of the real
-	space projector region.
-	\begin{enumerate}
-		\item
-		\textbf{Reciprocal Space Part}: The reciprocal space projection operator.
-		\item
-		\textbf{Real Space Part}: The real space projection operator values on a radial
-		grid. The radius at a given index $I$ is $RMAX*I/NDATA$, where RMAX and NDATA
-		are given in the settings section. Since $I$ is 0-indexed, the true maximal
-		radius of the projector is actually $RMAX*(NDATA-1)/NDATA$. Unlike the
-		\emph{partial wave} values (see \textbf{pseudo wavefunction},
-		the projector values are not mulitplied by $r$.
-		$$p(\mathbf{r})=realspacepart(index)Y_l^m(\hat{\mathbf{r}})$$
-	\end{enumerate}
-	\item
-	\textbf{PAW Radial Sets}
-	\begin{enumerate}
-		\item
-		Augmentation charges
-		\item
-		Occupancies
-		\item
-		\textbf{grid}: The exponential grid on which calculations related
-		to the \emph{partial waves} are performed.
-		\item
-		\textbf{pseudo wavefunction}: A pseudo \emph{partial wave} on the provided
-		radial grid, multiplied by $r$ for easy radial integration. I.e.
-		$$\phi(\mathbf{r}(index))=\frac{pseudowavefunction(index)}{r(index)}Y_l^m(\hat{\mathbf{r}})$$
-		Listed in the same order as the projector functions.
-		\item
-		\textbf{ae wavefunction}: Same pseudo wavefunction, but for the all electron \emph{partial wave}.
-	\end{enumerate}
-\end{enumerate}
+\begin{tabular}{c|c}
+Symbol & Definition\\
+\hline
+B & number of bands\\
+E & number of elements\\
+F & size of FFT grid\\
+G & size of partial wave radial grid\\
+K & number of k-points\\
+L & size of Legendre-Gauss grid around ions\\
+N & number of sites**\\
+P & number of projector functions\\
+S & number of spin states\\
+W & number of plane waves\\
+n & number of electrons (approximate scaling)
+\end{tabular}
+\end{table}
 
-\subsection*{}
+\subsection{Overlap of Pseudowavefunction ($\widetilde{O}$)}
+
+The pseudowavefunction is expanded as a sum of plane waves:
+
+\begin{equation}
+\widetilde{\psi}_{n\mathbf{k}} =\frac{1}{\sqrt{V}}\sum_{\mathbf{G}}
+C_{n\mathbf{k}\mathbf{G}}e^{i\mathbf{k'}\cdot \mathbf{r}}
+\label{eq:pswf}
+\end{equation}
+
+where $V$ is the volume of the unit cell, $\mathbf{k}$ is the k-point,
+$n$ is the band index, $\mathbf{r}$ is the position, and $C_{n\mathbf{k}\mathbf{G}}$
+are the plane-wave coefficients for the plane-waves with vector $\mathbf{k+G}$.
+
+Since plane waves are orthogonal and normalized to $V$ when integrated over the
+unit cell, the overlap of two pseudowavefunctions is evaluated easily
+by summing over plane-wave coefficients as described in the derivation section
+above.
+
+\subsection{Concentric Augmentation Spheres ($O_M$}
+
+Integrals of the type $\braket{\widetilde{\psi}_{Rn_1\mathbf{k}}|\widetilde{p}_{a\ind _1}}$
+between a pseudowavefunction and projector function are evaluated using a real-space
+FFT grid, as with VASP with LREAL=TRUE.\cite{vasp} Integrals of the
+type $\braket{\phi_{a\ind _1}|{\phi_{a\ind _2}}}$ between partial waves
+are evaluated by simple radial integration. This is possible because the augmentation
+spheres are concentric, so the spherical harmonics for the partial waves
+are orthonormal.
+
+\subsection{Partial Waves Overlapping with Pseudowavefunction ($O_R$, $O_S$)}
+
+These integrals are a little bit trickier because it is necessary to project
+a smoothly varying pseudowavefunction onto a rapidly varying AE partial wave.
+Performing such projections can become prohibitively computationally expensive
+for large cells.
+Taking advantage of the orthogonality of plane waves, this projection can be
+done in real space. Since a plane wave can be expanded around an arbitrary origin
+in space (to a phase factor) using Rayleigh expansion:
+
+\begin{equation}
+e^{i\mathbf{k} \cdot \mathbf{r}} = 4\pi \sum_{l=0}^{\infty}\sum_{m=-l}^{l}
+i^l j_l(kr)Y_l^{m*}(\mathbf{\hat{k}})Y_l^m(\mathbf{\hat{r}})
+\label{eq:pwexp}
+\end{equation}
+
+partial waves can be Fourier transformed into reciprocal space by evaluating
+overlap integrals with spherical Bessel functions. This is done using the
+$O(NlogN)$ NUMSBT algorithm developed by Talman.\cite{TALMAN} Then, all
+frequency components greater than the FFT grid density can be set to 0
+because those plane-waves are orthogonal to the finite plane-wave
+basis set of the pseudowavefunctions,
+and the partial waves can be transformed back into real space, also using
+the NUMSBT algorithm. This results in a smooth partial waves
+for which $(\bra{\phi_i}-\bra{\widetilde{\phi}_i})\ket{\widetilde{\psi}_{n\mathbf{k}}}$
+can be evaluated in real space.
+
+\subsection{Partial Wave Overlap on Non-Orthgonal Augmentation Spheres ($O_N$)}
+
+The $O_N$ term appears similar to the $O_M$ term, except that the integrals
+$(\bra{\phi_i}-\bra{\widetilde{\phi}_i})(\ket{\phi_j}-\ket{\widetilde{\phi}_j})$
+are more difficult to evaluate because the partial waves are centered
+at different sites. However, transforming these partial waves into
+reciprocal space using the spherical Bessel transform allows the
+overlap integrals to be evaluated using Equation (47) in Talman's
+NUMSBT paper.\cite{TALMAN}.
 

### 2018-08-22 pawpyseed/analysis/defect_composition.py
switch projection stuff over to Projector class

@@ -157,7 +157,7 @@ class BasisExpansion(PawpyData):
 
 			vr = Vasprun(os.path.join(wf_dir, 'vasprun.xml'))
 			dos = vr.tdos
-			expansion = np.zeros((wf.nband, basis.nband * basis.nwk * basis.nspin), dtype=np.float64)
+			expansion = np.zeros((wf.nband, basis.nband * basis.nwk * basis.nspin), dtype=np.complex128)
 			for b in range(wf.nband):
 				expansion[b,:] = wf.single_band_projection(b, basis)
 			bes[wf_dir] = BasisExpansion(dos, wf.structure, expansion)

### 2018-08-22 pawpyseed/core/projector.py

@@ -2,7 +2,7 @@ from pawpyseed.core.wavefunction import *
 
 class Projector(Wavefunction):
 
-	def __init__(wf, basis, setup_basis=True):
+	def __init__(self, wf, basis, projector_list = None):
 		"""
 		Projector is a class to projector KS states
 		from wf onto the KS states of basis
@@ -16,7 +16,7 @@ class Projector(Wavefunction):
 		self.cr = wf.cr
 		self.dim = wf.dim
 		self.projector_owner = True
-		self.projector_list = None
+		self.projector_list = projector_list
 		self.nband = wf.nband
 		self.nwk = wf.nwk
 		self.nspin = wf.nspin
@@ -24,12 +24,13 @@ class Projector(Wavefunction):
 		self.coords = wf.coords
 		self.basis = basis
 		self.wf = wf
+		self.num_proj_els = wf.num_proj_els
 
-		self.setup_projection(basis, setup_basis)
+		self.setup_projection(basis, projector_list == None)
 
 	@staticmethod
 	def from_files(basis, struct="CONTCAR", pwf="WAVECAR", cr="POTCAR",
-		vr="vasprun.xml", outcar="OUTCAR", setup_basis=True):
+		vr="vasprun.xml", outcar="OUTCAR", projector_list = None):
 		"""
 		Construct a Projector object from file paths.
 		Arguments:
@@ -45,10 +46,10 @@ class Projector(Wavefunction):
 		return Projector(Poscar.from_file(struct).structure,
 			PseudoWavefunction(pwf, vr),
 			CoreRegion(Potcar.from_file(cr)),
-			Outcar(outcar), setup_basis)
+			Outcar(outcar), projector_list)
 
 	@staticmethod
-	def from_directory(basis, path, setup_basis=True):
+	def from_directory(basis, path, projector_list = None):
 		"""
 		Assumes VASP output has the default filenames and is located
 		in the directory specificed by path.
@@ -62,7 +63,7 @@ class Projector(Wavefunction):
 		filepaths = []
 		for d in ["CONTCAR", "WAVECAR", "POTCAR", "vasprun.xml", "OUTCAR"]:
 			filepaths.append(str(os.path.join(path, d)))
-		args = filepaths + [setup_basis]
+		args = filepaths + [projector_list]
 		return Projector.from_files(*args)
 
 	def setup_projection(self, basis, setup_basis=True):
[…]

### 2018-08-22 pawpyseed/core/wavefunction.py

@@ -236,15 +236,16 @@ class Wavefunction:
 		self.dim = np.array(self.dim).astype(np.int32) // 2
 		self.projector_owner = False
 		self.projector_list = None
-			if setup_projectors:
-				self.projector_owner = True
-				self.projector_list, self.nums,\
-					self.coords = self.make_c_projectors()
+		if setup_projectors:
+			self.projector_owner = True
+			self.projector_list, self.nums,\
+				self.coords = self.make_c_projectors()
 		self.nband = PAWC.get_nband(c_void_p(pwf.wf_ptr))
 		self.nwk = PAWC.get_nwk(c_void_p(pwf.wf_ptr))
 		self.nspin = PAWC.get_nspin(c_void_p(pwf.wf_ptr))
 		self.nums = None
 		self.coords = None
+		self.num_proj_els = None
 
 	@staticmethod
 	def from_files(struct="CONTCAR", pwf="WAVECAR", cr="POTCAR",

### 2018-08-22 pawpyseed/analysis/defect_composition.py
cleaning up projector an wavefunction

@@ -114,10 +114,10 @@ class BulkCharacter(PawpyData):
 
 		bcs = {}
 
-		for wf_dir, basis, wf in generator:
+		for wf_dir, wf in generator:
 			vr = Vasprun(os.path.join(wf_dir, 'vasprun.xml'))
 			dos = vr.tdos
-			data = wf.defect_band_analysis(basis, spinpol = True)
+			data = wf.defect_band_analysis(spinpol = True)
 			bcs[wf_dir] = BulkCharacter(dos, wf.structure, data)
 
 		return bcs
@@ -153,13 +153,14 @@ class BasisExpansion(PawpyData):
 
 		bes = {}
 
-		for wf_dir, basis, wf in generator:
+		for wf_dir, wf in generator:
 
 			vr = Vasprun(os.path.join(wf_dir, 'vasprun.xml'))
 			dos = vr.tdos
-			expansion = np.zeros((wf.nband, basis.nband * basis.nwk * basis.nspin), dtype=np.complex128)
+			expansion = np.zeros((wf.nband, basis.nband * basis.nwk * basis.nspin),
+				dtype=np.complex128)
 			for b in range(wf.nband):
-				expansion[b,:] = wf.single_band_projection(b, basis)
+				expansion[b,:] = wf.single_band_projection(b)
 			bes[wf_dir] = BasisExpansion(dos, wf.structure, expansion)
 
 		return bes

### 2018-08-22 pawpyseed/core/projector.py

@@ -1,3 +1,10 @@
+# coding: utf-8
+
+## @package pawpyseed.core.projector
+# Defines the Projector class, an extension
+# of the Wavefunction class for evaluating
+# AE projection operators.
+
 from pawpyseed.core.wavefunction import *
 
 class Projector(Wavefunction):
@@ -10,6 +17,22 @@ class Projector(Wavefunction):
 		Wavefunction, so a Projector is essentially
 		a Wavefunction object that is set up to be
 		projected onto basis.
+
+		Arguments:
+			wf (Wavefunction): The wavefunction objects whose
+				bands are to be projected onto basis
+			basis (Wavefunction): The wavefunction whose bands
+				serve as the basis set for projection
+			projector_list (c_void_p) (default None): pointer to a list of C
+				ppot_t objects. When manually calling the initializer,
+				this should generally be left as the default, in which
+				case the setup will be performed for wf and basis.
+				projector_list != None is used by setup_multiple_projections
+				for efficiency and memory management
+
+		Returns:
+			Projector object, containing all the same fields as
+				wf but set up for projections onto basis
 		"""
 		self.structure = wf.structure
 		self.pwf = wf.pwf
@@ -65,6 +88,51 @@ class Projector(Wavefunction):
 			filepaths.append(str(os.path.join(path, d)))
 		args = filepaths + [projector_list]
 		return Projector.from_files(*args)
+
+	def make_site_lists(self, basis):
+		"""
+		Organizes sites into sets for use in the projection scheme. M_R and M_S contain site indices
+		of sites which are identical in structures R (basis) and S (self). N_R and N_S contain all other
+		site indices, and N_RS contains pairs of indices in R and S with overlapping augmentation
+		spheres in the PAW formalism.
+
+		Arguments:
+			basis (Wavefunction object): Wavefunction in the same lattice as self.
+				The bands in self will be projected onto the bands in basis
+		Returns:
+			M_R (numpy array): Indices of sites in basis which have an identical site in
[…]

### 2018-08-22 pawpyseed/core/tests/test_core.py

@@ -27,15 +27,15 @@ if not "PAWPYCC" in os.environ:
 	elif subprocess.call("which gcc".split()) == 0:
 		os.environ["PAWPYCC"] = "gcc"
 	else:
-		raise PawpyBuildError("Can't find icc or gcc compiler!")
+		raise PawpyError("Can't find icc or gcc compiler!")
 
 status = subprocess.call('make tests'.split())
 if status != 0:
-	raise PawpyBuildError("Can't compile tpawpy.so! Check the C error output for details.")
+	raise PawpyError("Can't compile tpawpy.so! Check the C error output for details.")
 	status = subprocess.call('make tests'.split())
 status = subprocess.call('make memtest'.split())
 if status != 0:
-	raise PawpyBuildError("Can't compile memtest! Check the C error output for details.")
+	raise PawpyError("Can't compile memtest! Check the C error output for details.")
 os.chdir(currdir)
 
 MODULE_DIR = os.path.dirname(os.path.abspath(__file__))
@@ -333,10 +333,11 @@ class TestMem:
 class TestPy:
 
 	def setup(self):
-		pass
+		self.currdir = os.getcwd()
+		os.chdir(os.path.join(MODULE_DIR, '../../../test_files'))
 
 	def teardown(self):
-		pass
+		os.chdir(self.currdir)
 
 	def test_init(self):
 		wf = Wavefunction.from_directory('.', True)
@@ -350,3 +351,32 @@ class TestPy:
 			'POTCAR', 'vasprun.xml', 'OUTCAR', False)
 		wf.free_all()
 		wf = Wavefunction()
+
+	def test_writestate(self):
+		wf = Wavefunction.from_directory('.')
+		fileprefix = ''
+		b, k, s = 10, 1, 0
+		state1 = wf.write_state_realspace(self, b, k, s, fileprefix = "", 
+			dim=np.array([30,30,30]), return_wf = True)
+		wf.free_all()
+		wf = Wavefunction.from_directory('.', False)
+		state2 = wf.write_state_realspace(self, b, k, s, fileprefix = "", 
+			dim=np.array([30,30,30]), return_wf = True)
+		wf.free_all()
+		assert_almost_equal(np.linalg.norm(state1-state2),0)
+		assert state1.shape[0] == 2*30*30*30
+		filename_base = "%sB%dK%dS%d" % (fileprefix, b, k, s)
[…]

### 2018-08-22 pawpyseed/core/wavefunction.py

@@ -276,109 +276,6 @@ class Wavefunction:
 		args = filepaths + [setup_projectors]
 		return Wavefunction.from_files(*args)
 
-	def make_site_lists(self, basis):
-		"""
-		Organizes sites into sets for use in the projection scheme. M_R and M_S contain site indices
-		of sites which are identical in structures R (basis) and S (self). N_R and N_S contain all other
-		site indices, and N_RS contains pairs of indices in R and S with overlapping augmentation
-		spheres in the PAW formalism.
-
-		Arguments:
-			basis (Wavefunction object): Wavefunction in the same lattice as self.
-				The bands in self will be projected onto the bands in basis
-		Returns:
-			M_R (numpy array): Indices of sites in basis which have an identical site in
-				S (self) (same element and position to within tolerance of 0.02 Angstroms).
-			M_S (numpy array): Indices of sites in self which match sites in M_R
-				(i.e. M_R[i] is an identical site to M_S[i])
-			N_R (numpy array): Indices of sites in basis but not in M_R
-			N_S (numpy array): Indices of sites in self but not in M_S
-			N_RS (numpy array): Pairs of indices (one in basis and one in self) which
-				are not identical but have overlapping augmentation regions
-		"""
-		ref_sites = basis.structure.sites
-		sites = self.structure.sites
-		M_R = []
-		M_S = []
-		for i in range(len(ref_sites)):
-			for j in range(len(sites)):
-				if ref_sites[i].distance(sites[j]) <= 0.02 and el(ref_sites[i]) == el(sites[j]):
-					M_R.append(i)
-					M_S.append(j)
-		N_R = []
-		N_S = []
-		for i in range(len(ref_sites)):
-			if not i in M_R:
-				N_R.append(i)
-		for j in range(len(sites)):
-			if (not j in N_S) and (not j in M_S):
-				N_S.append(j)
-		
-		N_RS = []
-		for i in N_R:
-			for j in N_S:
-				if ref_sites[i].distance(sites[j]) < self.cr.pps[el(ref_sites[i])].rmax + self.cr.pps[el(sites[j])].rmax:
-					N_RS.append((i,j))
[…]

### 2018-10-05 pawpyseed/core/projector.c
resolve #48 but create a couple more specific issues

@@ -444,6 +444,7 @@ void make_pwave_overlap_matrices(ppot_t* pp_ptr) {
 void setup_projections_no_rayleigh(pswf_t* wf, ppot_t* pps, int num_elems,
 	int num_sites, int* fftg, int* labels, double* coords) {
 
+	wf->num_sites = num_sites;
 	wf->fftg = (int*) malloc(3*sizeof(int));
 	wf->fftg[0] = fftg[0];
 	wf->fftg[1] = fftg[1];

### 2018-10-05 pawpyseed/core/projector.py

@@ -601,7 +601,7 @@ class Projector(Wavefunction):
 		and projector_list is the C pointer of the same name returned by setup_bases
 		"""
 		
-		PAWC.free_ppot_list(c_void_p(projector_list), len(self.cr.pps))
+		PAWC.free_ppot_list(c_void_p(projector_list), num_elems)
 
 	def free_all(self):
 		"""

### 2018-10-05 pawpyseed/core/utils.c

@@ -146,16 +146,32 @@ void free_rayleigh_set_list(rayleigh_set_t* sets, int num_projs) {
 	free(sets);
 }
 
-void free_kpoint(kpoint_t* kpt, int num_elems, int* num_projs) {
+void free_projection_list(projection_t* projlist, int num) {
+	for (int i = 0; i < num; i++) {
+		free(projlist[i].ms);
+		free(projlist[i].ls);
+		free(projlist[i].ns);
+		free(projlist[i].overlaps);
+	}
+	free(projlist);
+}
+
+void free_kpoint(kpoint_t* kpt, int num_elems, int num_sites, int* num_projs) {
 	for (int b = 0; b < kpt->num_bands; b++) {
 		band_t* curr_band = kpt->bands[b];
 		free(curr_band->Cs);
-		//if (curr_band->projections != NULL) {
-		//	free(curr_band->projections);
-		//}
+		if (curr_band->projections != NULL) {
+			free_projection_list(curr_band->projections, num_sites);
+		}
 		//if (curr_band->wave_projections != NULL) {
-		//	free(curr_band->wave_projections);
+		//	free_projection_list(curr_band->wave_projections, num_sites);
 		//}
+		if (curr_band->up_projections != NULL) {
+			free_projection_list(curr_band->up_projections, num_sites);
+		}
+		if (curr_band->down_projections != NULL) {
+			free_projection_list(curr_band->down_projections, num_sites);
+		}
 		if (curr_band->CRs != NULL) {
 			mkl_free(curr_band->CRs);
 		}
@@ -207,11 +223,14 @@ void free_real_proj(real_proj_t* proj) {
 
 void free_pswf(pswf_t* wf) {
 	for (int i = 0; i < wf->nwk * wf->nspin; i++)
-		free_kpoint(wf->kpts[i], wf->num_elems, wf->num_projs);
+		free_kpoint(wf->kpts[i], wf->num_elems, wf->num_sites, wf->num_projs);
 	if (wf->overlaps != NULL) {
 		for (int i = 0; i < wf->num_aug_overlap_sites; i++)
 			free(wf->overlaps[i]);
 		free(wf->overlaps);
+	}
+	if (wf->num_projs != NULL) {
+		free(wf->num_projs);
 	}
 	free(wf->kpts);
[…]

### 2018-10-05 pawpyseed/core/utils.h

@@ -212,7 +212,9 @@ void min_cart_path(double* coord, double* center, double* lattice, double* path,
 
 double complex trilinear_interpolate(double complex* c, double* frac, int* fftg);
 
-void free_kpoint(kpoint_t* kpt, int num_elems, int* num_projs);
+void free_projection_list(projection_t* projlist, int num);
+
+void free_kpoint(kpoint_t* kpt, int num_elems, int num_sites, int* num_projs);
 
 void free_ppot(ppot_t* pp);
 

### 2018-10-05 pawpyseed/core/utils.py

@@ -75,8 +75,13 @@ PAWC.get_nband.restype = c_int
 PAWC.get_nwk.restype = c_int
 PAWC.get_nspin.restype = c_int
 
+PAWC.free_ptr.argtypes = [c_void_p]
 PAWC.free_ptr.restype = None
+
+PAWC.free_ppot_list.argtypes = [c_void_p, c_int]
 PAWC.free_ppot_list.restype = None
+
+PAWC.free_pswf.argtypes = [c_void_p]
 PAWC.free_pswf.restype = None
 
 class PAWpyError(Exception):

### 2018-10-05 pawpyseed/core/wavefunction.py

@@ -4,11 +4,11 @@
 # Base class containing Python classes for parsing files
 # and storing and analyzing wavefunction data.
 
-
 from pymatgen.io.vasp.inputs import Potcar, Poscar
 from pymatgen.io.vasp.outputs import Vasprun, Outcar
 from pymatgen.core.structure import Structure
 from pymatgen.symmetry.analyzer import SpacegroupAnalyzer
+from pymatgen.core.operations import SymmOp
 import numpy as np
 from ctypes import *
 from pawpyseed.core.utils import *
@@ -557,16 +557,22 @@ class Wavefunction:
 		print("KPTS", allkpts)
 		return np.array(allkpts), orig_kptnums, op_nums, symmops
 
-	def get_kpt_mapping(self, allkpts, symprec=1e-3):
+	def get_kpt_mapping(self, allkpts, symprec=1e-3, invsym = True):
 		sga = SpacegroupAnalyzer(self.structure, symprec)
 		symmops = sga.get_symmetry_operations()
+		newops = []
+		if invsym:
+			for op in symmops:
+				newops.append(SymmOp.from_rotation_and_translation(
+					op.rotation_matrix*-1, op.translation_vector*-1))
+		symmops += newops
 		kpts = np.array(self.pwf.kpts)
 		orig_kptnums = []
 		op_nums = []
 		for nkpt in allkpts:
 			match = False
-			for k, kpt in enumerate(kpts):
-				for i, op in enumerate(symmops):
+			for i, op in enumerate(symmops):
+				for k, kpt in enumerate(kpts):
 					newkpt = np.dot(op.rotation_matrix, kpt)
 					if np.linalg.norm(newkpt-nkpt) < 1e-10:
 						match = True

### 2018-10-05 docs/techref.tex
add time reversal symmetry to expand_symm_wf, get_kpt_mapping, and get_nosym_kpoints

@@
 where the sum is over the sites $a$ in the structure and a set of
-angular and radial quantum nubers $l$, $m$, and $\epsilon$ at each site.
-The conventional overlap operator used for these wavefunctions is
+angular and radial quantum numbers $l$, $m$, and $\epsilon$ at each site.
+Local and semilocal operators in PAW can be expressed as
 \begin{equation}
@@
 presents a runtime scaling table for each operation involved in evaluating
-the formula. The algorithm for each operation is then discussed
+the formula. The algorithm for each operation is then discussed.
 

### 2018-10-05 pawpyseed/core/projector.py

@@ -67,32 +67,32 @@ class Projector(Wavefunction):
 		#__init__(self, filename="WAVECAR", vr="vasprun.xml")
 
 		if unsym_basis and unsym_wf:
-			allkpts, borig_kptnums, bop_nums, bsymmops = basis.get_nosym_kpoints()
+			allkpts, borig_kptnums, bop_nums, bsymmops, btrs = basis.get_nosym_kpoints()
 			weights = np.ones(allkpts.shape[0]) / allkpts.shape[0]
-			worig_kptnums, wop_nums, wsymmops = wf.get_kpt_mapping(allkpts)
+			worig_kptnums, wop_nums, wsymmops, wtrs = wf.get_kpt_mapping(allkpts)
 			bops, bdrs = make_c_ops(bop_nums, bsymmops)
 			wops, wdrs = make_c_ops(wop_nums, wsymmops)
 			bptr = cfunc_call(PAWC.expand_symm_wf, None, basis.pwf.wf_ptr,
-				len(borig_kptnums), borig_kptnums, bops, bdrs, weights)
+				len(borig_kptnums), borig_kptnums, bops, bdrs, weights, btrs)
 			wptr = cfunc_call(PAWC.expand_symm_wf, None, wf.pwf.wf_ptr,
-				len(worig_kptnums), worig_kptnums, wops, wdrs, weights)
+				len(worig_kptnums), worig_kptnums, wops, wdrs, weights, wtrs)
 			basis = copy_wf(basis, bptr, allkpts, weights, False, True)
 			wf = copy_wf(wf, wptr, allkpts, weights, False, True)
 		elif unsym_wf and not unsym_basis:
 			allkpts = basis.pwf.kpts
 			weights = basis.pwf.kws
-			worig_kptnums, wop_nums, wsymmops = wf.get_kpt_mapping(allkpts)
+			worig_kptnums, wop_nums, wsymmops, trs = wf.get_kpt_mapping(allkpts)
 			wops, wdrs = make_c_ops(wop_nums, wsymmops)
 			wptr = cfunc_call(PAWC.expand_symm_wf, None, wf.pwf.wf_ptr,
-				len(worig_kptnums), worig_kptnums, wops, wdrs, weights)
+				len(worig_kptnums), worig_kptnums, wops, wdrs, weights, trs)
 			wf = copy_wf(wf, wptr, allkpts, weights, False, True)
 		elif unsym_basis and not unsym_wf:
 			allkpts = wf.pwf.kpts
[…]

### 2018-10-05 pawpyseed/core/utils.c

@@ -848,7 +848,7 @@ void copy_rayleigh_expansion_terms(pswf_t* wf, ppot_t* pps, int num_elems, pswf_
 }
 
 pswf_t* expand_symm_wf(pswf_t* rwf, int num_kpts, int* maps,
-	double* ops, double* drs, double* kws) {
+	double* ops, double* drs, double* kws, int* trs) {
 
 	double* lattice = rwf->lattice;
 	double* reclattice = rwf->reclattice;
@@ -898,7 +898,13 @@ pswf_t* expand_symm_wf(pswf_t* rwf, int num_kpts, int* maps,
 		kpt->up = rkpt->up;
 		kpt->num_waves = rkpt->num_waves;
 		kpt->k = (double*) malloc(3 * sizeof(double));
+		int tr = trs[knum%num_kpts];
 		rotation_transform(kpt->k, ops+OPSIZE*(knum%num_kpts), rkpt->k);
+		if (tr == 1) {
+			kpt->k[0] *= -1;
+			kpt->k[1] *= -1;
+			kpt->k[2] *= -1;
+		}
 		//printf("OLD KPT %lf %lf %lf\n", okpt->k[0], okpt->k[1], okpt->k[2]);
 		printf("NEW KPT %lf %lf %lf\n", kpt->k[0], kpt->k[1], kpt->k[2]);
 		//kpt->Gs = (int*) malloc(3 * kpt->num_waves * sizeof(int));
@@ -1000,6 +1006,11 @@ pswf_t* expand_symm_wf(pswf_t* rwf, int num_kpts, int* maps,
 			pw[2] = rkpt->k[2] + rkpt->Gs[3*g+2];
 
 			rotation_transform(pw, ops+OPSIZE*(knum%num_kpts), pw);
+			if (tr == 1) {
+				pw[0] *= -1;
+				pw[1] *= -1;
+				pw[2] *= -1;
+			}
 
 			pw[0] -= kpt->k[0];
 			pw[1] -= kpt->k[1];
@@ -1044,6 +1055,9 @@ pswf_t* expand_symm_wf(pswf_t* rwf, int num_kpts, int* maps,
 					printf("ERROR, INCOMPLETE PLANE WAVE MAPPING\n");
 				}
 				kpt->bands[b]->Cs[w] = factors[w] * rkpt->bands[b]->Cs[gmaps[w]];
+				if (tr == 1) {
[…]

### 2018-10-05 pawpyseed/core/utils.h

@@ -388,7 +388,7 @@ to new kpoints, and calculates a new wavefunction that has the
 additional kpoints.
 */
 pswf_t* expand_symm_wf(pswf_t* rwf, int num_kpts, int* maps,
-	double* ops, double* drs, double* kws);
+	double* ops, double* drs, double* kws, int* trs);
 
 /**
 Called after a malloc or calloc call to check that

### 2018-10-05 pawpyseed/core/wavefunction.py

@@ -525,17 +525,20 @@ class Wavefunction:
 		self._convert_to_vasp_volumetric(filename, dim)
 		return res
 
-	def get_nosym_kpoints(self, init_kpts = None, symprec=1e-3, invsym = True):
+	def get_nosym_kpoints(self, init_kpts = None, symprec=1e-3,
+		gen_trsym = True, fil_trsym = True):
+
 		kpts = np.array(self.pwf.kpts)
 		allkpts = [] if init_kpts == None else [kpt for kpt in init_kpts]
 		orig_kptnums = []
 		op_nums = []
 		sga = SpacegroupAnalyzer(self.structure, symprec)
 		symmops = sga.get_point_group_operations()
+		trs = []
 		for i, op in enumerate(symmops):
 			for k, kpt in enumerate(kpts):
 				newkpt = np.dot(op.rotation_matrix, kpt)
-				if invsym:
+				if fil_trsym:
 					if newkpt[2] < -1e-10 or \
 						(abs(newkpt[2]) < 1e-10 and newkpt[1] < -1e-10):
 						continue
@@ -549,15 +552,35 @@ class Wavefunction:
 					allkpts.append(newkpt)
 					orig_kptnums.append(k)
 					op_nums.append(i)
+					trs.append(0)
+		if gen_trsym:
+			for i, op in enumerate(symmops):
+				for k, kpt in enumerate(kpts):
+					newkpt = np.dot(op.rotation_matrix, kpt) * -1
+					if fil_trsym:
+						if newkpt[2] < -1e-10 or \
+							(abs(newkpt[2]) < 1e-10 and newkpt[1] < -1e-10):
+							continue
+					unique = True
+					for nkpt in allkpts:
+						if ( np.linalg.norm(newkpt-nkpt) < 1e-10 ) \
+								and (np.abs(newkpt) < 1).all():
+							unique = False
+							break
+					if unique:
+						allkpts.append(newkpt)
+						orig_kptnums.append(k)
+						op_nums.append(i)
+						trs.append(1)
 		self.nosym_kpts = allkpts
 		self.orig_kptnums = orig_kptnums
 		self.op_nums = op_nums
 		self.symmops = symmops
 		print("NUMBER OF KPTS", len(allkpts))
 		print("KPTS", allkpts)
-		return np.array(allkpts), orig_kptnums, op_nums, symmops
+		return np.array(allkpts), orig_kptnums, op_nums, symmops, trs
 
[…]

### 2018-10-05 pawpyseed/core/wavefunction.py
resolve #56

@@ -584,10 +584,6 @@ class Wavefunction:
 		sga = SpacegroupAnalyzer(self.structure, symprec)
 		symmops = sga.get_symmetry_operations()
 		newops = []
-		if invsym:
-			for op in symmops:
-				newops.append(SymmOp.from_rotation_and_translation(
-					op.rotation_matrix*-1, op.translation_vector*-1))
 		symmops += newops
 		kpts = np.array(self.pwf.kpts)
 		orig_kptnums = []

### 2018-10-06 pawpyseed/core/utils.c
finish kpoint symmetry mapping and resolve #53

@@ -156,16 +156,29 @@ void free_projection_list(projection_t* projlist, int num) {
 	free(projlist);
 }
 
-void free_kpoint(kpoint_t* kpt, int num_elems, int num_sites, int* num_projs) {
+void clean_wave_projections(pswf_t* wf) {
+
+	for (int i = 0; i < wf->nwk * wf->nspin; i++) {
+		kpoint_t* kpt = wf->kpts[i];
+		for (int b = 0; b < kpt->num_bands; b++) {
+			if (kpt->bands[b]->wave_projections != NULL) {
+				free_projection_list(kpt->bands[b]->wave_projections, wf->wp_num);
+			}
+		}
+	}
+
+}
+
+void free_kpoint(kpoint_t* kpt, int num_elems, int num_sites, int wp_num, int* num_projs) {
 	for (int b = 0; b < kpt->num_bands; b++) {
 		band_t* curr_band = kpt->bands[b];
 		free(curr_band->Cs);
 		if (curr_band->projections != NULL) {
 			free_projection_list(curr_band->projections, num_sites);
 		}
-		//if (curr_band->wave_projections != NULL) {
-		//	free_projection_list(curr_band->wave_projections, num_sites);
-		//}
+		if (curr_band->wave_projections != NULL) {
+			free_projection_list(curr_band->wave_projections, wp_num);
+		}
 		if (curr_band->up_projections != NULL) {
 			free_projection_list(curr_band->up_projections, num_sites);
 		}
@@ -223,7 +236,7 @@ void free_real_proj(real_proj_t* proj) {
 
 void free_pswf(pswf_t* wf) {
 	for (int i = 0; i < wf->nwk * wf->nspin; i++)
-		free_kpoint(wf->kpts[i], wf->num_elems, wf->num_sites, wf->num_projs);
+		free_kpoint(wf->kpts[i], wf->num_elems, wf->num_sites, wf->wp_num, wf->num_projs);
 	if (wf->overlaps != NULL) {
 		for (int i = 0; i < wf->num_aug_overlap_sites; i++)
 			free(wf->overlaps[i]);
@@ -881,6 +894,7 @@ pswf_t* expand_symm_wf(pswf_t* rwf, int num_kpts, int* maps,
 	wf->dcoords = NULL;
 	wf->overlaps = NULL;
 	wf->num_projs = NULL;
+	wf->wp_num = 0;
 
[…]

### 2018-10-06 pawpyseed/core/utils.h

@@ -90,7 +90,7 @@ typedef struct band {
 	projection_t* projections; ///< length==number of sites in structure
 	projection_t* up_projections; ///< length==number of sites in structure
 	projection_t* down_projections; ///< length==number of sites in structure
-	projection_t* wave_projections; ///< length==number of sites in structure
+	projection_t* wave_projections; ///< used for offsite compensation terms
 } band_t;
 
 typedef struct rayleigh_set {
@@ -126,6 +126,7 @@ typedef struct pswf {
 
 	int is_ncl; ///< 1 if noncollinear, 0 otherwise
 
+	int wp_num; ///< length==size of wave_projections in each band
 	int num_aug_overlap_sites; ///< used for Projector operations
 	double* dcoords; ///< used for Projector operations
 	double complex** overlaps; ///< used for Projector operations
@@ -214,7 +215,9 @@ double complex trilinear_interpolate(double complex* c, double* frac, int* fftg)
 
 void free_projection_list(projection_t* projlist, int num);
 
-void free_kpoint(kpoint_t* kpt, int num_elems, int num_sites, int* num_projs);
+void clean_wave_projections(pswf_t* wf);
+
+void free_kpoint(kpoint_t* kpt, int num_elems, int num_sites, int wp_num, int* num_projs);
 
 void free_ppot(ppot_t* pp);
 
